---
title: "A2 Technical Appendix: Nike Text Analytics and Classification"
author: "Team 6"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
	html_document:
		toc: true
		toc_depth: 3
		number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 10,
	fig.height = 6
)
```

## 1. Business Framing and Decision Context

### Client decision to support

Nike leadership wants evidence-based guidance on brand perception, product quality pain points, sustainability narrative credibility, pricing sensitivity, and competitor positioning.

### Strategic business questions selected in this analysis

1. How is Nike emotionally positioned in online conversation versus Adidas and Under Armour?
2. What complaint themes most strongly drive negative Nike reviews?
3. Is sustainability language associated with trust or skepticism?
4. Is premium-pricing language associated with negative sentiment?

### Hypotheses

1. Negative Nike sentiment is concentrated in sizing, durability, and price-related language.
2. Sustainability mentions are polarized, showing both trust and skepticism language.
3. Nike language differs from competitors through innovation/performance terms, while competitors over-index on value language.

## 2. Reproducible Environment

```{r packages}
required_pkgs <- c(
	"tidyverse", "tidytext", "lubridate", "stringr", "janitor",
	"stopwords", "SnowballC", "textdata", "topicmodels", "widyr",
	"igraph", "ggraph", "scales", "broom", "glmnet", "yardstick"
)

missing_pkgs <- required_pkgs[!sapply(required_pkgs, requireNamespace, quietly = TRUE)]
if (length(missing_pkgs) > 0) {
	message("Install missing packages before knitting: ", paste(missing_pkgs, collapse = ", "))
}

invisible(lapply(required_pkgs, function(p) {
	suppressPackageStartupMessages(library(p, character.only = TRUE))
}))

set.seed(42)
```

## 3. Data Sources and Input Schema

This appendix expects team-collected data from at least two channels (for example: Nike product reviews + X posts, or Nike reviews + Reddit).

Place source files under a folder named data in the same project as this Rmd.

Supported file types: CSV and TXT.

### 3.1 Expected minimum fields

- text: raw text content
- brand: Nike, Adidas, Under Armour, or Other
- source: nike_site, retailer, x, reddit, youtube, app_store, news

### 3.2 Optional fields used for deeper analysis

- product_line: Pegasus, Air Max, Jordan, Metcon, etc.
- rating: numeric rating where available
- date: post/review date

```{r load-data}
data_dir <- "data"

if (!dir.exists(data_dir)) {
	stop("Create a data/ folder and add your team-collected files before knitting.")
}

csv_files <- list.files(data_dir, pattern = "\\.csv$", full.names = TRUE)
txt_files <- list.files(data_dir, pattern = "\\.txt$", full.names = TRUE)

if (length(csv_files) + length(txt_files) == 0) {
	stop("No input files found in data/. Add at least two text data sources.")
}

read_one_csv <- function(path) {
	x <- readr::read_csv(path, show_col_types = FALSE) %>%
		janitor::clean_names()

	# Flexible column mapping for common naming variants.
	nm <- names(x)
	if (!"text" %in% nm) {
		text_candidates <- c("review", "review_text", "content", "body", "comment", "tweet", "title")
		hit <- intersect(text_candidates, nm)
		if (length(hit) > 0) x <- dplyr::rename(x, text = !!hit[1])
	}

	if (!"brand" %in% names(x)) x$brand <- NA_character_
	if (!"source" %in% names(x)) x$source <- tools::file_path_sans_ext(basename(path))
	if (!"product_line" %in% names(x)) x$product_line <- NA_character_
	if (!"rating" %in% names(x)) x$rating <- NA_real_
	if (!"date" %in% names(x)) x$date <- NA

	x %>%
		mutate(
			file_name = basename(path),
			text = as.character(text),
			brand = as.character(brand),
			source = as.character(source),
			product_line = as.character(product_line),
			rating = suppressWarnings(as.numeric(rating)),
			date = suppressWarnings(lubridate::as_date(date))
		) %>%
		filter(!is.na(text), str_trim(text) != "") %>%
		select(file_name, source, brand, product_line, rating, date, text, everything())
}

read_one_txt <- function(path) {
	tibble(
		file_name = basename(path),
		source = tools::file_path_sans_ext(basename(path)),
		brand = NA_character_,
		product_line = NA_character_,
		rating = NA_real_,
		date = as.Date(NA),
		text = readr::read_file(path)
	)
}

raw_text <- bind_rows(
	purrr::map_dfr(csv_files, read_one_csv),
	purrr::map_dfr(txt_files, read_one_txt)
) %>%
	mutate(
		doc_id = row_number(),
		source = str_to_lower(source),
		brand = case_when(
			str_detect(str_to_lower(brand), "nike") ~ "Nike",
			str_detect(str_to_lower(brand), "adidas") ~ "Adidas",
			str_detect(str_to_lower(brand), "under\\s*armour|under\\s*armor") ~ "Under Armour",
			TRUE ~ coalesce(brand, "Unknown")
		)
	)

raw_text %>% count(source, sort = TRUE)
```

## 4. Text Preprocessing and Feature Engineering

```{r preprocess}
custom_stop <- c(
	"nike", "adidas", "under", "armour", "armor", "shoe", "shoes",
	"just", "really", "also", "would", "could", "im", "ive", "dont"
)

all_stop <- unique(c(
	tidytext::stop_words$word,
	stopwords::stopwords("en"),
	custom_stop
))

tokens <- raw_text %>%
	select(doc_id, source, brand, product_line, rating, date, text) %>%
	unnest_tokens(word, text) %>%
	filter(str_detect(word, "^[a-z]+$")) %>%
	filter(!word %in% all_stop) %>%
	mutate(stem = SnowballC::wordStem(word, language = "en"))

tokens %>%
	count(stem, sort = TRUE) %>%
	slice_head(n = 20)
```

### 4.1 N-grams (bi-grams)

```{r bigrams}
bigrams <- raw_text %>%
	select(doc_id, source, brand, product_line, rating, text) %>%
	unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
	separate(bigram, into = c("w1", "w2"), sep = " ") %>%
	filter(!w1 %in% all_stop, !w2 %in% all_stop) %>%
	filter(str_detect(w1, "^[a-z]+$"), str_detect(w2, "^[a-z]+$")) %>%
	unite("bigram", w1, w2, sep = " ")

bigrams %>%
	count(brand, bigram, sort = TRUE) %>%
	group_by(brand) %>%
	slice_head(n = 12)
```

### 4.2 Document-Term Matrix

```{r dtm}
dtm_input <- tokens %>% count(doc_id, stem, sort = FALSE)
dtm <- dtm_input %>% cast_dtm(document = doc_id, term = stem, value = n)

dtm
```

## 5. Sentiment and Emotion Analysis (NRC and Bing)

```{r sentiment-lexicons}
nrc <- tidytext::get_sentiments("nrc")
bing <- tidytext::get_sentiments("bing")

nrc_emotion <- tokens %>%
	inner_join(nrc, by = "word") %>%
	filter(!sentiment %in% c("positive", "negative")) %>%
	count(brand, sentiment, sort = TRUE)

ggplot(nrc_emotion, aes(x = reorder(sentiment, n), y = n, fill = brand)) +
	geom_col(position = "dodge") +
	coord_flip() +
	labs(
		title = "Emotion Breakdown by Brand (NRC)",
		x = "Emotion",
		y = "Token Count"
	)
```

```{r sentiment-by-segment}
sentiment_scored <- tokens %>%
	inner_join(bing, by = "word") %>%
	mutate(score = if_else(sentiment == "positive", 1L, -1L)) %>%
	group_by(doc_id, brand, product_line, source) %>%
	summarise(sentiment_score = sum(score), .groups = "drop")

sentiment_scored %>%
	group_by(brand) %>%
	summarise(
		avg_sentiment = mean(sentiment_score, na.rm = TRUE),
		docs = n(),
		.groups = "drop"
	) %>%
	arrange(avg_sentiment)
```

## 6. Topic Modeling (LDA)

```{r lda-model}
non_sparse <- dtm

lda_k <- 6
if (nrow(non_sparse) < lda_k || ncol(non_sparse) < lda_k) {
	stop("Not enough documents/terms for LDA. Add more text data or reduce lda_k.")
}

lda_fit <- topicmodels::LDA(non_sparse, k = lda_k, control = list(seed = 42))

topic_terms <- tidytext::tidy(lda_fit, matrix = "beta") %>%
	group_by(topic) %>%
	slice_max(beta, n = 10) %>%
	ungroup()

ggplot(topic_terms, aes(x = reorder_within(term, beta, topic), y = beta, fill = factor(topic))) +
	geom_col(show.legend = FALSE) +
	scale_x_reordered() +
	coord_flip() +
	facet_wrap(~topic, scales = "free_y") +
	labs(
		title = "Top Terms by Topic (LDA)",
		x = "Term",
		y = "Beta"
	)
```

```{r topic-interpretation}
doc_topics <- tidytext::tidy(lda_fit, matrix = "gamma") %>%
	group_by(document) %>%
	slice_max(gamma, n = 1) %>%
	ungroup() %>%
	rename(doc_id = document, dominant_topic = topic, topic_prob = gamma) %>%
	mutate(doc_id = as.integer(doc_id))

topic_by_brand <- raw_text %>%
	select(doc_id, brand, product_line, source) %>%
	left_join(doc_topics, by = "doc_id") %>%
	count(brand, dominant_topic, sort = TRUE)

topic_by_brand
```

## 7. Business-Driven Method 1: TF-IDF Brand Differentiation

```{r tfidf-brand}
tfidf_brand <- tokens %>%
	count(brand, stem, sort = FALSE) %>%
	bind_tf_idf(term = stem, document = brand, n = n) %>%
	group_by(brand) %>%
	slice_max(tf_idf, n = 12) %>%
	ungroup()

ggplot(tfidf_brand, aes(x = reorder_within(stem, tf_idf, brand), y = tf_idf, fill = brand)) +
	geom_col(show.legend = FALSE) +
	scale_x_reordered() +
	coord_flip() +
	facet_wrap(~brand, scales = "free_y") +
	labs(
		title = "Brand Differentiation Terms (TF-IDF)",
		x = "Term",
		y = "TF-IDF"
	)
```

## 8. Business-Driven Method 2: Keyword Co-Occurrence Network

```{r network}
pair_counts <- raw_text %>%
	select(doc_id, text) %>%
	unnest_tokens(word, text) %>%
	filter(str_detect(word, "^[a-z]+$"), !word %in% all_stop) %>%
	pairwise_count(word, doc_id, sort = TRUE, upper = FALSE)

top_pairs <- pair_counts %>% filter(n >= quantile(n, 0.97, na.rm = TRUE))

if (nrow(top_pairs) > 1) {
	graph <- top_pairs %>%
		graph_from_data_frame(directed = FALSE)

	ggraph(graph, layout = "fr") +
		geom_edge_link(aes(width = n), alpha = 0.3, color = "gray40") +
		geom_node_point(size = 4, color = "steelblue") +
		geom_node_text(aes(label = name), repel = TRUE, size = 3.5) +
		scale_edge_width(range = c(0.2, 2)) +
		labs(title = "High-Strength Keyword Co-Occurrence Network")
}
```

## 9. Optional Advanced Challenge: Classification of Low Ratings

This model runs only if a numeric rating field is available.

```{r classification}
clf_data <- raw_text %>%
	filter(!is.na(rating), rating >= 1, rating <= 5) %>%
	mutate(target = case_when(
		rating <= 2 ~ "low_1_2",
		rating == 3 ~ "mid_3",
		rating >= 4 ~ "high_4_5"
	))

if (nrow(clf_data) >= 100) {
	clf_tokens <- clf_data %>%
		select(doc_id, target, text) %>%
		unnest_tokens(word, text) %>%
		filter(str_detect(word, "^[a-z]+$"), !word %in% all_stop) %>%
		mutate(word = SnowballC::wordStem(word))

	top_terms <- clf_tokens %>%
		count(word, sort = TRUE) %>%
		slice_head(n = 1500) %>%
		pull(word)

	x_mat <- clf_tokens %>%
		filter(word %in% top_terms) %>%
		count(doc_id, word) %>%
		cast_sparse(doc_id, word, n)

	y_lookup <- clf_data %>%
		distinct(doc_id, target)

	y <- y_lookup %>%
		filter(doc_id %in% as.integer(rownames(x_mat))) %>%
		arrange(match(doc_id, as.integer(rownames(x_mat)))) %>%
		pull(target)

	cv_fit <- cv.glmnet(
		x = x_mat,
		y = y,
		family = "multinomial",
		type.measure = "class",
		alpha = 1
	)

	pred <- predict(cv_fit, newx = x_mat, s = "lambda.min", type = "class") %>%
		as.vector()

	tibble(truth = y, estimate = pred) %>%
		yardstick::metrics(truth = truth, estimate = estimate)
}
```

## 10. Findings and Strategic Recommendations

Replace the bracketed notes with your actual results.

1. Brand perception: [Summarize Nike emotional profile vs competitors from NRC/Bing output.]
2. Product strategy: [State top complaint topics and affected product lines.]
3. Sustainability narrative: [Report whether trust or skepticism dominates sustainability terms.]
4. Pricing sensitivity: [Quantify association between price terms and negative sentiment.]
5. Competitive positioning: [Explain differentiating TF-IDF language by brand.]
6. Growth opportunities: [Highlight high-engagement language, segments, or product lines.]

## 11. Limitations and Risk Controls

1. Sampling bias: Sources may overrepresent vocal users or specific geographies.
2. Fake/manipulated reviews: Lexicon and topic methods cannot reliably identify coordinated manipulation.
3. Lexicon bias: Dictionary sentiment can miss sarcasm and domain-specific context.
4. Overfitting risk: Classification performance must be evaluated with holdout validation in final submission.
5. Ethical usage: Remove personal identifiers and comply with platform terms of service.

## 12. Appendix: Session Info

```{r session-info}
sessionInfo()
```
