---
title: "A2: Nike Text Analytics & Classification Modeling"
author: "Team 6"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
format:
    html:
        theme: 
            light: flatly
            dark: darkly
        highlight-style: github
        code-fold: true
        code-tools: 
            source: true
            toggle: true
        code-copy: true
        self-contained: true
        html-math-method: katex
        embed-resources: true
        code-overflow: wrap
        smooth-scroll: true       
        page-layout: full
        toc: true
        toc-location: right
        lightbox: true
---

```{r setup, include=FALSE}
# ──────────────────────────────────────────────────────────────
# 0. Package Management & Global Configuration
# ──────────────────────────────────────────────────────────────
required_pkgs <- c(
  # tidyverse & data wrangling
  "tidyverse", "lubridate", "stringr", "janitor", "scales",
  # rendering & tables
  "knitr", "kableExtra",
  # text mining & NLP
  "tidytext", "tm", "quanteda", "stopwords", "SnowballC", "textdata",
  "topicmodels", "widyr", "igraph", "ggraph",
  # modeling utilities
  "broom", "glmnet", "yardstick", "Matrix", "slam",
  # data I/O
  "jsonlite", "httr", "rappdirs",
  # plotting extras
  "RColorBrewer", "ggrepel", "patchwork"
)

missing <- required_pkgs[!vapply(required_pkgs, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing)) {
  message("Installing: ", paste(missing, collapse = ", "))
  install.packages(missing, repos = "https://cloud.r-project.org", dependencies = TRUE)
}

still_missing <- required_pkgs[!vapply(required_pkgs, requireNamespace, logical(1), quietly = TRUE)]
if (length(still_missing)) {
  warning("Could not install: ", paste(still_missing, collapse = ", "), ". Some sections may be skipped.")
}

invisible(lapply(required_pkgs, function(p) {
  tryCatch(suppressPackageStartupMessages(library(p, character.only = TRUE)),
           error = function(e) message(sprintf("Skipping '%s': %s", p, e$message)))
}))

set.seed(42)

knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 10,
  fig.height = 6,
  fig.align  = "center",
  dpi        = 150
)

# ── Tunable parameters ───────────────────────────────────────
LDA_K            <- 3       # number of executive topic segments
MIN_TERM_FREQ    <- 5       # floor for "rare but recurring" terms
MIN_DOC_COUNT    <- 3       # minimum docs before including a group
TOP_N_TERMS      <- 15      # default top terms / bigrams to show
BOTOM_N_TERMS    <- 15      # default top terms / bigrams to show
COOCCUR_MIN_FREQ <- 5       # min doc frequency for co-occurrence
COOCCUR_MIN_CORR <- 0.20    # min correlation for network edges
COOCCUR_MAX_EDGES <- 80     # cap edges in network plot
LDA_SPARSITY     <- 0.995   # removeSparseTerms threshold

# ── Global theme & palettes ──────────────────────────────────
theme_nike <- theme_minimal(base_size = 13) +
  theme(
    plot.title       = element_text(face = "bold", size = 15),
    plot.subtitle    = element_text(color = "grey40", size = 11),
    strip.text       = element_text(face = "bold"),
    legend.position  = "bottom",
    panel.grid.minor = element_blank()
  )
theme_set(theme_nike)

nike_accent    <- "#F46B2F"
brand_colors   <- c("Nike" = nike_accent, "Adidas" = "#1D1D1B", "Under Armour" = "#003DA5")
source_levels  <- c("Reddit", "YouTube", "Unknown")
source_colors  <- c("Reddit" = "#4E79A7", "YouTube" = "#E15759", "Unknown" = "#76B7B2")
lexicon_colors <- c("AFINN" = nike_accent, "Bing" = "#4E79A7", "NRC" = "#59A14F")
vocab_palette  <- c("Sustainability" = "#2E8B57", "Greenwashing" = "#B22222")
topic_palette  <- setNames(c("#F28E2B", "#4E79A7", "#59A14F", "#E15759", "#76B7B2", "#EDC948"),
                           as.character(1:6))
topic_segment_palette <- c(
  "Core complaint themes"           = "#B22222",
  "Product differentiation themes"  = nike_accent,
  "Emerging brand risks"            = "#4E79A7"
)

# ── Reusable scale helpers ───────────────────────────────────
scale_fill_brand   <- function(...) scale_fill_manual(values = brand_colors, ...)
scale_fill_source  <- function(...) scale_fill_manual(values = source_colors, breaks = source_levels, drop = TRUE, ...)
scale_fill_lexicon <- function(...) scale_fill_manual(values = lexicon_colors, ...)
scale_fill_topic   <- function(...) scale_fill_manual(values = topic_palette, ...)

# ──────────────────────────────────────────────────────────────
# Helper Functions (defined once, reused everywhere)
# ──────────────────────────────────────────────────────────────

#' Normalize source labels to Reddit / YouTube / Unknown
normalize_source <- function(source) {
  s <- str_to_lower(coalesce(source, "unknown"))
  case_when(str_detect(s, "reddit") ~ "Reddit",
            str_detect(s, "youtube") ~ "YouTube",
            TRUE ~ "Unknown")
}

#' Read a term list from a URL or local path.
#' Strips comments, splits on comma/semicolon, and optionally stems.
read_terms <- function(url, label, stem = FALSE) {
  raw <- tryCatch(readr::read_lines(url, progress = FALSE),
                  error = function(e) stop(sprintf("Failed to load %s from '%s': %s", label, url, e$message)))
  terms <- raw %>%
    str_replace_all("#.*$", "") %>%
    str_split("[,;]") %>%
    purrr::flatten_chr() %>%
    str_trim() %>%
    purrr::discard(~ .x == "")
  if (!length(terms)) stop(sprintf("Terms file for %s is empty: %s", label, url))
  terms <- tolower(terms)
  if (stem) terms <- SnowballC::wordStem(terms, language = "en")
  unique(terms)
}

#' Read Nike product segments from a two-column CSV.
read_product_segments <- function(url) {
  product_segments <- tryCatch(
    readr::read_csv(url, show_col_types = FALSE),
    error = function(e) stop(sprintf("Failed to load Nike product segments from '%s': %s", url, e$message))
  )

  required_cols <- c("category", "product")
  missing_cols <- setdiff(required_cols, names(product_segments))
  if (length(missing_cols)) {
    stop(sprintf("Nike product segments CSV is missing columns: %s", paste(missing_cols, collapse = ", ")))
  }

  product_segments %>%
    transmute(
      category = str_squish(category),
      product = str_squish(product)
    ) %>%
    filter(category != "", product != "")
}

#' Build bigrams from a text tibble, removing stopwords but preserving negation.
build_bigrams <- function(df, stop_words_vec, min_word_len = 2) {
  negation_keep <- c("no", "not", "nor", "never")
  sw <- tibble(word = setdiff(stop_words_vec, negation_keep))
  pat <- sprintf("^[a-z]{%d,}$", min_word_len)
  df %>%
    select(doc_id, text) %>%
    distinct() %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, into = c("w1", "w2"), sep = " ", remove = FALSE) %>%
    filter(!is.na(w1), !is.na(w2),
           str_detect(w1, pat), str_detect(w2, pat)) %>%
    anti_join(sw, by = c("w1" = "word")) %>%
    anti_join(sw, by = c("w2" = "word"))
}

#' Tokenize text with shared stopword list; returns word + stem columns.
tokenize_text <- function(df, stop_words_vec) {
  df %>%
    select(doc_id, source, brand, product_line, rating, date, text) %>%
    unnest_tokens(word, text) %>%
    filter(str_detect(word, "^[a-z]{2,}$"), !word %in% stop_words_vec) %>%
    mutate(word = if_else(word == "nmds", "nmd", word),
           stem = SnowballC::wordStem(word, language = "en"),
           stem = if_else(stem == "nmds", "nmd", stem))
}

# ── Pre-cache textdata lexicons for non-interactive render ───
ensure_textdata_lexicon <- function(data_name, rds_name) {
  if (!requireNamespace("textdata", quietly = TRUE)) return(FALSE)
  cache_dir <- file.path(rappdirs::user_cache_dir("textdata"), data_name)
  rds_path  <- file.path(cache_dir, rds_name)
  if (file.exists(rds_path)) return(TRUE)
  dir.create(cache_dir, recursive = TRUE, showWarnings = FALSE)
  tryCatch({
    if (!length(list.files(cache_dir))) textdata:::download_functions[[data_name]](cache_dir)
    textdata:::process_functions[[data_name]](cache_dir, rds_path)
    TRUE
  }, error = function(e) {
    message(sprintf("Could not pre-cache '%s': %s", data_name, e$message))
    FALSE
  })
}

if (!interactive()) {
  invisible(ensure_textdata_lexicon("nrc", "NRCWordEmotion.rds"))
  invisible(ensure_textdata_lexicon("bing", "bing.rds"))
}

#' Load AFINN-111 lexicon directly from GitHub.
load_afinn_lexicon <- function() {
  tryCatch(
    readr::read_tsv("https://raw.githubusercontent.com/fnielsen/afinn/master/afinn/data/AFINN-111.txt",
                    col_names = c("word", "value"), show_col_types = FALSE, progress = FALSE),
    error = function(e) { message("AFINN unavailable: ", e$message); tibble(word = character(), value = numeric()) }
  )
}

#' Safe lexicon loader — returns an empty tibble on failure.
safe_get_sentiments <- function(lexicon) {
  tryCatch(tidytext::get_sentiments(lexicon), error = function(e) {
    message(sprintf("%s lexicon unavailable: %s", lexicon, e$message))
    tibble(word = character(), sentiment = character())
  })
}

#' Placeholder plot when a lexicon or data source is unavailable.
placeholder_plot <- function(msg) {
  ggplot() + annotate("text", x = 0, y = 0, label = msg, size = 5, color = "grey50") + theme_void()
}
```

# 1. Business Context and Analytical Focus

Nike’s brand equity is shaped not only by its products and campaigns, but also by how consumers discuss the brand across public digital channels. Unstructured text provides a useful view of those perceptions, especially in areas where sentiment, trust, and consumer expectations are changing quickly.

This analysis focuses on three strategic themes: sustainability perception, pricing sensitivity, and competitive positioning. Based on these themes, the work was organized around four business questions:

1.  How is Nike emotionally positioned in online conversations?
2.  What complaints are driving negative reviews in specific product lines?
3.  Is Nike’s sustainability messaging resonating with consumers, or is greenwashing language appearing?
4.  Are customers increasingly describing Nike as overpriced?

Together, these questions help assess where brand strength is being reinforced and where reputational or product-related pressure may be emerging.

------------------------------------------------------------------------

# 2. Data Collection and Scope

The analysis used consumer-generated text from two public digital channels: Reddit and YouTube. These sources were selected because they capture different types of brand conversation. Reddit tends to contain longer and more detailed discussion, while YouTube comments reflect faster reactions to reviews, comparisons, and brand-related content.

The dataset included Nike, Adidas, and Under Armour. Nike was the primary focus, while Adidas and Under Armour were included to provide competitive context. Reddit data was collected from active footwear and sport-related communities, including r/Sneakers, r/RunningShoeGeeks, r/Running, r/BasketballShoes, and r/TrailRunning, as well as brand-specific subreddits when available. YouTube data was collected using search terms related to reviews, sustainability, pricing, and brand comparisons across 2025 and 2026.

The collection approach was broad at the brand level, and thematic filtering was applied later during the analysis. Each record represents a text document from one of the two platforms. Channel comparison was included intentionally, since the tone, depth, and style of discussion differ across Reddit and YouTube.

Text preparation at this stage was kept relatively simple. Standard tidytext stop words were used together with custom stop words to remove platform-specific and low-value terms. No major duplication issue was identified during preparation, and no additional language filtering was applied.

------------------------------------------------------------------------

# 3. Data Preparation and Analytical Method

After combining the Reddit and YouTube datasets, the text was cleaned and standardized for analysis. The preparation process included tokenization at the word level, removal of standard and custom stop words, and stemming to reduce related word forms to a common root. Bigrams were also created in selected sections to preserve phrase-level context where single words were too broad to be informative.

The analysis used several complementary NLP techniques. Frequency analysis was used to identify recurring language patterns across brands and channels. Sentiment analysis was conducted using the Bing, NRC, and AFINN lexicons to compare emotional tone across Nike, Adidas, and Under Armour. TF-IDF was used to identify terms that were more distinctive to each brand rather than simply common across the full corpus.

To address the core business questions more directly, the analysis also used targeted term lists related to sustainability, greenwashing, and pricing. These allowed the work to move beyond general sentiment and examine how specific issues were being discussed. Topic modeling was then applied to the Nike corpus to identify broader themes that were not fully visible through term frequency or lexicon-based sentiment alone.

Together, these methods provided a practical and interpretable analytical framework. The goal was not technical complexity for its own sake, but a defensible set of text analytics tools that could support clear business insight.

```{r load-csv-data, echo=FALSE}
# ── GitHub raw URLs ──────────────────────────────────────────
gh_base <- "https://raw.githubusercontent.com/renan-peres/mban-unstructured-data/refs/heads/main/%23A2%20-%20Nike%20Text%20Analytics%20(N-Aible%20Simulator)/data"

urls <- list(
  reddit        = paste0(gh_base, "/reddit_comments.csv"),
  youtube       = paste0(gh_base, "/youtube_comments.csv"),
  stopwords     = paste0(gh_base, "/custom_stopwords.txt"),
  sustain       = paste0(gh_base, "/sustainability_terms.txt"),
  greenwash     = paste0(gh_base, "/greenwashing_terms.txt"),
  product_lines = paste0(gh_base, "/nike_product_segments.csv")
)

# ── Load CSVs with fallback ──────────────────────────────────
load_csv_safe <- function(url, label) {
  tryCatch(read_csv(url, show_col_types = FALSE),
           error = function(e) { cat(sprintf("  %s CSV failed: %s\n", label, e$message)); NULL })
}

source_frames <- list()

reddit_df <- load_csv_safe(urls$reddit, "Reddit")
if (!is.null(reddit_df)) {
  source_frames[["reddit"]] <- reddit_df
  cat(sprintf("✓ Reddit: %s rows\n", format(nrow(reddit_df), big.mark = ",")))
}

youtube_df <- load_csv_safe(urls$youtube, "YouTube")
if (!is.null(youtube_df)) {
  source_frames[["youtube"]] <- youtube_df
  cat(sprintf("✓ YouTube: %s rows\n", format(nrow(youtube_df), big.mark = ",")))
}

if (!length(source_frames)) stop("No data loaded -- check URLs or connectivity.")

# ── Load external term lists ─────────────────────────────────
sustainability_terms      <- read_terms(urls$sustain, "sustainability terms", stem = TRUE)
greenwash_terms           <- read_terms(urls$greenwash, "greenwashing terms", stem = TRUE)
nike_product_segments     <- read_product_segments(urls$product_lines)
```

```{r build-master-dataset, echo=FALSE}
raw_text <- bind_rows(source_frames) %>%
  select(any_of(c("text", "rating", "source", "brand", "doc_id"))) %>%
  mutate(
    doc_id       = row_number(),
    source       = factor(normalize_source(source), levels = source_levels),
    brand        = case_when(
      str_detect(str_to_lower(coalesce(brand, "")), "nike")             ~ "Nike",
      str_detect(str_to_lower(coalesce(brand, "")), "adidas")           ~ "Adidas",
      str_detect(str_to_lower(coalesce(brand, "")), "under\\s*armou?r") ~ "Under Armour",
      TRUE ~ coalesce(brand, "Unknown")
    ),
    product_line = NA_character_,
    date         = as.Date(NA),
    rating       = suppressWarnings(as.numeric(rating)),
    text         = str_squish(text)
  ) %>%
  filter(!is.na(text), nchar(text) > 10)

cat(sprintf("Master dataset: %s documents across %d sources and %d brands.\n",
            format(nrow(raw_text), big.mark = ","),
            n_distinct(raw_text$source),
            n_distinct(raw_text$brand)))

# ── Build shared stopword set (once) ─────────────────────────
custom_stop <- read_terms(urls$stopwords, "custom stopwords", stem = FALSE)
all_stop    <- unique(c(tidytext::stop_words$word, stopwords::stopwords("en"), custom_stop))
```

```{r analysis-primitives, echo=FALSE}
# ── Shared tokenization (used across every section) ──────────
tokens <- tokenize_text(raw_text, all_stop)

# ── Bing lexicon & document-level sentiment ──────────────────
bing <- safe_get_sentiments("bing")
if (!nrow(bing)) stop("Bing lexicon is required. Run once with internet to populate the textdata cache.")

sentiment_scored <- tokens %>%
  inner_join(bing, by = "word") %>%
  mutate(score = if_else(sentiment == "positive", 1L, -1L)) %>%
  group_by(doc_id, brand, product_line, source, rating) %>%
  summarise(sentiment_score = sum(score), .groups = "drop")

cat(sprintf("Shared objects: %s tokens and %s sentiment-scored documents.\n",
            format(nrow(tokens), big.mark = ","),
            format(nrow(sentiment_scored), big.mark = ",")))
```

```{r shared-derived-objects, echo=FALSE}
# ── Nike subsets ─────────────────────────────────────────────
nike_text <- raw_text %>% filter(brand == "Nike")
if (!nrow(nike_text)) stop("No Nike documents found after brand normalization.")
nike_tokens <- tokens %>% filter(brand == "Nike")

# ── Price terms & document flags (all brands) ────────────────
price_terms <- c(
  "expensive", "pricey", "overpriced", "ripoff", "scam", "markup", "costly",
  "retail", "standard", "msrp", "normal", "base", "average", "regular",
  "cheap", "affordable", "deal", "steal", "discount", "sale", "budget"
)

price_doc_flags <- tokens %>%
  group_by(doc_id, brand) %>%
  summarise(has_price_mention = any(stem %in% price_terms), .groups = "drop")

# ── Nike product-line document mapping ───────────────────────
nike_product_lookup <- nike_product_segments %>%
  mutate(product_id = row_number()) %>%
  unnest_tokens(segment_token, product, drop = FALSE) %>%
  filter(str_detect(segment_token, "^[a-z]{2,}$")) %>%
  mutate(stem = SnowballC::wordStem(segment_token, language = "en")) %>%
  distinct(product_id, category, product, stem) %>%
  add_count(product_id, name = "product_token_count")

nike_doc_product_matches <- nike_tokens %>%
  select(doc_id, stem) %>%
  distinct() %>%
  inner_join(nike_product_lookup, by = "stem") %>%
  count(doc_id, product_id, category, product, product_token_count, name = "matched_tokens") %>%
  mutate(match_share = matched_tokens / product_token_count) %>%
  filter(matched_tokens >= 2 | match_share >= 0.5)

nike_doc_product_lines <- nike_doc_product_matches %>%
  group_by(doc_id) %>%
  arrange(desc(match_share), desc(matched_tokens), product) %>%
  slice_head(n = 1) %>%
  ungroup() %>%
  transmute(doc_id, product_line = product)

# ── Nike term frequency (for baseline plots) ─────────────────
nike_term_frequency <- nike_tokens %>% count(stem, sort = TRUE)

nike_doc_categories <- nike_doc_product_matches %>%
  count(doc_id, category, wt = matched_tokens, name = "match_count") %>%
  group_by(doc_id) %>%
  slice_max(match_count, n = 1, with_ties = FALSE) %>%
  ungroup()

# ── Sustainability / greenwashing flags (all brands) ─────────
sus_flagged <- tokens %>%
  mutate(is_sustainability = stem %in% sustainability_terms,
         is_greenwash      = stem %in% greenwash_terms) %>%
  group_by(doc_id, brand) %>%
  summarise(has_sustainability = any(is_sustainability),
            has_greenwash      = any(is_greenwash),
            .groups = "drop")

# ── Nike sustainability vocabulary profile ───────────────────
nike_vocab_sentiment <- bind_rows(
  nike_tokens %>% filter(stem %in% sustainability_terms) %>%
    count(word, stem, sort = TRUE) %>% mutate(Vocabulary = "Sustainability"),
  nike_tokens %>% filter(stem %in% greenwash_terms) %>%
    count(word, stem, sort = TRUE) %>% mutate(Vocabulary = "Greenwashing")
) %>%
  left_join(bing %>% select(word, sentiment), by = c("stem" = "word")) %>%
  mutate(sentiment = replace_na(sentiment, "Not labeled"))

# ── Nike sustainability bigrams ──────────────────────────────
nike_vocab_bigram <- nike_text %>%
  build_bigrams(all_stop) %>%
  mutate(
    stem1 = SnowballC::wordStem(w1, language = "en"),
    stem2 = SnowballC::wordStem(w2, language = "en"),
    Vocabulary = case_when(
      stem1 %in% sustainability_terms | stem2 %in% sustainability_terms ~ "Sustainability",
      stem1 %in% greenwash_terms | stem2 %in% greenwash_terms ~ "Greenwashing",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Vocabulary)) %>%
  count(Vocabulary, bigram, sort = TRUE)

# ── Product complaint objects ───────────────────────────
product_terms <- c(
  "size", "fit", "small", "big", "tight", "loose",
  "comfort", "comfortable", "uncomfortable",
  "quality", "material", "durable", "cheap",
  "sole", "design", "style", "color",
  "break", "tear", "wear", "support", "cushion"
)
product_terms_stem <- unique(SnowballC::wordStem(product_terms, language = "en"))

nike_product_docs   <- nike_tokens %>% filter(stem %in% product_terms_stem) %>% distinct(doc_id)
nike_product_text   <- nike_text %>% filter(doc_id %in% nike_product_docs$doc_id)
nike_product_tokens <- nike_product_text %>%
  select(doc_id, text) %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "^[a-z]{2,}$"), !word %in% all_stop) %>%
  mutate(stem = SnowballC::wordStem(word, language = "en"))

nike_product_negative <- nike_product_tokens %>%
  inner_join(bing, by = "word") %>%
  filter(sentiment == "negative") %>%
  count(stem, sort = TRUE)

product_sentiment_by_term <- nike_product_tokens %>%
  inner_join(bing, by = "word") %>%
  filter(stem %in% product_terms_stem) %>%
  group_by(stem) %>%
  summarise(score = sum(if_else(sentiment == "positive", 1L, -1L)),
            mentions = n(), .groups = "drop") %>%
  arrange(score, desc(mentions))

nike_low_sentiment_docs <- sentiment_scored %>%
  filter(brand == "Nike", sentiment_score < 0) %>%
  select(doc_id, sentiment_score)

nike_complaint_bigrams <- nike_text %>%
  select(doc_id, text) %>%
  inner_join(nike_low_sentiment_docs %>% select(doc_id), by = "doc_id") %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, into = c("word1", "word2"), sep = " ", remove = FALSE) %>%
  filter(!is.na(word1), !is.na(word2),
         str_detect(word1, "^[a-z]{2,}$"), str_detect(word2, "^[a-z]{2,}$")) %>%
  anti_join(tibble(word = setdiff(all_stop, c("no", "not", "nor", "never"))),
            by = c("word1" = "word")) %>%
  anti_join(tibble(word = setdiff(all_stop, c("no", "not", "nor", "never"))),
            by = c("word2" = "word")) %>%
  filter(str_detect(bigram, "break|cheap|hurt|tear|tight|small|uncomfort|wear")) %>%
  count(bigram, sort = TRUE)

# ── Top terms in positive vs negative Nike docs ──────────────
nike_pos_neg_words <- nike_tokens %>%
  inner_join(sentiment_scored %>% filter(brand == "Nike") %>% select(doc_id, sentiment_score),
             by = "doc_id") %>%
  mutate(group = if_else(sentiment_score > 0, "Positive", "Negative")) %>%
  count(group, stem) %>%
  group_by(group) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup()

cat(sprintf(
  "Shared Nike objects ready: %s Nike docs, %s Nike tokens, %s sustainability bigrams, %s complaint-focused docs.\n",
  format(nrow(nike_text), big.mark = ","),
  format(nrow(nike_tokens), big.mark = ","),
  format(nrow(nike_vocab_bigram), big.mark = ","),
  format(nrow(nike_product_docs), big.mark = ",")
))
```

```{r data-summary-table}
raw_text %>%
  group_by(Brand = brand, Source = source) %>%
  summarise(Documents = n(), `Avg Length` = round(mean(nchar(text)), 0), .groups = "drop") %>%
  arrange(Brand, desc(Documents)) %>%
  kable(caption = "Data Composition by Brand and Source") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r brand-volume-plot, fig.height=5}
raw_text %>%
  count(brand, source) %>%
  ggplot(aes(x = reorder(brand, -n), y = n, fill = source)) +
  geom_col(alpha = 0.85) +
  scale_fill_source() +
  labs(title = "Documents by Brand and Source",
       subtitle = "Collected via 00_data_collection.R (Reddit + YouTube APIs)",
       x = NULL, y = "Documents", fill = "Source")
```

Nike has the largest document volume across both sources, followed by Adidas and then Under Armour. The mix by source also differs by brand: Nike’s dataset is more Reddit-heavy, while Adidas and Under Armour are relatively more balanced across Reddit and YouTube. This matters analytically because source mix can influence tone, language style, and the level of detail in the discussion.

------------------------------------------------------------------------

# 4. Nike Baseline Analysis

Before comparing across brands, we run a focused Nike-only pass to understand the single-brand landscape: term frequencies, bigrams, emotion profile, topics, and keyword relationships.

```{r nike-baseline-summary, echo=FALSE}
cat(sprintf("Nike-only baseline: %s documents and %s cleaned tokens.\n",
            format(nrow(nike_text), big.mark = ","),
            format(nrow(nike_tokens), big.mark = ",")))
```

```{r nike-summary-table, echo=FALSE}
nike_text %>%
  group_by(Source = source) %>%
  summarise(Documents = n(),
            `Avg Length` = round(mean(nchar(text)), 0),
            `Avg Rating` = round(mean(rating, na.rm = TRUE), 2),
            .groups = "drop") %>%
  arrange(desc(Documents)) %>%
  kable(caption = "Nike Baseline by Source") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## 4.1 Top Frequent Terms

The bar chart below shows the most common stemmed terms in Nike documents. Product-related stems like "shoe," "run," and "air" dominate as expected; watch for quality- or complaint-related stems mixed in.

```{r nike-top-terms, fig.height=5}
nike_term_frequency %>%
  slice_head(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(stem, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.85) +
  coord_flip() +
  labs(title = "Nike: Top 15 Stemmed Terms",
       subtitle = "Core conversation themes in Nike-only documents",
       x = "Stem", y = "Frequency")

```

*Top Frequent Terms Interpretation:* Nike’s most frequent terms suggest that the conversation is centered primarily on footwear, especially running, trail, and well-known product lines such as Vomero, Air, and Jordan. Terms such as “size,” “wear,” and “buy” also indicate that the discussion is strongly tied to product experience and purchase behavior. However, because these are stemmed single-word frequencies, they are more useful for directional context than for identifying specific drivers of sentiment.

## 4.2 Bigrams

Bigrams capture two-word pairings that unigrams miss -- product names ("air force"), quality descriptors ("runs small"), and brand signals ("nike dunk").

```{r nike-bigrams, fig.height=5}
nike_bigrams <- nike_text %>%
  build_bigrams(all_stop) %>%
  unite("bigram", w1, w2, sep = " ")

nike_bigrams %>%
  count(bigram, sort = TRUE) %>%
  slice_head(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(bigram, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.85) +
  coord_flip() +
  labs(title = "Nike: Top 15 Bigrams",
       subtitle = "Common phrase pairings in Nike conversations",
       x = "Bigram", y = "Frequency")
```

*Top Frequent Bigrams Interpretation:*Nike’s most frequent bigrams show that the conversation is concentrated around footwear, especially specific product lines such as Air Max, Zoom Fly, Pegasus Premium, Vomero Premium, and Air Jordan. The language also reflects a strong running and trail context, with phrases such as “trail running” and “half marathon.” In addition, terms such as “toe box,” “ankle support,” and “half size” suggest that fit and performance features are recurring themes in the discussion. As a result, the Nike conversation appears to be driven more by product-level usage and evaluation than by broad brand-level commentary.

```{r nike-bigrams-bottom, fig.height=5}
nike_bigrams %>%
  count(bigram, sort = TRUE) %>%
  filter(n >= 10) %>% 
  slice_tail(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(bigram, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.85) +
  coord_flip() +
  labs(title = "Nike: Lowest Frequecy Bigrams",
       subtitle = "Common phrase pairings in Nike conversations",
       x = "Bigram", y = "Frequency")
```

*Least Frequent Terms Interpretation:* Even the lower-frequency recurring bigrams remain concentrated around product use, fit, and running-specific contexts. Terms such as “wide feet,” “daily trainer,” “road running,” and “pegasus trail” suggest that smaller Nike conversations still revolve around functional product needs rather than generic brand discussion. While these themes are too niche to treat as major findings on their own, they help identify specialized areas of consumer interest that may warrant closer review.

## 4.3 Lexicon Sentiment Snapshot

We compare three sentiment lexicons on the same Nike token corpus. When all three point in the same direction, we can be more confident the signal is real and not an artifact of any single dictionary.

```{r nike-nrc-emotions, fig.height=5}
nrc <- safe_get_sentiments("nrc")

if (!nrow(nrc)) {
  nike_nrc_pct <- tibble(sentiment = character(), n = integer(), pct = numeric())
  placeholder_plot("NRC lexicon unavailable")
} else {
  nike_nrc_pct <- nike_tokens %>%
    inner_join(nrc, by = "word") %>%
    filter(!sentiment %in% c("positive", "negative")) %>%
    count(sentiment, sort = TRUE) %>%
    mutate(pct = 100 * n / sum(n))

  ggplot(nike_nrc_pct, aes(x = reorder(sentiment, pct), y = pct)) +
    geom_col(fill = nike_accent, alpha = 0.85) +
    coord_flip() +
    labs(title = "Nike Emotion Profile (NRC)",
         subtitle = "Share of emotion-tagged tokens in Nike documents",
         x = "Emotion", y = "% of Emotion Tokens")
}
```

Trust and anticipation lead Nike's emotion profile, a positive signal reflecting brand credibility and product excitement. However joy and surprise, the emotions most associated with genuine brand delight, are the weakest positive signals. Meanwhile fear, sadness and anger collectively account for nearly a third of all emotion tokens. The overall picture is a brand that consumers respect and follow, but do not passionately celebrate.

```{r nike-lexicon-comparison, fig.height=5}
afinn_lex <- load_afinn_lexicon()

afinn_compare <- nike_tokens %>%
  inner_join(afinn_lex, by = "word") %>%
  summarise(sentiment = sum(value, na.rm = TRUE)) %>%
  mutate(method = "AFINN")

bing_nrc_compare <- bind_rows(
  nike_tokens %>% inner_join(bing, by = "word") %>% mutate(method = "Bing"),
  nike_tokens %>%
    inner_join(nrc %>% filter(sentiment %in% c("positive", "negative")), by = "word") %>%
    mutate(method = "NRC")
) %>%
  count(method, sentiment, name = "n") %>%
  complete(method, sentiment = c("positive", "negative"), fill = list(n = 0)) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(sentiment = positive - negative)

lexicon_compare <- bind_rows(afinn_compare, bing_nrc_compare) %>%
  mutate(method = factor(method, levels = c("AFINN", "Bing", "NRC")))

ggplot(lexicon_compare, aes(method, sentiment, fill = method)) +
  geom_col(show.legend = FALSE, alpha = 0.9) +
  facet_wrap(~method, ncol = 1, scales = "free_y") +
  scale_fill_lexicon() +
  labs(title = "Nike Lexicon Comparison: AFINN vs Bing vs NRC",
       subtitle = "Net sentiment totals on the same Nike token set",
       x = NULL, y = "Net Sentiment")
```

All three lexicons point in the same positive direction, and that convergence matters. When independent measurement approaches agree, the finding is more defensible. However the magnitude tells a more cautious story. AFINN and NRC show larger positive scores, but both are sensitive to emotional and expressive vocabulary, common in sneaker communities. Bing, our most conservative measure, returns a modest positive margin across nearly 5,000 documents. That is less than one net positive word per document, positive, but barely so.

## 4.4 Keyword Co-occurrence Network

The network below shows which terms tend to appear together in the same Nike documents. Thicker edges indicate stronger co-occurrence; larger nodes indicate higher degree centrality (more connections).

```{r cooccurrence-network, fig.height=8, fig.width=10}
pairwise_terms <- nike_tokens %>%
  select(doc_id, stem) %>%
  distinct() %>%
  add_count(stem, name = "doc_freq") %>%
  filter(doc_freq >= COOCCUR_MIN_FREQ)

pair_counts <- pairwise_terms %>%
  pairwise_cor(stem, doc_id, sort = TRUE, upper = FALSE)

top_pairs <- pair_counts %>%
  filter(correlation >= COOCCUR_MIN_CORR) %>%
  slice_head(n = COOCCUR_MAX_EDGES)

if (nrow(top_pairs) > 2) {
  graph <- graph_from_data_frame(top_pairs, directed = FALSE)
  V(graph)$centrality <- degree(graph)

  ggraph(graph, layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation, edge_width = correlation), color = "gray55") +
    geom_node_point(aes(size = centrality), color = nike_accent, alpha = 0.8) +
    geom_node_text(aes(label = name), repel = TRUE, size = 3.3, max.overlaps = 40) +
    scale_edge_alpha(range = c(0.15, 0.6), guide = "none") +
    scale_edge_width(range = c(0.2, 1.8), guide = "none") +
    scale_size_continuous(range = c(2.5, 7), guide = "none") +
    labs(title = "Nike Keyword Co-Occurrence Network",
         subtitle = "Edges = pairwise correlations across Nike documents") +
    theme_void() +
    theme(plot.title    = element_text(face = "bold", size = 15),
          plot.subtitle = element_text(color = "grey40", size = 11))
} else {
  cat("Not enough strongly correlated term pairs to build a network.\n")
}
```

*Co-occurrence Network Interpretation:* The co-occurrence network provides an exploratory view of how Nike-related terms appear together across documents. The strongest connections remain concentrated around product use, running contexts, and functional themes such as support, training, and specific product lines. However, the network is more useful for identifying possible thematic clusters than for supporting standalone conclusions, since many connections are low-frequency and fragmented.

## 4.5 Pricing Sentiment

Do comments that mention price-related language carry lower sentiment? The chart below filters to documents where a price term (e.g., "expensive," "deal," "overpriced") was detected, then compares average Bing sentiment across brands.

```{r nike-overpriced-language, fig.height=5}
# Terms that explicitly signal overpricing or poor value
overpriced_patterns <- c(
  "overpriced",
  "way overpriced",
  "too expensive",
  "very expensive",
  "so expensive",
  "priced too high",
  "price is too high",
  "price too high",
  "costs too much",
  "cost too much",
  "not worth it",
  "not worth the price",
  "not worth the money",
  "expensive for what it is",
  "ridiculous price",
  "absurd price",
  "crazy price",
  "way too expensive"
)

nike_overpriced_docs <- raw_text %>%
  filter(brand == "Nike") %>%
  mutate(
    text_lower = str_to_lower(text),
    has_price_mention = str_detect(
      text_lower,
      "price|priced|cost|costs|expensive|cheap|value|worth|afford|premium"
    ),
    has_overpriced_mention = str_detect(
      text_lower,
      str_c(overpriced_patterns, collapse = "|")
    )
  )

nike_overpriced_summary <- nike_overpriced_docs %>%
  summarise(
    total_nike_docs = n(),
    price_docs = sum(has_price_mention, na.rm = TRUE),
    overpriced_docs = sum(has_overpriced_mention, na.rm = TRUE),
    pct_overpriced_all = mean(has_overpriced_mention, na.rm = TRUE),
    pct_overpriced_within_price = mean(has_overpriced_mention[has_price_mention], na.rm = TRUE)
  )

nike_overpriced_plot <- tibble(
  metric = "Nike price-mentioned comments",
  perception = c("Thinks it is overpriced", "Does not think it is overpriced"),
  pct = c(
    nike_overpriced_summary$pct_overpriced_within_price,
    1 - nike_overpriced_summary$pct_overpriced_within_price
  )
)

ggplot(nike_overpriced_plot, aes(x = metric, y = pct, fill = perception)) +
  geom_col(alpha = 0.9, width = 0.6) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = c(
    "Thinks it is overpriced" = "#B22222",
    "Does not think it is overpriced" = "#4E79A7"
  )) +
  labs(
    title = "Nike Price-Mentioned Comments: Overpriced vs Not Overpriced",
    subtitle = "Among Nike comments that discuss price, share using explicit overpricing language versus those that do not",
    x = NULL,
    y = "Share of Comments",
    fill = "Perception"
  )
```

*Is overpricing mentioned?* Explicit overpricing language is uncommon in the overall Nike conversation, appearing in less than 1% of all Nike comments. However, within comments that mention price, the share rises to roughly 7%–8%. This suggests that overpricing is not a dominant brand-wide narrative, but it does become a meaningful source of friction once consumers begin discussing value and affordability.

```{r pricing-sentiment, fig.height=5}
price_flagged <- sentiment_scored %>%
  select(doc_id, brand, sentiment_score) %>%
  inner_join(price_doc_flags, by = c("doc_id", "brand"))

price_summary <- price_flagged %>%
  group_by(brand, has_price_mention) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE), n = n(), .groups = "drop")

price_mentioned_summary <- price_summary %>% filter(has_price_mention)

ggplot(price_mentioned_summary, aes(x = reorder(brand, avg_sentiment), y = avg_sentiment, fill = brand)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_brand() +
  coord_flip() +
  labs(title = "Sentiment in Price-Mentioned Comments",
       subtitle = "Average Bing sentiment among comments that explicitly discuss price",
       x = NULL, y = "Average Sentiment Score")
```

*Sentiment Score For pricing Interpretation:* Price-related conversation shows a weaker tone for Nike than for Adidas. Among comments that explicitly mention price, Nike’s average sentiment is slightly negative, while Adidas remains positive and Under Armour is more negative. This reinforces the view that price is a meaningful point of friction for Nike, although not to the same extent as Under Armour. Combined with the overpricing-language analysis, the results suggest that value perception becomes more vulnerable once consumers begin discussing price directly.

```{r nike-pricing-segments, fig.height=5}
pricing_by_product_line <- sentiment_scored %>%
  filter(brand == "Nike") %>%
  select(-product_line) %>%
  inner_join(nike_doc_product_lines, by = "doc_id") %>%
  inner_join(
    price_doc_flags %>% filter(brand == "Nike", has_price_mention) %>% select(doc_id),
    by = "doc_id"
  )

product_line_price_summary <- pricing_by_product_line %>%
  group_by(product_line) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE),
            doc_count = n(), .groups = "drop") %>%
  mutate(sentiment_band = if_else(avg_sentiment < 0, "Negative", "Non-negative")) %>%
  filter(doc_count >= MIN_DOC_COUNT)

ggplot(product_line_price_summary,
       aes(x = reorder(product_line, avg_sentiment), y = avg_sentiment, fill = sentiment_band)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  coord_flip() +
  scale_fill_manual(values = c("Negative" = "#B22222", "Non-negative" = nike_accent)) +
  labs(title = "Nike Pricing Sentiment by Product Line",
       subtitle = "Only Nike comments with explicit price mentions",
       x = "Product Line", y = "Average Sentiment Score (Bing)")
```

*Pricing Sentiment Score by product line Interpretation:* Price-related sentiment varies meaningfully across Nike product lines. React, Pegasus, and Vomero remain positive when price is discussed, suggesting relatively resilient value perception in those lines. In contrast, Vaporfly stands out with clearly negative price-related sentiment, indicating that pricing tension is more concentrated in this premium performance segment than across Nike’s portfolio overall.

```{r nike-pricing-categories, fig.height=5}
categorized_summary <- sentiment_scored %>%
  filter(brand == "Nike") %>%
  inner_join(nike_doc_categories, by = "doc_id") %>%
  inner_join(
    price_doc_flags %>% filter(brand == "Nike", has_price_mention) %>% select(doc_id),
    by = "doc_id"
  ) %>%
  group_by(category) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE),
            doc_count = n(), .groups = "drop") %>%
  filter(doc_count >= MIN_DOC_COUNT, !near(avg_sentiment, 0)) %>%
  arrange(desc(avg_sentiment))

ggplot(categorized_summary,
       aes(x = reorder(category, -avg_sentiment), y = avg_sentiment, fill = category)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_manual(values = c(
    "Footwear" = nike_accent,
    "Apparel" = "#2E8B57",
    "Accessories & Equipment" = "#4E79A7"
  )) +
  coord_flip() +
  labs(title = "Nike Pricing Sentiment by Product Category",
       subtitle = "Each price-mentioned Nike comment assigned by dominant product category (Footwear, Apparel, Accessories & Equipment)",
       x = "Product Category", y = "Average Sentiment Score")
```

*Pricing sentiment Score by Business Segment Interpretation:* At the category level, price-related sentiment remains positive across Footwear, Apparel, and Accessories & Equipment. Accessories & Equipment shows the strongest score, followed by Apparel, while Footwear is the weakest category. This suggests that pricing is not broadly undermining Nike’s value perception at the portfolio level, although the weaker Footwear result is consistent with the product-line analysis showing more concentrated tension in specific premium shoe lines.

## 4.6 Sustainability Language

How common are sustainability and greenwashing terms in Nike comments relative to competitors? The table below reports document-level counts and percentages.

```{r sustainability-summary-table}
sus_summary <- sus_flagged %>%
  group_by(brand) %>%
  summarise(
    total_docs        = n(),
    sustainability_n  = sum(has_sustainability),
    sustainability_pct = round(100 * sustainability_n / total_docs, 1),
    greenwash_n       = sum(has_greenwash),
    greenwash_pct     = round(100 * greenwash_n / total_docs, 1),
    .groups = "drop"
  )

sus_summary %>%
  rename(Brand = brand, `Total Docs` = total_docs,
         `Sustainability Mentions` = sustainability_n, `Sustainability %` = sustainability_pct,
         `Greenwash Mentions` = greenwash_n, `Greenwash %` = greenwash_pct) %>%
  kable(caption = "Sustainability and Greenwashing Language by Brand") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

The next two plots show which specific sustainability and greenwashing words Nike customers actually use.

```{r sustainability-vocab, fig.height=6}
nike_vocab_sentiment %>%
  group_by(Vocabulary) %>%
  slice_head(n = 10) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, Vocabulary)) %>%
  ggplot(aes(x = word, y = n, fill = Vocabulary)) +
  geom_col(show.legend = FALSE, alpha = 0.9) +
  coord_flip() +
  scale_fill_manual(values = vocab_palette) +
  scale_x_reordered() +
  facet_wrap(~Vocabulary, scales = "free_y") +
  labs(title = "Nike Sustainability & Greenwashing Vocabulary",
       subtitle = "Top 10 terms in each group",
       x = NULL, y = "Frequency")
```

*Interpretation:*

```{r sustainability-bigrams, fig.height=6}
nike_vocab_bigram %>%
  group_by(Vocabulary) %>%
  slice_head(n = TOP_N_TERMS) %>%
  ungroup() %>%
  mutate(bigram = reorder_within(bigram, n, Vocabulary)) %>%
  ggplot(aes(x = bigram, y = n, fill = Vocabulary)) +
  geom_col(show.legend = FALSE, alpha = 0.9) +
  coord_flip() +
  scale_fill_manual(values = vocab_palette) +
  scale_x_reordered() +
  facet_wrap(~Vocabulary, scales = "free_y") +
  labs(title = "Nike Sustainability & Greenwashing Bigrams",
       subtitle = "Top bigrams containing vocabulary from each group",
       x = NULL, y = "Frequency")
```

*Interpretation:*

## 4.7 Product Complaints

Which product-related terms carry the most negative sentiment? We filter to Nike comments that mention product-feature words (sizing, comfort, quality, durability) and surface the top negatives.

```{r complaint-terms, fig.height=5}
nike_product_negative %>%
  slice_head(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(stem, n), y = n)) +
  geom_col(fill = "#D62728", alpha = 0.9) +
  coord_flip() +
  labs(title = "Top Negative Terms in Nike Product Comments",
       subtitle = "Negative Bing words in comments mentioning product features",
       x = "Stem", y = "Frequency")
```

*Interpretation:*

```{r complaint-feature-impact, fig.height=5}
product_sentiment_by_term %>%
  slice_max(abs(score), n = TOP_N_TERMS, with_ties = FALSE) %>%
  ggplot(aes(x = reorder(stem, score), y = score, fill = score > 0)) +
  geom_col(alpha = 0.9, show.legend = FALSE) +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "#4E79A7", "FALSE" = "#D62728")) +
  labs(title = "Product Feature Sentiment Impact",
       subtitle = "Net Bing sentiment for key product-feature stems",
       x = "Feature Stem", y = "Net Sentiment Score")
```

*Interpretation:*

The bigram chart below shows two-word phrases from negatively scored Nike documents that contain complaint keywords, giving phrase-level context.

```{r complaint-bigrams, fig.height=5}
nike_complaint_bigrams %>%
  slice_head(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(bigram, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.9) +
  coord_flip() +
  labs(title = "Complaint Context Bigrams",
       subtitle = "Frequent two-word phrases in negative Nike product documents",
       x = "Bigram", y = "Frequency")
```

*Interpretation:*

## 4.8 Topic Discovery (LDA)

This Nike-only LDA model reveals hidden conversation clusters within Nike comments that are not obvious from sentiment scores alone.

```{r lda-model, fig.height=8}
lda_k <- 6

nike_dtm_input <- nike_tokens %>%
  count(doc_id, stem)

nike_dtm <- nike_dtm_input %>%
  cast_dtm(document = doc_id, term = stem, value = n)

# Remove extremely sparse terms for better topic quality
dtm_trimmed <- tm::removeSparseTerms(nike_dtm, sparse = 0.995)

# Safety check
if (nrow(dtm_trimmed) < lda_k || ncol(dtm_trimmed) < lda_k) {
  cat("Insufficient Nike terms/docs for LDA after trimming. Using full Nike DTM.\n")
  dtm_trimmed <- nike_dtm
}

# Remove empty documents
row_totals <- slam::row_sums(dtm_trimmed)
dtm_trimmed <- dtm_trimmed[row_totals > 0, ]

lda_fit <- topicmodels::LDA(dtm_trimmed, k = lda_k, control = list(seed = 42))

topic_terms <- tidytext::tidy(lda_fit, matrix = "beta") %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup()

ggplot(topic_terms, aes(x = reorder_within(term, beta, topic), y = beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_topic() +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~topic, scales = "free_y", ncol = 2,
             labeller = labeller(topic = function(x) paste("Topic", x))) +
  labs(
    title    = "Nike Topic Discovery: Top 10 Terms per Topic",
    subtitle = sprintf("k = %d topics fitted on %s Nike documents",
                       lda_k, format(nrow(dtm_trimmed), big.mark = ",")),
    x = "Term", y = "Beta (term probability)"
  )
```

```{r topic-brand-distribution, fig.height=5}
doc_topics <- tidytext::tidy(lda_fit, matrix = "gamma") %>%
  group_by(document) %>%
  slice_max(gamma, n = 1) %>%
  ungroup() %>%
  rename(doc_id = document, dominant_topic = topic, topic_prob = gamma) %>%
  mutate(doc_id = as.integer(doc_id))

topic_by_source <- nike_text %>%
  select(doc_id, source) %>%
  inner_join(doc_topics, by = "doc_id") %>%
  count(source, dominant_topic)

ggplot(topic_by_source, aes(x = factor(dominant_topic), y = n, fill = source)) +
  geom_col(position = "fill", alpha = 0.85) +
  scale_fill_source() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title    = "Nike Topic Distribution by Source",
    subtitle = "How Nike topics differ between Reddit and YouTube comments",
    x = "Dominant Topic", y = "Proportion of Nike Documents", fill = "Source"
  )
```

```{r topic-summary-table}
topic_terms %>%
  group_by(Topic = topic) %>%
  summarise(`Top Terms` = paste(term, collapse = ", "), .groups = "drop") %>%
  kable(caption = "Nike LDA Topics -- Top 10 Terms for Labeling") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

> **Interpretation:** .

With latent Nike topics identified, we next isolate which terms most clearly differentiate each brand's language.

------------------------------------------------------------------------

# 5. Cross-Brand NLP (Nike vs Adidas vs Under Armour)

With the Nike baseline established, we now compare all three brands using the same tokenization and sentiment pipelines.

```{r cross-brand-token-summary, echo=FALSE}
cat(sprintf("Tokenization: %s tokens from %s documents.\n",
            format(nrow(tokens), big.mark = ","),
            format(n_distinct(tokens$doc_id), big.mark = ",")))
```

## 5.1 Cross-Brand Bigrams

```{r cross-brand-bigrams, fig.height=8}
bigrams_all <- raw_text %>%
  build_bigrams(all_stop) %>%
  unite("bigram", w1, w2, sep = " ") %>%
  left_join(raw_text %>% select(doc_id, brand), by = "doc_id")

bigrams_all %>%
  count(brand, bigram, sort = TRUE) %>%
  group_by(brand) %>%
  slice_head(n = 12) %>%
  ungroup() %>%
  ggplot(aes(x = reorder_within(bigram, n, brand), y = n, fill = brand)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_brand() +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~brand, scales = "free_y") +
  labs(title = "Top 12 Bigrams by Brand",
       subtitle = "Two-word phrases across the full corpus",
       x = "Bigram", y = "Count")
```

*Interpretation* A relevant pattern in the bigram comparison is that each brand seems to occupy a different space in consumer conversation. Adidas appears more strongly associated with named performance models and sports-related contexts, which suggests stronger performance credibility and a clearer connection to competitive sport. Nike, by contrast, appears more anchored in its flagship product franchises and in product-use language, such as trail running, toe box, and half marathon. This suggests strong product salience, but less visible connection to broader sports ecosystems in the text than Adidas, what is surprising considering all the sponsorship that Nike does. Under Armour shows the weakest thematic cohesion, with conversation spread across athlete-led lines, functional terms, and competitor references. Overall, the pattern suggests that Nike is winning more through product franchise strength, Adidas through performance positioning, and Under Armour through a more fragmented set of associations.

## 5.2 NRC Emotion Breakdown by Brand

Emotion profiles go beyond simple positive/negative polarity. Trust and anticipation tend to dominate sneaker communities, but the relative differences between brands are what matter most.

```{r nrc-cross-brand, fig.height=7}
if (!nrow(nrc)) {
  placeholder_plot("NRC lexicon unavailable")
} else {
  nrc_pct <- tokens %>%
    inner_join(nrc, by = "word") %>%
    filter(!sentiment %in% c("positive", "negative")) %>%
    count(brand, sentiment, sort = TRUE) %>%
    group_by(brand) %>%
    mutate(pct = n / sum(n) * 100) %>%
    ungroup()

  ggplot(nrc_pct, aes(x = reorder(sentiment, pct), y = pct, fill = brand)) +
    geom_col(position = "dodge", alpha = 0.85) +
    scale_fill_brand() +
    coord_flip() +
    labs(title = "Emotion Profile by Brand (NRC)",
         subtitle = "Percentage of emotion-tagged tokens within each brand",
         x = "Emotion", y = "% of Emotion Tokens", fill = "Brand")
}
```

*Interpretation* What stands out here is that the emotional structure is broadly similar across the three brands, but the intensity is not. Trust is the strongest emotion for all of them, which suggests that the category overall is still anchored in confidence and brand familiarity. However, Adidas leads on trust and also shows the highest joy, while Nike is slightly lower on both. This may suggest that Nike remains emotionally strong, but not quite as positively reinforced as Adidas in the current conversation.

At the same time, Nike shows higher fear, sadness, and anger than Adidas, which points to more emotional friction in the brand discussion. Under Armour is the most polarized profile, with the highest anticipation and surprise, but also the highest disgust. Overall, Nike appears to sit in the middle: still emotionally strong, but with more tension in the conversation than Adidas and less volatility than Under Armour.

## 5.3 Bing Sentiment by Brand and Source

Average document-level Bing sentiment. The bar chart includes sample sizes so we can judge how stable each estimate is.

```{r sentiment-brand-plot, fig.height=5}
brand_sentiment <- sentiment_scored %>%
  group_by(brand) %>%
  summarise(avg_sentiment    = mean(sentiment_score, na.rm = TRUE),
            median_sentiment = median(sentiment_score, na.rm = TRUE),
            docs             = n(),
            .groups = "drop")

ggplot(brand_sentiment, aes(x = reorder(brand, avg_sentiment), y = avg_sentiment, fill = brand)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_brand() +
  geom_text(
    aes(label = sprintf("%.2f (n=%s)", avg_sentiment, format(docs, big.mark = ","))),
    hjust = -0.1, size = 4
  ) +
  coord_flip() +
  labs(title = "Average Bing Sentiment Score by Brand",
       subtitle = "Positive = net positive language; Negative = net negative language",
       x = NULL, y = "Average Sentiment Score") +
  expand_limits(y = max(abs(brand_sentiment$avg_sentiment)) * 1.5)
```

*Interpretation* At a high level, all three brands still show net positive language, but the strength of that positivity is clearly different. Adidas has the strongest average sentiment score, followed by Nike, while Under Armour is positive but much weaker. This suggests that Nike still benefits from a favorable overall conversation, but it is not generating the same level of positive reinforcement as Adidas. Under Armour, in turn, appears to have the weakest emotional position of the three.

Another important point is volume. Nike has the largest number of comments in the sample, which means its sentiment score is being shaped by a broader and more diverse set of conversations. In that context, Nike’s positive score is still meaningful, but the gap versus Adidas suggests more friction or less concentrated enthusiasm in how consumers talk about the brand.

```{r sentiment-by-source, fig.height=5}
source_sentiment <- sentiment_scored %>%
  group_by(brand, source) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE), docs = n(), .groups = "drop") %>%
  filter(docs >= MIN_DOC_COUNT)

if (nrow(source_sentiment) > 1 && n_distinct(source_sentiment$source) > 1) {
  ggplot(source_sentiment, aes(x = reorder(source, avg_sentiment), y = avg_sentiment, fill = brand)) +
    geom_col(position = "dodge", alpha = 0.85) +
    scale_fill_brand() +
    coord_flip() +
    labs(title = "Sentiment by Source and Brand",
         subtitle = "Comparing Reddit vs YouTube",
         x = "Source", y = "Avg Sentiment", fill = "Brand")
}
```

------------------------------------------------------------------------

# 6. Brand Differentiation (TF-IDF)

TF-IDF surfaces terms that are distinctive to each brand's conversation. A high TF-IDF score means the term appears often for that brand but rarely for the others.

```{r tfidf-brand, fig.height=8}
tfidf_brand <- tokens %>%
  count(brand, stem) %>%
  bind_tf_idf(term = stem, document = brand, n = n) %>%
  group_by(brand) %>%
  slice_max(tf_idf, n = TOP_N_TERMS) %>%
  ungroup()

ggplot(tfidf_brand, aes(x = reorder_within(stem, tf_idf, brand), y = tf_idf, fill = brand)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_brand() +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~brand, scales = "free_y") +
  labs(title = "Brand Differentiation: Unique Terms (TF-IDF)",
       subtitle = "Terms that distinguish each brand's customer language",
       x = "Stemmed Term", y = "TF-IDF Score")
```

*Interpretation* What this chart shows is not what each brand is mentioned with most often, but what language is most uniquely associated with each one. Adidas stands out for football and performance heritage, with distinctive terms linked to technical lines, teams, and athletes. Nike’s distinctive language is more connected to sneaker culture, product-specific communities, and functional use cases, including fit-related terms that do not appear as strongly for the other brands. Under Armour looks more narrowly differentiated, with language concentrated around athlete-led identities, golf, and functional apparel. Taken together, the pattern suggests Adidas owns more of the sport-performance space, Nike is differentiated more through product franchise and user experience, and Under Armour is differentiated in a narrower and more specialized way.

```{r tfidf-table, echo=FALSE}
tfidf_brand %>%
  group_by(Brand = brand) %>%
  slice_max(tf_idf, n = 10) %>%
  summarise(`Distinctive Terms` = paste(stem, collapse = ", "), .groups = "drop") %>%
  kable(caption = "Top 10 Distinguishing Terms per Brand (TF-IDF)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```
