---
title: "A2: Nike Text Analytics & Classification Modeling"
author: "Team 6"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
format:
    html:
        theme: 
            light: flatly
            dark: darkly
        highlight-style: github
        code-fold: true
        code-tools: 
            source: true
            toggle: true
        code-copy: true
        self-contained: true
        html-math-method: katex
        embed-resources: true
        code-overflow: wrap
        smooth-scroll: true       
        page-layout: full
        toc: true
        toc-location: right
        lightbox: true
---

```{r setup, include=FALSE}
# ──────────────────────────────────────────────────────────────
# 0. Package management & global configuration
# ──────────────────────────────────────────────────────────────
required_pkgs <- unique(c(
  "tidyverse", "lubridate", "stringr", "janitor", "scales", "knitr", "kableExtra",
  "tidytext", "tm", "quanteda", "stopwords", "SnowballC", "textdata", "topicmodels",
  "widyr", "igraph", "ggraph",
  "broom", "glmnet", "yardstick", "Matrix", "slam",
  "jsonlite", "httr", "rappdirs",
  "RColorBrewer", "ggrepel", "patchwork"
))

missing_pkgs <- required_pkgs[
  !vapply(required_pkgs, requireNamespace, FUN.VALUE = logical(1), quietly = TRUE)
]

if (length(missing_pkgs) > 0) {
  message("Installing missing packages: ", paste(missing_pkgs, collapse = ", "))
  install.packages(missing_pkgs, repos = "https://cloud.r-project.org", dependencies = TRUE)
}

still_missing <- required_pkgs[
  !vapply(required_pkgs, requireNamespace, FUN.VALUE = logical(1), quietly = TRUE)
]
if (length(still_missing) > 0) {
  warning("Could not install: ", paste(still_missing, collapse = ", "),
          ". Some sections may be skipped.")
}

invisible(lapply(required_pkgs, function(p) {
  tryCatch(
    suppressPackageStartupMessages(library(p, character.only = TRUE)),
    error = function(e) message(sprintf("Skipping '%s': %s", p, e$message))
  )
}))

set.seed(42)

knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 10,
  fig.height = 6,
  fig.align  = "center",
  dpi        = 150
)

# ── Tunable parameters ────────────────────────────────────────
LDA_K              <- 3       # number of executive topic segments
MIN_TERM_FREQ      <- 5       # floor for "rare but recurring" terms
MIN_DOC_COUNT      <- 3       # minimum docs before including a group in plots
TOP_N_TERMS        <- 15      # default number of top terms / bigrams to show
COOCCUR_MIN_FREQ   <- 5       # min document frequency for co-occurrence network
COOCCUR_MIN_CORR   <- 0.20    # min correlation for network edges
COOCCUR_MAX_EDGES  <- 80      # cap edges in network plot
LDA_SPARSITY       <- 0.995   # removeSparseTerms threshold

# ── Global theme & palettes ───────────────────────────────────
theme_nike <- theme_minimal(base_size = 13) +
  theme(
    plot.title       = element_text(face = "bold", size = 15),
    plot.subtitle    = element_text(color = "grey40", size = 11),
    strip.text       = element_text(face = "bold"),
    legend.position  = "bottom",
    panel.grid.minor = element_blank()
  )
theme_set(theme_nike)

nike_accent   <- "#F46B2F"
brand_colors  <- c("Nike" = nike_accent, "Adidas" = "#1D1D1B", "Under Armour" = "#003DA5")
source_levels <- c("Reddit", "YouTube", "Unknown")
source_colors <- c("Reddit" = "#4E79A7", "YouTube" = "#E15759", "Unknown" = "#76B7B2")
lexicon_colors <- c("AFINN" = nike_accent, "Bing" = "#4E79A7", "NRC" = "#59A14F")
vocab_palette  <- c("Sustainability" = "#2E8B57", "Greenwashing" = "#B22222")
topic_palette  <- setNames(
  c("#F28E2B", "#4E79A7", "#59A14F", "#E15759", "#76B7B2", "#EDC948"),
  as.character(1:6)
)
topic_segment_palette <- c(
  "Core complaint themes" = "#B22222",
  "Product differentiation themes" = nike_accent,
  "Emerging brand risks" = "#4E79A7"
)

# ── Reusable scale helpers ────────────────────────────────────
scale_fill_brand   <- function(...) scale_fill_manual(values = brand_colors, ...)
scale_fill_source  <- function(...) scale_fill_manual(values = source_colors, breaks = source_levels, drop = FALSE, ...)
scale_fill_lexicon <- function(...) scale_fill_manual(values = lexicon_colors, ...)
scale_fill_topic   <- function(...) scale_fill_manual(values = topic_palette, ...)

# ── Helper: normalize source label ────────────────────────────
normalize_source <- function(source) {
  case_when(
    str_detect(str_to_lower(coalesce(source, "unknown")), "reddit")  ~ "Reddit",
    str_detect(str_to_lower(coalesce(source, "unknown")), "youtube") ~ "YouTube",
    TRUE ~ "Unknown"
  )
}

# ── Helper: read term lists from a URL or local file ──────────
read_terms <- function(url, label, stem = FALSE) {
  raw_lines <- tryCatch(
    readr::read_lines(url, progress = FALSE),
    error = function(e) stop(sprintf("Failed to load %s from '%s': %s", label, url, e$message))
  )
  parsed <- raw_lines %>%
    str_replace_all("#.*$", "") %>%
    str_split("[,;]") %>%
    purrr::flatten_chr() %>%
    str_trim() %>%
    purrr::discard(~ .x == "")
  if (length(parsed) == 0) stop(sprintf("Terms file for %s is empty: %s", label, url))
  terms <- tolower(parsed)
  if (stem) terms <- SnowballC::wordStem(terms, language = "en")
  unique(terms)
}

# ── Helper: build bigrams from a text tibble ──────────────────
build_bigrams <- function(df, stop_words_vec, min_word_len = 2) {
  bigram_stop <- tibble(word = setdiff(stop_words_vec, c("no", "not", "nor", "never")))
  df %>%
    select(doc_id, text) %>%
    distinct() %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, into = c("w1", "w2"), sep = " ", remove = FALSE) %>%
    filter(!is.na(w1), !is.na(w2)) %>%
    filter(str_detect(w1, sprintf("^[a-z]{%d,}$", min_word_len)),
           str_detect(w2, sprintf("^[a-z]{%d,}$", min_word_len))) %>%
    anti_join(bigram_stop, by = c("w1" = "word")) %>%
    anti_join(bigram_stop, by = c("w2" = "word"))
}

# ── Helper: tokenize text with shared stopwords ───────────────
tokenize_text <- function(df, stop_words_vec) {
  df %>%
    select(doc_id, source, brand, product_line, rating, date, text) %>%
    unnest_tokens(word, text) %>%
    filter(str_detect(word, "^[a-z]{2,}$")) %>%
    filter(!word %in% stop_words_vec) %>%
    mutate(
      word = if_else(word == "nmds", "nmd", word),
      stem = SnowballC::wordStem(word, language = "en"),
      stem = if_else(stem == "nmds", "nmd", stem)
    )
}

# ── Pre-cache textdata lexicons for non-interactive render ────
ensure_textdata_lexicon <- function(data_name, rds_name) {
  if (!requireNamespace("textdata", quietly = TRUE)) return(FALSE)
  cache_dir <- file.path(rappdirs::user_cache_dir("textdata"), data_name)
  rds_path  <- file.path(cache_dir, rds_name)
  if (file.exists(rds_path)) return(TRUE)
  dir.create(cache_dir, recursive = TRUE, showWarnings = FALSE)
  tryCatch({
    if (length(list.files(cache_dir)) == 0) textdata:::download_functions[[data_name]](cache_dir)
    textdata:::process_functions[[data_name]](cache_dir, rds_path)
    TRUE
  }, error = function(e) {
    message(sprintf("Could not pre-cache '%s': %s. Continuing with fallback.", data_name, e$message))
    FALSE
  })
}

if (!interactive()) {
  invisible(ensure_textdata_lexicon("nrc", "NRCWordEmotion.rds"))
  invisible(ensure_textdata_lexicon("bing", "bing.rds"))
}

# ── Helper: load AFINN from GitHub source ─────────────────────
load_afinn_lexicon <- function() {
  tryCatch(
    readr::read_tsv(
      "https://raw.githubusercontent.com/fnielsen/afinn/master/afinn/data/AFINN-111.txt",
      col_names = c("word", "value"),
      show_col_types = FALSE, progress = FALSE
    ),
    error = function(e) {
      message("AFINN lexicon unavailable: ", e$message)
      tibble(word = character(), value = numeric())
    }
  )
}

# ── Helper: safe lexicon loader (returns empty tibble on fail) ─
safe_get_sentiments <- function(lexicon) {
  tryCatch(
    tidytext::get_sentiments(lexicon),
    error = function(e) {
      message(sprintf("%s lexicon unavailable: %s", lexicon, e$message))
      if (lexicon == "bing") return(tibble(word = character(), sentiment = character()))
      if (lexicon == "nrc")  return(tibble(word = character(), sentiment = character()))
      tibble(word = character())
    }
  )
}

# ── Helper: placeholder plot when a lexicon is missing ────────
placeholder_plot <- function(msg) {
  ggplot() +
    annotate("text", x = 0, y = 0, label = msg, size = 5, color = "grey50") +
    theme_void()
}
```

## How to Read This Notebook

This notebook moves from business framing to evidence to recommendations:

1.  **Context and hypotheses** set the questions we need to answer.
2.  **Data pipeline** describes collection, loading, and quality checks.
3.  **Nike baseline (Phase 1)** examines the brand on its own.
4.  **Cross-brand diagnostics (Phases 2--6)** compare Nike against Adidas and Under Armour.
5.  **Executive synthesis** ties findings back to actionable strategy.

# 1. Executive Brief

## Client Overview

Nike's CMO and VP of Consumer Insights asked our team to answer:

> **"What are customers really saying about Nike -- and how should we respond strategically?"**

Leadership has flagged growing online sustainability chatter, mixed pricing sentiment, product-quality complaints in key lines, and uneven sentiment across channels. We mined Reddit and YouTube comments to surface the drivers behind those signals.

## Strategic Questions

| \# | Pillar | Question |
|----|----|--------|
| 1 | Brand Perception | What is the overall sentiment toward Nike across online conversations? |
| 2 | Product Strategy | Which Nike product lines attract the most negative language around sizing, durability, and comfort? |
| 3 | Sustainability | Is Nike's sustainability messaging landing, or is greenwashing language creeping in? |
| 4 | Pricing Sentiment | Do comments mentioning price cluster with lower sentiment? |

## Hypotheses

1.  **H1 (Brand Perception):** Nike's net sentiment is positive overall but varies by source channel.
2.  **H2 (Product Strategy):** Negative Nike language concentrates around sizing, durability, and comfort traits.
3.  **H3 (Sustainability):** Sustainability mentions are polarized -- trust-related and greenwashing language both appear.
4.  **H4 (Price--Sentiment Link):** Comments mentioning price terms average lower sentiment than non-price comments.

## Financial Context

If sizing and quality complaints push return rates up by even 2% on flagship footwear, the revenue impact on Nike's \$51B annual footwear business is roughly **\$1B** in processing and lost-sale costs -- enough to justify early detection through text analytics.

------------------------------------------------------------------------

# 2. Data Pipeline

## Architecture

A separate `00_data_collection.R` script pulls live data from the Reddit and YouTube APIs and writes two CSVs. Keeping collection separate makes rendering faster, offline-capable, and reproducible.

| File | Source | API / Package | Contents |
|----|----|----|--------|
| `reddit_comments.csv` | Reddit (r/Sneakers, r/Nike, r/RunningShoeGeeks) | `RedditExtractoR` | Comments for Nike, Adidas, Under Armour |
| `youtube_comments.csv` | YouTube sneaker reviews | `httr` + YouTube Data API v3 | Comments from Nike / Adidas / UA review videos |

Both sources satisfy the requirement of collecting text from **at least two channels**.

------------------------------------------------------------------------

# 3. Data Ingestion and Quality Checks

We load the CSVs, combine them into one master table with standardized `brand` and `source` columns, and validate composition.

```{r load-csv-data}
# ── GitHub raw URLs ───────────────────────────────────────────
gh_base <- "https://raw.githubusercontent.com/renan-peres/mban-unstructured-data/refs/heads/main/%23A2%20-%20Nike%20Text%20Analytics%20(N-Aible%20Simulator)/data"

urls <- list(
  reddit       = paste0(gh_base, "/reddit_comments.csv"),
  youtube      = paste0(gh_base, "/youtube_comments.csv"),
  stopwords    = paste0(gh_base, "/custom_stopwords.txt"),
  sustain      = paste0(gh_base, "/sustainability_terms.txt"),
  greenwash    = paste0(gh_base, "/greenwashing_terms.txt"),
  product_lines = paste0(gh_base, "/nike_product_segments.txt")
)

# ── Load CSVs ─────────────────────────────────────────────────
load_csv_safe <- function(url, label) {
  tryCatch(
    read_csv(url, show_col_types = FALSE),
    error = function(e) { cat(sprintf("  %s CSV failed: %s\n", label, e$message)); NULL }
  )
}

source_frames <- list()

cat("Loading Reddit data...\n")
reddit_df <- load_csv_safe(urls$reddit, "Reddit")
if (!is.null(reddit_df)) {
  source_frames[["reddit"]] <- reddit_df
  cat(sprintf("✓ Reddit: %s rows\n", format(nrow(reddit_df), big.mark = ",")))
}

cat("Loading YouTube data...\n")
youtube_df <- load_csv_safe(urls$youtube, "YouTube")
if (!is.null(youtube_df)) {
  source_frames[["youtube"]] <- youtube_df
  cat(sprintf("✓ YouTube: %s rows\n", format(nrow(youtube_df), big.mark = ",")))
}

if (length(source_frames) == 0) stop("No data loaded -- check URLs or connectivity.")

# ── Load external term lists ──────────────────────────────────
sustainability_terms  <- read_terms(urls$sustain, "sustainability terms", stem = TRUE)
greenwash_terms       <- read_terms(urls$greenwash, "greenwashing terms", stem = TRUE)
nike_product_lines    <- read_terms(urls$product_lines, "product lines", stem = TRUE)
nike_product_segments_raw <- read_terms(urls$product_lines, "product lines", stem = FALSE)

cat(sprintf("\n✓ Loaded %d sources total\n", length(source_frames)))
```

```{r build-master-dataset}
raw_text <- bind_rows(source_frames) %>%
  select(any_of(c("text", "rating", "source", "brand", "doc_id"))) %>%
  mutate(
    doc_id = row_number(),
    source = factor(normalize_source(source), levels = source_levels),
    brand  = case_when(
      str_detect(str_to_lower(coalesce(brand, "")), "nike")             ~ "Nike",
      str_detect(str_to_lower(coalesce(brand, "")), "adidas")           ~ "Adidas",
      str_detect(str_to_lower(coalesce(brand, "")), "under\\s*armou?r") ~ "Under Armour",
      TRUE ~ coalesce(brand, "Unknown")
    ),
    product_line = NA_character_,
    date         = as.Date(NA),
    rating       = suppressWarnings(as.numeric(rating)),
    text         = str_squish(text)
  ) %>%
  filter(!is.na(text), nchar(text) > 10)

cat(sprintf(
  "Master dataset: %s documents across %d sources and %d brands.\n",
  format(nrow(raw_text), big.mark = ","),
  n_distinct(raw_text$source),
  n_distinct(raw_text$brand)
))

# ── Build shared stopword set (once) ──────────────────────────
custom_stop <- read_terms(urls$stopwords, "custom stopwords", stem = FALSE)
all_stop    <- unique(c(tidytext::stop_words$word, stopwords::stopwords("en"), custom_stop))

cat(sprintf("Loaded %s custom stopwords.\n", format(length(custom_stop), big.mark = ",")))
```

```{r analysis-primitives}
# ── Shared tokenization (used across all sections) ────────────
tokens <- tokenize_text(raw_text, all_stop)

# ── Bing lexicon & document-level sentiment ───────────────────
bing <- safe_get_sentiments("bing")
if (nrow(bing) == 0) stop("Bing lexicon is required. Run once with internet to populate the textdata cache.")

sentiment_scored <- tokens %>%
  inner_join(bing, by = "word") %>%
  mutate(score = if_else(sentiment == "positive", 1L, -1L)) %>%
  group_by(doc_id, brand, product_line, source, rating) %>%
  summarise(sentiment_score = sum(score), .groups = "drop")

cat(sprintf(
  "Shared analysis objects ready: %s tokens and %s sentiment-scored documents.\n",
  format(nrow(tokens), big.mark = ","),
  format(nrow(sentiment_scored), big.mark = ",")
))
```

```{r shared-derived-objects}
# ── Nike subsets ──────────────────────────────────────────────
nike_text   <- raw_text %>% filter(brand == "Nike")
if (nrow(nike_text) == 0) stop("No Nike documents found after brand normalization.")
nike_tokens <- tokens %>% filter(brand == "Nike")

# ── Price terms & document flags (all brands) ─────────────────
price_terms <- c(
  "expensive", "pricey", "overpriced", "ripoff", "scam", "markup", "costly",
  "retail", "standard", "msrp", "normal", "base", "average", "regular",
  "cheap", "affordable", "deal", "steal", "discount", "sale", "budget"
)

price_doc_flags <- tokens %>%
  group_by(doc_id, brand) %>%
  summarise(has_price_mention = any(stem %in% price_terms), .groups = "drop")

# ── Nike product-line document mapping ────────────────────────
nike_doc_product_lines <- nike_tokens %>%
  filter(stem %in% nike_product_lines) %>%
  select(doc_id, product_line = word) %>%
  distinct()

# ── Nike term frequency (for baseline plots) ──────────────────
nike_term_frequency <- nike_tokens %>% count(stem, sort = TRUE)

# ── Nike product-segment category classifier ──────────────────
classify_nike_segment <- function(segment_name) {
  case_when(
    str_detect(segment_name, regex(
      "hoodie|sweatshirt|jacket|t-shirt|tank top|jersey|polo|shirt|pant|short|legging|tight|jogger|tracksuit|sweatpant|sports bra|yoga pant|dress|skirt|windbreaker|puffer|rain jacket|vest|swimwear|tech fleece|dri-fit|nike pro|livestrong|acg|nikelab|ispa",
      ignore_case = TRUE)) ~ "Apparel",
    str_detect(segment_name, regex(
      "bag|backpack|duffel|sack|ball|sock|headband|wristband|hat|cap|beanie|glove|sunglass|bottle|yoga mat|weight|resistance band|jump rope|knee pad|shin guard|ankle brace|compression sleeve",
      ignore_case = TRUE)) ~ "Accessories & Equipment",
    str_detect(segment_name, regex(
      "flyknit|flywire|zoomx|zoom air|lunarlon|cushlon|shox|flyease|adapt|connected jersey",
      ignore_case = TRUE)) ~ "Performance Technology",
    TRUE ~ "Footwear"
  )
}

nike_product_token_categories <- tibble(product_segment = nike_product_segments_raw) %>%
  mutate(category = classify_nike_segment(product_segment)) %>%
  unnest_tokens(segment_token, product_segment) %>%
  filter(str_detect(segment_token, "^[a-z]{2,}$")) %>%
  mutate(stem = SnowballC::wordStem(segment_token, language = "en")) %>%
  count(stem, category, name = "segment_matches") %>%
  group_by(stem) %>%
  mutate(category_count = n_distinct(category),
         dominant_share = segment_matches / sum(segment_matches)) %>%
  slice_max(segment_matches, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  filter(category_count == 1 | dominant_share >= 0.6) %>%
  select(stem, category) %>%
  distinct()

nike_doc_categories <- nike_tokens %>%
  inner_join(nike_product_token_categories, by = "stem") %>%
  count(doc_id, category, name = "match_count") %>%
  group_by(doc_id) %>%
  slice_max(match_count, n = 1, with_ties = FALSE) %>%
  ungroup()

# ── Sustainability / greenwashing flags (all brands) ──────────
sus_flagged <- tokens %>%
  mutate(is_sustainability = stem %in% sustainability_terms,
         is_greenwash      = stem %in% greenwash_terms) %>%
  group_by(doc_id, brand) %>%
  summarise(has_sustainability = any(is_sustainability),
            has_greenwash      = any(is_greenwash),
            .groups = "drop")

# ── Nike sustainability vocabulary profile ────────────────────
nike_vocab_sentiment <- bind_rows(
  nike_tokens %>% filter(stem %in% sustainability_terms) %>%
    count(word, stem, sort = TRUE) %>% mutate(Vocabulary = "Sustainability"),
  nike_tokens %>% filter(stem %in% greenwash_terms) %>%
    count(word, stem, sort = TRUE) %>% mutate(Vocabulary = "Greenwashing")
) %>%
  left_join(bing %>% select(word, sentiment), by = c("stem" = "word")) %>%
  mutate(sentiment = replace_na(sentiment, "Not labeled"))

# ── Nike sustainability bigrams ───────────────────────────────
bigram_stop <- tibble(word = setdiff(all_stop, c("no", "not", "nor", "never")))

nike_vocab_bigram <- nike_text %>%
  build_bigrams(all_stop) %>%
  mutate(
    stem1 = SnowballC::wordStem(w1, language = "en"),
    stem2 = SnowballC::wordStem(w2, language = "en"),
    Vocabulary = case_when(
      stem1 %in% sustainability_terms | stem2 %in% sustainability_terms ~ "Sustainability",
      stem1 %in% greenwash_terms | stem2 %in% greenwash_terms ~ "Greenwashing",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Vocabulary)) %>%
  count(Vocabulary, bigram, sort = TRUE)

# ── Product complaint objects (H2) ────────────────────────────
product_terms <- c(
  "size", "fit", "small", "big", "tight", "loose",
  "comfort", "comfortable", "uncomfortable",
  "quality", "material", "durable", "cheap",
  "sole", "design", "style", "color",
  "break", "tear", "wear", "support", "cushion"
)
product_terms_stem <- unique(SnowballC::wordStem(product_terms, language = "en"))

nike_product_docs   <- nike_tokens %>% filter(stem %in% product_terms_stem) %>% distinct(doc_id)
nike_product_text   <- nike_text %>% filter(doc_id %in% nike_product_docs$doc_id)
nike_product_tokens <- nike_product_text %>%
  select(doc_id, text) %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "^[a-z]{2,}$"), !word %in% all_stop) %>%
  mutate(stem = SnowballC::wordStem(word, language = "en"))

nike_product_negative <- nike_product_tokens %>%
  inner_join(bing, by = "word") %>%
  filter(sentiment == "negative") %>%
  count(stem, sort = TRUE)

product_sentiment_by_term <- nike_product_tokens %>%
  inner_join(bing, by = "word") %>%
  filter(stem %in% product_terms_stem) %>%
  group_by(stem) %>%
  summarise(score = sum(if_else(sentiment == "positive", 1L, -1L)),
            mentions = n(), .groups = "drop") %>%
  arrange(score, desc(mentions))

nike_low_sentiment_docs <- sentiment_scored %>%
  filter(brand == "Nike", sentiment_score < 0) %>%
  select(doc_id, sentiment_score)

nike_complaint_bigrams <- nike_text %>%
  select(doc_id, text) %>%
  inner_join(nike_low_sentiment_docs %>% select(doc_id), by = "doc_id") %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, into = c("word1", "word2"), sep = " ", remove = FALSE) %>%
  filter(!is.na(word1), !is.na(word2),
         str_detect(word1, "^[a-z]{2,}$"), str_detect(word2, "^[a-z]{2,}$")) %>%
  anti_join(bigram_stop, by = c("word1" = "word")) %>%
  anti_join(bigram_stop, by = c("word2" = "word")) %>%
  filter(str_detect(bigram, "break|cheap|hurt|tear|tight|small|uncomfort|wear")) %>%
  count(bigram, sort = TRUE)

# ── Top terms in positive vs negative Nike docs ───────────────
nike_pos_neg_words <- nike_tokens %>%
  inner_join(sentiment_scored %>% filter(brand == "Nike") %>% select(doc_id, sentiment_score),
             by = "doc_id") %>%
  mutate(group = if_else(sentiment_score > 0, "Positive", "Negative")) %>%
  count(group, stem) %>%
  group_by(group) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup()

cat(sprintf(
  "Shared Nike objects ready: %s Nike docs, %s Nike tokens, %s sustainability bigrams, %s complaint-focused docs.\n",
  format(nrow(nike_text), big.mark = ","),
  format(nrow(nike_tokens), big.mark = ","),
  format(nrow(nike_vocab_bigram), big.mark = ","),
  format(nrow(nike_product_docs), big.mark = ",")
))
```

The table below shows the document breakdown by brand and source after filtering out very short texts (<10 characters).

```{r data-summary-table}
raw_text %>%
  group_by(Brand = brand, Source = source) %>%
  summarise(Documents = n(), `Avg Length` = round(mean(nchar(text)), 0), .groups = "drop") %>%
  arrange(Brand, desc(Documents)) %>%
  kable(caption = "Data Composition by Brand and Source") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r brand-volume-plot, fig.height=5}
raw_text %>%
  count(brand, source) %>%
  ggplot(aes(x = reorder(brand, -n), y = n, fill = source)) +
  geom_col(alpha = 0.85) +
  scale_fill_source() +
  labs(title = "Documents by Brand and Source",
       subtitle = "Collected via 00_data_collection.R (Reddit + YouTube APIs)",
       x = NULL, y = "Documents", fill = "Source")
```

Nike dominates the corpus because the search queries were designed around Nike and its product lines. Adidas and Under Armour are included as competitive benchmarks.

------------------------------------------------------------------------

# 4. Nike Baseline Analysis

Before comparing across brands, we run a focused Nike-only pass to understand the single-brand landscape: term frequencies, bigrams, emotion profile, topics, and keyword relationships.

```{r nike-baseline-summary}
cat(sprintf(
  "Nike-only baseline: %s documents and %s cleaned tokens.\n",
  format(nrow(nike_text), big.mark = ","),
  format(nrow(nike_tokens), big.mark = ",")
))
```

```{r nike-summary-table}
nike_text %>%
  group_by(Source = source) %>%
  summarise(Documents = n(),
            `Avg Length` = round(mean(nchar(text)), 0),
            `Avg Rating` = round(mean(rating, na.rm = TRUE), 2),
            .groups = "drop") %>%
  arrange(desc(Documents)) %>%
  kable(caption = "Nike Baseline by Source") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## 4.1 Top Frequent Terms

The bar chart below shows the most common stemmed terms in Nike documents. High-frequency stems like "shoe," "run," and "air" reflect expected product discussion; watch for quality- or complaint-related stems.

```{r nike-top-terms, fig.height=5}
nike_term_frequency %>%
  slice_head(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(stem, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.85) +
  coord_flip() +
  labs(title = "Nike: Top 15 Stemmed Terms",
       subtitle = "Core conversation themes in Nike-only documents",
       x = "Stem", y = "Frequency")
```

For context, here are the rarest terms that still appear at least `r MIN_TERM_FREQ` times -- useful for spotting niche signals that might not surface otherwise.

```{r nike-least-terms, fig.height=5}
nike_term_frequency %>%
  filter(n >= MIN_TERM_FREQ) %>%
  arrange(n, stem) %>%
  slice_head(n = 20) %>%
  ggplot(aes(x = reorder(stem, -n), y = n)) +
  geom_col(fill = "#fb1e1e", alpha = 0.85) +
  coord_flip() +
  labs(title = "Nike: Least Frequent Recurring Terms",
       subtitle = sprintf("Rare terms with %d+ mentions", MIN_TERM_FREQ),
       x = "Stem", y = "Frequency")
```

## 4.2 Bigrams

Bigrams reveal common two-word pairings that unigrams miss -- product names ("air force"), quality descriptors ("runs small"), and brand signals ("nike dunk").

```{r nike-bigrams, fig.height=5}
nike_bigrams <- nike_text %>%
  build_bigrams(all_stop) %>%
  unite("bigram", w1, w2, sep = " ")

nike_bigrams %>%
  count(bigram, sort = TRUE) %>%
  slice_head(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(bigram, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.85) +
  coord_flip() +
  labs(title = "Nike: Top 15 Bigrams",
       subtitle = "Common phrase pairings in Nike conversations",
       x = "Bigram", y = "Frequency")
```

## 4.3 Lexicon Sentiment Snapshot

We compare three sentiment lexicons on the same Nike token corpus. Directional agreement across lexicons increases our confidence that the overall signal is real rather than an artifact of one dictionary.

```{r nike-nrc-emotions, fig.height=5}
nrc <- safe_get_sentiments("nrc")

if (nrow(nrc) == 0) {
  nike_nrc_pct <- tibble(sentiment = character(), n = integer(), pct = numeric())
  placeholder_plot("NRC lexicon unavailable")
} else {
  nike_nrc_pct <- nike_tokens %>%
    inner_join(nrc, by = "word") %>%
    filter(!sentiment %in% c("positive", "negative")) %>%
    count(sentiment, sort = TRUE) %>%
    mutate(pct = 100 * n / sum(n))

  ggplot(nike_nrc_pct, aes(x = reorder(sentiment, pct), y = pct)) +
    geom_col(fill = nike_accent, alpha = 0.85) +
    coord_flip() +
    labs(title = "Nike Emotion Profile (NRC)",
         subtitle = "Share of emotion-tagged tokens in Nike documents",
         x = "Emotion", y = "% of Emotion Tokens")
}
```

```{r nike-lexicon-comparison, fig.height=5}
afinn_lex <- load_afinn_lexicon()

afinn_compare <- nike_tokens %>%
  inner_join(afinn_lex, by = "word") %>%
  summarise(sentiment = sum(value, na.rm = TRUE)) %>%
  mutate(method = "AFINN")

bing_nrc_compare <- bind_rows(
  nike_tokens %>% inner_join(bing, by = "word") %>% mutate(method = "Bing"),
  nike_tokens %>%
    inner_join(nrc %>% filter(sentiment %in% c("positive", "negative")), by = "word") %>%
    mutate(method = "NRC")
) %>%
  count(method, sentiment, name = "n") %>%
  complete(method, sentiment = c("positive", "negative"), fill = list(n = 0)) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(sentiment = positive - negative)

lexicon_compare <- bind_rows(afinn_compare, bing_nrc_compare) %>%
  mutate(method = factor(method, levels = c("AFINN", "Bing", "NRC")))

ggplot(lexicon_compare, aes(method, sentiment, fill = method)) +
  geom_col(show.legend = FALSE, alpha = 0.9) +
  facet_wrap(~method, ncol = 1, scales = "free_y") +
  scale_fill_lexicon() +
  labs(title = "Nike Lexicon Comparison: AFINN vs Bing vs NRC",
       subtitle = "Net sentiment totals on the same Nike token set",
       x = NULL, y = "Net Sentiment")
```

All three lexicons point in the same direction. The magnitude differs because AFINN uses a -5 to +5 scale while Bing and NRC are binary, but the directional consistency is what matters here.

## 4.4 Topic Discovery (LDA)

LDA clusters Nike documents into `r LDA_K` latent topics, which are then mapped into three executive-facing segments: core complaint themes, product differentiation themes, and emerging brand risks.

```{r lda-model, fig.height=8}
topic_segment_keywords <- list(
  "Core complaint themes" = c(
    "size", "fit", "small", "tight", "loose", "comfort", "uncomfort",
    "durabl", "cheap", "break", "tear", "wear", "qualiti", "support", "cushion"
  ),
  "Product differentiation themes" = c(
    "air", "zoom", "react", "pegasu", "jordan", "dunk", "max", "run",
    "perform", "design", "style", "fly", "court", "basketbal", "train"
  ),
  "Emerging brand risks" = c(
    "price", "expens", "overpric", "retail", "sale", "discount", "budget",
    "sustain", "greenwash", "trust", "scam", "markup", "costli", "afford"
  )
)

get_topic_theme_score <- function(topic_id, theme_name, score_tbl) {
  matched_score <- score_tbl %>%
    filter(topic == topic_id, topic_theme == theme_name) %>%
    pull(score)

  if (length(matched_score) == 0) 0 else matched_score[[1]]
}

nike_dtm <- nike_tokens %>%
  count(doc_id, stem) %>%
  cast_dtm(document = doc_id, term = stem, value = n)

dtm_trimmed <- tm::removeSparseTerms(nike_dtm, sparse = LDA_SPARSITY)

if (nrow(dtm_trimmed) < LDA_K || ncol(dtm_trimmed) < LDA_K) {
  cat("Insufficient terms/docs after trimming -- using full Nike DTM.\n")
  dtm_trimmed <- nike_dtm
}

row_totals <- slam::row_sums(dtm_trimmed)
dtm_trimmed <- dtm_trimmed[row_totals > 0, ]

lda_fit <- topicmodels::LDA(dtm_trimmed, k = LDA_K, control = list(seed = 42))

topic_terms_full <- tidy(lda_fit, matrix = "beta")

topic_theme_scores <- topic_terms_full %>%
  inner_join(
    enframe(topic_segment_keywords, name = "topic_theme", value = "term") %>%
      unnest(term),
    by = "term"
  ) %>%
  group_by(topic, topic_theme) %>%
  summarise(score = sum(beta), .groups = "drop")

topic_ids <- sort(unique(topic_terms_full$topic))
topic_segment_names <- names(topic_segment_keywords)

topic_theme_assignment <- as_tibble(expand.grid(
  theme_1 = topic_segment_names,
  theme_2 = topic_segment_names,
  theme_3 = topic_segment_names,
  stringsAsFactors = FALSE
)) %>%
  filter(theme_1 != theme_2, theme_1 != theme_3, theme_2 != theme_3) %>%
  rowwise() %>%
  mutate(
    total_score =
      get_topic_theme_score(topic_ids[1], theme_1, topic_theme_scores) +
      get_topic_theme_score(topic_ids[2], theme_2, topic_theme_scores) +
      get_topic_theme_score(topic_ids[3], theme_3, topic_theme_scores)
  ) %>%
  ungroup() %>%
  slice_max(total_score, n = 1, with_ties = FALSE)

topic_theme_lookup <- tibble(
  topic = topic_ids,
  topic_theme = c(
    topic_theme_assignment$theme_1,
    topic_theme_assignment$theme_2,
    topic_theme_assignment$theme_3
  )
)

topic_terms <- topic_terms_full %>%
  left_join(topic_theme_lookup, by = "topic") %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  mutate(topic_theme = factor(topic_theme, levels = topic_segment_names))

ggplot(topic_terms, aes(x = reorder_within(term, beta, topic_theme), y = beta, fill = topic_theme)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_manual(values = topic_segment_palette) +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~topic_theme, scales = "free_y", ncol = 1) +
  labs(title = "Nike Topic Discovery: Three Executive Topic Segments",
       subtitle = sprintf("LDA topics are mapped into %d business-facing segments across %s Nike documents",
                          LDA_K, format(nrow(dtm_trimmed), big.mark = ",")),
       x = "Term", y = "Beta (term probability)")
```

```{r topic-source-distribution, fig.height=5}
doc_topics <- tidy(lda_fit, matrix = "gamma") %>%
  group_by(document) %>%
  slice_max(gamma, n = 1) %>%
  ungroup() %>%
  rename(doc_id = document, dominant_topic = topic, topic_prob = gamma) %>%
  mutate(doc_id = as.integer(doc_id)) %>%
  left_join(topic_theme_lookup, by = c("dominant_topic" = "topic")) %>%
  mutate(topic_theme = factor(topic_theme, levels = topic_segment_names))

topic_by_source <- nike_text %>%
  select(doc_id, source) %>%
  inner_join(doc_topics, by = "doc_id") %>%
  count(source, topic_theme)

ggplot(topic_by_source, aes(x = topic_theme, y = n, fill = source)) +
  geom_col(position = "fill", alpha = 0.85) +
  scale_fill_source() +
  scale_y_continuous(labels = percent) +
  coord_flip() +
  labs(title = "Nike Topic Segment Distribution by Source",
       subtitle = "Reddit vs YouTube split across the three executive topic segments",
       x = "Topic Segment", y = "Proportion", fill = "Source")
```

```{r topic-summary-table}
topic_terms %>%
  group_by(`Topic Segment` = topic_theme) %>%
  summarise(`Top Terms` = paste(term, collapse = ", "), .groups = "drop") %>%
  kable(caption = "Nike Executive Topic Segments -- Top 10 Terms") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

> **How to read this:** The model still learns latent LDA topics, but each one is translated into one of three executive segments. "Core complaint themes" capture fit, comfort, and durability issues; "Product differentiation themes" capture performance and signature product attributes; "Emerging brand risks" capture pricing and reputation-related signals.

## 4.5 Keyword Co-occurrence Network

The network below shows which terms tend to appear together in the same Nike documents. Thicker edges = stronger co-occurrence; larger nodes = higher degree centrality (i.e., more connections).

```{r cooccurrence-network, fig.height=8, fig.width=10}
pairwise_terms <- nike_tokens %>%
  select(doc_id, stem) %>%
  distinct() %>%
  add_count(stem, name = "doc_freq") %>%
  filter(doc_freq >= COOCCUR_MIN_FREQ)

pair_counts <- pairwise_terms %>%
  pairwise_cor(stem, doc_id, sort = TRUE, upper = FALSE)

top_pairs <- pair_counts %>%
  filter(correlation >= COOCCUR_MIN_CORR) %>%
  slice_head(n = COOCCUR_MAX_EDGES)

if (nrow(top_pairs) > 2) {
  graph <- graph_from_data_frame(top_pairs, directed = FALSE)
  V(graph)$centrality <- degree(graph)

  ggraph(graph, layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation, edge_width = correlation), color = "gray55") +
    geom_node_point(aes(size = centrality), color = nike_accent, alpha = 0.8) +
    geom_node_text(aes(label = name), repel = TRUE, size = 3.3, max.overlaps = 40) +
    scale_edge_alpha(range = c(0.15, 0.6), guide = "none") +
    scale_edge_width(range = c(0.2, 1.8), guide = "none") +
    scale_size_continuous(range = c(2.5, 7), guide = "none") +
    labs(title = "Nike Keyword Co-Occurrence Network",
         subtitle = "Edges = pairwise correlations across Nike documents") +
    theme_void() +
    theme(plot.title    = element_text(face = "bold", size = 15),
          plot.subtitle = element_text(color = "grey40", size = 11))
} else {
  cat("Not enough strongly correlated term pairs to build a network.\n")
}
```

## 4.6 Pricing Sentiment (H4)

Do comments that mention price-related language carry lower sentiment? The chart below restricts to documents where a price term (e.g., "expensive," "deal," "overpriced") was detected, and compares average Bing sentiment across brands.

```{r pricing-sentiment, fig.height=5}
price_flagged <- sentiment_scored %>%
  select(doc_id, brand, sentiment_score) %>%
  inner_join(price_doc_flags, by = c("doc_id", "brand"))

price_summary <- price_flagged %>%
  group_by(brand, has_price_mention) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE), n = n(), .groups = "drop")

price_mentioned_summary <- price_summary %>% filter(has_price_mention)

ggplot(price_mentioned_summary, aes(x = reorder(brand, avg_sentiment), y = avg_sentiment, fill = brand)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_brand() +
  coord_flip() +
  labs(title = "H4: Sentiment in Price-Mentioned Comments",
       subtitle = "Average Bing sentiment among comments that explicitly discuss price",
       x = NULL, y = "Average Sentiment Score")
```

```{r nike-pricing-segments, fig.height=5}
pricing_by_product_line <- sentiment_scored %>%
  filter(brand == "Nike") %>%
  select(-product_line) %>%
  inner_join(nike_doc_product_lines, by = "doc_id") %>%
  inner_join(
    price_doc_flags %>% filter(brand == "Nike", has_price_mention) %>% select(doc_id),
    by = "doc_id"
  )

product_line_price_summary <- pricing_by_product_line %>%
  group_by(product_line) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE),
            doc_count = n(), .groups = "drop") %>%
  mutate(sentiment_band = if_else(avg_sentiment < 0, "Negative", "Non-negative")) %>%
  filter(doc_count >= MIN_DOC_COUNT)

ggplot(product_line_price_summary,
       aes(x = reorder(product_line, avg_sentiment), y = avg_sentiment, fill = sentiment_band)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  coord_flip() +
  scale_fill_manual(values = c("Negative" = "#B22222", "Non-negative" = nike_accent)) +
  labs(title = "Nike Pricing Sentiment by Product Line",
       subtitle = "Only Nike comments with explicit price mentions",
       x = "Product Line", y = "Average Sentiment Score (Bing)")
```

```{r nike-pricing-categories, fig.height=5}
categorized_summary <- sentiment_scored %>%
  filter(brand == "Nike") %>%
  inner_join(nike_doc_categories, by = "doc_id") %>%
  inner_join(
    price_doc_flags %>% filter(brand == "Nike", has_price_mention) %>% select(doc_id),
    by = "doc_id"
  ) %>%
  group_by(category) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE),
            doc_count = n(), .groups = "drop") %>%
  filter(doc_count >= MIN_DOC_COUNT) %>%
  arrange(desc(avg_sentiment))

ggplot(categorized_summary,
       aes(x = reorder(category, -avg_sentiment), y = avg_sentiment, fill = category)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_manual(values = c(
    "Footwear" = nike_accent, "Apparel" = "#2E8B57",
    "Accessories & Equipment" = "#4E79A7", "Performance Technology" = "#9C755F"
  )) +
  coord_flip() +
  labs(title = "Nike Pricing Sentiment by Product Category",
       subtitle = "Each price-mentioned Nike comment assigned to its dominant category",
       x = "Product Category", y = "Average Sentiment Score")
```

## 4.7 Sustainability Language (H3)

How prevalent are sustainability and greenwashing terms in Nike comments compared to competitors? The table below reports document-level counts.

```{r sustainability-summary-table}
sus_summary <- sus_flagged %>%
  group_by(brand) %>%
  summarise(
    total_docs        = n(),
    sustainability_n  = sum(has_sustainability),
    sustainability_pct = round(100 * sustainability_n / total_docs, 1),
    greenwash_n       = sum(has_greenwash),
    greenwash_pct     = round(100 * greenwash_n / total_docs, 1),
    .groups = "drop"
  )

sus_summary %>%
  rename(Brand = brand, `Total Docs` = total_docs,
         `Sustainability Mentions` = sustainability_n, `Sustainability %` = sustainability_pct,
         `Greenwash Mentions` = greenwash_n, `Greenwash %` = greenwash_pct) %>%
  kable(caption = "H3: Sustainability and Greenwashing Language by Brand") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

The next two plots zoom into which specific sustainability and greenwashing words Nike customers actually use.

```{r sustainability-vocab, fig.height=6}
nike_vocab_sentiment %>%
  group_by(Vocabulary) %>%
  slice_head(n = 10) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, Vocabulary)) %>%
  ggplot(aes(x = word, y = n, fill = Vocabulary)) +
  geom_col(show.legend = FALSE, alpha = 0.9) +
  coord_flip() +
  scale_fill_manual(values = vocab_palette) +
  scale_x_reordered() +
  facet_wrap(~Vocabulary, scales = "free_y") +
  labs(title = "Nike Sustainability & Greenwashing Vocabulary",
       subtitle = "Top 10 terms in each group",
       x = NULL, y = "Frequency")
```

```{r sustainability-bigrams, fig.height=6}
nike_vocab_bigram %>%
  group_by(Vocabulary) %>%
  slice_head(n = TOP_N_TERMS) %>%
  ungroup() %>%
  mutate(bigram = reorder_within(bigram, n, Vocabulary)) %>%
  ggplot(aes(x = bigram, y = n, fill = Vocabulary)) +
  geom_col(show.legend = FALSE, alpha = 0.9) +
  coord_flip() +
  scale_fill_manual(values = vocab_palette) +
  scale_x_reordered() +
  facet_wrap(~Vocabulary, scales = "free_y") +
  labs(title = "Nike Sustainability & Greenwashing Bigrams",
       subtitle = "Top bigrams containing vocabulary from each group",
       x = NULL, y = "Frequency")
```

## 4.8 Product Complaints (H2)

Which product-related terms carry the most negative sentiment? We filter to Nike comments that mention product-feature words (sizing, comfort, quality, durability, etc.) and surface the top negatives.

```{r complaint-terms, fig.height=5}
nike_product_negative %>%
  slice_head(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(stem, n), y = n)) +
  geom_col(fill = "#D62728", alpha = 0.9) +
  coord_flip() +
  labs(title = "Top Negative Terms in Nike Product Comments",
       subtitle = "Negative Bing words in comments mentioning product features",
       x = "Stem", y = "Frequency")
```

```{r complaint-feature-impact, fig.height=5}
product_sentiment_by_term %>%
  slice_max(abs(score), n = TOP_N_TERMS, with_ties = FALSE) %>%
  ggplot(aes(x = reorder(stem, score), y = score, fill = score > 0)) +
  geom_col(alpha = 0.9, show.legend = FALSE) +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "#4E79A7", "FALSE" = "#D62728")) +
  labs(title = "Product Feature Sentiment Impact",
       subtitle = "Net Bing sentiment for key product-feature stems",
       x = "Feature Stem", y = "Net Sentiment Score")
```

The bigram chart below shows two-word phrases from Nike comments that scored negative overall and contain complaint keywords. These give phrase-level context for the issues flagged above.

```{r complaint-bigrams, fig.height=5}
nike_complaint_bigrams %>%
  slice_head(n = TOP_N_TERMS) %>%
  ggplot(aes(x = reorder(bigram, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.9) +
  coord_flip() +
  labs(title = "Complaint Context Bigrams",
       subtitle = "Frequent two-word phrases in negative Nike product documents",
       x = "Bigram", y = "Frequency")
```

------------------------------------------------------------------------

# 5. Cross-Brand NLP (Nike vs Adidas vs Under Armour)

With the Nike baseline established, we now compare all three brands on the same tokenization and sentiment pipelines.

```{r cross-brand-token-summary, echo=FALSE}
cat(sprintf(
  "Tokenization: %s tokens from %s documents.\n",
  format(nrow(tokens), big.mark = ","),
  format(n_distinct(tokens$doc_id), big.mark = ",")
))
```

## 5.1 Cross-Brand Bigrams

```{r cross-brand-bigrams, fig.height=8}
bigrams_all <- raw_text %>%
  build_bigrams(all_stop) %>%
  unite("bigram", w1, w2, sep = " ") %>%
  left_join(raw_text %>% select(doc_id, brand), by = "doc_id")

bigrams_all %>%
  count(brand, bigram, sort = TRUE) %>%
  group_by(brand) %>%
  slice_head(n = 12) %>%
  ungroup() %>%
  ggplot(aes(x = reorder_within(bigram, n, brand), y = n, fill = brand)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_brand() +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~brand, scales = "free_y") +
  labs(title = "Top 12 Bigrams by Brand",
       subtitle = "Two-word phrases across the full corpus",
       x = "Bigram", y = "Count")
```

## 5.2 NRC Emotion Breakdown by Brand

Emotion profiles show how each brand is discussed beyond simple positive/negative polarity. Trust and anticipation often dominate sneaker communities, but relative differences matter.

```{r nrc-cross-brand, fig.height=7}
if (nrow(nrc) == 0) {
  placeholder_plot("NRC lexicon unavailable")
} else {
  nrc_pct <- tokens %>%
    inner_join(nrc, by = "word") %>%
    filter(!sentiment %in% c("positive", "negative")) %>%
    count(brand, sentiment, sort = TRUE) %>%
    group_by(brand) %>%
    mutate(pct = n / sum(n) * 100) %>%
    ungroup()

  ggplot(nrc_pct, aes(x = reorder(sentiment, pct), y = pct, fill = brand)) +
    geom_col(position = "dodge", alpha = 0.85) +
    scale_fill_brand() +
    coord_flip() +
    labs(title = "Emotion Profile by Brand (NRC)",
         subtitle = "Percentage of emotion-tagged tokens within each brand",
         x = "Emotion", y = "% of Emotion Tokens", fill = "Brand")
}
```

## 5.3 Bing Sentiment by Brand and Source

Average document-level Bing sentiment is the main metric for H1. The bar chart includes the sample size so we can judge how stable each estimate is.

```{r sentiment-brand-plot, fig.height=5}
brand_sentiment <- sentiment_scored %>%
  group_by(brand) %>%
  summarise(avg_sentiment    = mean(sentiment_score, na.rm = TRUE),
            median_sentiment = median(sentiment_score, na.rm = TRUE),
            docs             = n(),
            .groups = "drop")

ggplot(brand_sentiment, aes(x = reorder(brand, avg_sentiment), y = avg_sentiment, fill = brand)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_brand() +
  geom_text(
    aes(label = sprintf("%.2f (n=%s)", avg_sentiment, format(docs, big.mark = ","))),
    hjust = -0.1, size = 4
  ) +
  coord_flip() +
  labs(title = "Average Bing Sentiment Score by Brand",
       subtitle = "Positive = net positive language; Negative = net negative language",
       x = NULL, y = "Average Sentiment Score") +
  expand_limits(y = max(abs(brand_sentiment$avg_sentiment)) * 1.5)
```

```{r sentiment-by-source, fig.height=5}
source_sentiment <- sentiment_scored %>%
  group_by(brand, source) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE), docs = n(), .groups = "drop") %>%
  filter(docs >= MIN_DOC_COUNT)

if (nrow(source_sentiment) > 1 && n_distinct(source_sentiment$source) > 1) {
  ggplot(source_sentiment, aes(x = reorder(source, avg_sentiment), y = avg_sentiment, fill = brand)) +
    geom_col(position = "dodge", alpha = 0.85) +
    scale_fill_brand() +
    coord_flip() +
    labs(title = "Sentiment by Source and Brand",
         subtitle = "Comparing Reddit vs YouTube",
         x = "Source", y = "Avg Sentiment", fill = "Brand")
}
```

------------------------------------------------------------------------

# 6. Brand Differentiation (TF-IDF)

TF-IDF surfaces terms that are distinctive to each brand's conversation. High TF-IDF means the term appears often for that brand but rarely for the others.

```{r tfidf-brand, fig.height=8}
tfidf_brand <- tokens %>%
  count(brand, stem) %>%
  bind_tf_idf(term = stem, document = brand, n = n) %>%
  group_by(brand) %>%
  slice_max(tf_idf, n = TOP_N_TERMS) %>%
  ungroup()

ggplot(tfidf_brand, aes(x = reorder_within(stem, tf_idf, brand), y = tf_idf, fill = brand)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_brand() +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~brand, scales = "free_y") +
  labs(title = "Brand Differentiation: Unique Terms (TF-IDF)",
       subtitle = "Terms that distinguish each brand's customer language",
       x = "Stemmed Term", y = "TF-IDF Score")
```

```{r tfidf-table}
tfidf_brand %>%
  group_by(Brand = brand) %>%
  slice_max(tf_idf, n = 10) %>%
  summarise(`Distinctive Terms` = paste(stem, collapse = ", "), .groups = "drop") %>%
  kable(caption = "Top 10 Distinguishing Terms per Brand (TF-IDF)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

------------------------------------------------------------------------

# 7. Executive Synthesis

## Hypothesis Verdicts

```{r hypothesis-verdicts}
# Pull computed values for inline narrative
nike_sent  <- brand_sentiment %>% filter(brand == "Nike") %>% pull(avg_sentiment) %>% round(2)
adi_sent   <- brand_sentiment %>% filter(brand == "Adidas") %>% pull(avg_sentiment) %>% round(2)
ua_sent    <- brand_sentiment %>% filter(brand == "Under Armour") %>% pull(avg_sentiment) %>% round(2)

nike_sus_pct <- sus_summary %>% filter(brand == "Nike") %>% pull(sustainability_pct)
nike_gw_pct  <- sus_summary %>% filter(brand == "Nike") %>% pull(greenwash_pct)

price_yes_avg <- price_flagged %>% filter(has_price_mention) %>% pull(sentiment_score) %>% mean(na.rm = TRUE) %>% round(2)
price_no_avg  <- price_flagged %>% filter(!has_price_mention) %>% pull(sentiment_score) %>% mean(na.rm = TRUE) %>% round(2)
```

**H1 -- Brand Perception: `r ifelse(nike_sent > 0, "Supported", "Not supported")`.**
Nike's average Bing sentiment is `r nike_sent`, which is positive but trails Adidas (`r adi_sent`) and sits above Under Armour (`r ua_sent`). The sentiment ranking is Adidas > Nike > Under Armour. Nike sentiment is positive overall, and as the "Sentiment by Source and Brand" plot shows, scores do shift between Reddit and YouTube, confirming channel-level variation. However, Nike does not lead the three brands -- Adidas edges it out. H1 is supported in its claim of positive overall sentiment and channel variation, but the assumption that Nike leads is not borne out.

**H2 -- Product Strategy: Supported.**
The "Top Negative Terms in Nike Product Comments" and "Product Feature Sentiment Impact" charts confirm that complaint language clusters around sizing ("small," "tight"), comfort ("uncomfortable"), and durability ("cheap," "break," "tear"). The "Complaint Context Bigrams" chart adds phrase-level detail. Negative product-feature language is concentrated, not diffuse, which means targeted QA fixes can address it.

**H3 -- Sustainability: Partially supported.**
As shown in the sustainability summary table, sustainability terms appear in `r nike_sus_pct`% of Nike documents, while greenwashing terms appear in `r nike_gw_pct`%. Both vocabularies are present, confirming polarization, but greenwashing language is relatively rare compared to sustainability mentions. The ratio suggests Nike's sustainability messaging mostly resonates, though a small but real skepticism signal exists.

**H4 -- Price--Sentiment Link: Supported.**
Comments mentioning price terms average `r price_yes_avg` sentiment vs. `r price_no_avg` for non-price comments -- a notable gap. The "Pricing Sentiment by Product Line" and "Pricing Sentiment by Product Category" plots further show that the effect is not uniform across lines. H4 is supported: price language is associated with weaker sentiment.

## Findings Summary

The table below is generated directly from computed objects to maintain traceability.

```{r findings-summary}
findings <- tibble(
  `#` = 1:4,
  `Strategic Pillar` = c("Brand Perception", "Product Strategy",
                         "Sustainability", "Pricing Sentiment"),
  `Key Finding` = c(
    sprintf("Nike avg sentiment = %.2f vs Adidas = %.2f and UA = %.2f (Bing). Adidas leads; Nike is positive but second. Trust and anticipation dominate Nike's NRC emotion profile.",
            nike_sent, adi_sent, ua_sent),
    "Negative language in product comments concentrates on sizing, comfort, and durability stems. Complaint bigrams confirm phrase-level patterns (e.g., 'runs small').",
    sprintf("Sustainability terms appear in %.1f%% of Nike docs; greenwashing in %.1f%%. Both are present but greenwashing is much less common -- messaging is mostly landing.",
            nike_sus_pct, nike_gw_pct),
    sprintf("Price-mentioning comments average %.2f sentiment vs %.2f for non-price -- a %.2f point gap. Pricing language does cluster with weaker sentiment.",
            price_yes_avg, price_no_avg, price_no_avg - price_yes_avg)
  ),
  Recommendation = c(
    "Monitor trust-related sentiment by channel. Investigate why Adidas scores slightly higher -- it may reflect product mix or community composition rather than true brand strength.",
    "Prioritize QA on product lines with recurring sizing and durability complaints. A standardized fit guide could reduce 'runs small' frustrations.",
    "Continue sustainability efforts and proactively address skepticism with verifiable product-level evidence. The greenwashing signal is small but worth watching.",
    "Reframe premium pricing around value-for-performance rather than prestige. The gap is meaningful but not extreme -- messaging refinement, not a pricing overhaul, is warranted."
  )
)

findings %>%
  kable(caption = "Strategic Findings and Recommendations") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE) %>%
  column_spec(3, width = "40%") %>%
  column_spec(4, width = "30%")
```

## Recommendations by Pillar

### Brand Strategy

-   **Emotional drivers:** Trust, anticipation, and joy are Nike's strongest NRC associations. Campaign narratives should lean into these emotions.
-   **Trust vs. price tension:** A measurable segment trusts Nike quality but notes high prices. Messaging should reframe cost as "investment in performance."
-   **Competitive gap:** Adidas edges Nike on average Bing sentiment. Investigate whether this reflects product satisfaction differences or community sampling effects before acting on it.

### Product Operations

-   **Sizing inconsistencies:** Bigrams like "runs small" and "size chart" appear frequently. Recommend a standardized fit guide and closer monitoring of size-related returns.
-   **Durability language:** "Cheap," "break," and "tear" surface in negative product documents. Flag the implicated lines for QA review.
-   **Delivery signals:** Some negative clusters mention availability and fulfillment terms, suggesting supply-chain friction worth tracking.

### Sustainability

-   **Greenwashing risk is low but present:** At `r nike_gw_pct`% of documents, greenwashing language is a small minority, but proactive transparency -- connecting claims to specific materials or processes -- can keep it from growing.
-   **Messaging alignment:** Ensure public sustainability claims are backed by product-level evidence that customers can verify.

### Pricing

-   **Price--sentiment gap:** The `r round(price_no_avg - price_yes_avg, 2)`-point gap between price-mentioning and non-price comments is real but not catastrophic. It calls for messaging refinement, not deep discounting.
-   **Value communication:** Link pricing narratives to durability, performance, and long-term use rather than status alone.

------------------------------------------------------------------------

# 8. Limitations and Ethics

| \# | Limitation | Impact | Mitigation |
|----|-----------|--------|-----------|
| 1 | **Sampling bias** | Reddit skews younger/male/US; YouTube toward engaged sneaker fans. Neither represents all Nike customers. | Triangulate both sources; note demographic skew in all recommendations. |
| 2 | **Manipulated content** | Astroturfing or coordinated voting can distort Reddit sentiment. Lexicon methods cannot detect this. | Flag short/repetitive comments; disclose limitation to stakeholders. |
| 3 | **Lexicon limits** | Dictionary methods miss sarcasm, negation ("not great"), and sneaker slang. | Supplement with classification models and manual spot-checks for production use. |
| 4 | **Temporal snapshot** | Data reflects recent posts only; no historical trend analysis is possible. | Disclose recency window; recommend longitudinal monitoring. |
| 5 | **Proxy ratings** | Reddit upvotes and YouTube likes are engagement signals, not quality ratings. | Label as engagement-based proxy; recommend collecting actual star ratings for validation. |
| 6 | **Ethics** | User-generated content collected without explicit analytics consent. | Remove personal identifiers; comply with platform ToS; do not republish individual comments. |
| 7 | **English only** | Excludes global markets (China, Latin America, Europe). | Note geographic scope limitation. |

> All findings should be treated as directional signals from two English-language online communities, not as statistically representative of Nike's full customer base. We recommend a follow-up quantitative survey to validate the top hypotheses before major strategic decisions.

------------------------------------------------------------------------

# 9. Appendix: Session Info

```{r session-info}
sessionInfo()
```

------------------------------------------------------------------------

*End of Technical Appendix -- Team 6*
