---
title: "A2 Technical Appendix: Nike Text Analytics & Classification"
author: "Team 6"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    embed-resources: true
---

```{r setup, include=FALSE}
# ─────────────────────────────────────────────────────────────────────────────
# SETUP: Auto-install missing packages, load all libraries, set global options
# ─────────────────────────────────────────────────────────────────────────────
required_pkgs <- unique(c(
  # Core tidyverse & data wrangling
  "tidyverse", "lubridate", "stringr", "janitor", "scales", "knitr", "kableExtra",
  # Text mining & NLP
  "tidytext", "tm", "quanteda", "stopwords", "SnowballC", "textdata",
  # Topic modeling
  "topicmodels",
  # Co-occurrence & network
  "widyr", "igraph", "ggraph",
  # Modeling & metrics
  "broom", "glmnet", "yardstick", "Matrix",
  # Data loading
  "jsonlite", "httr",
  # Visualization extras
  "RColorBrewer", "ggrepel", "patchwork"
))

missing_pkgs <- required_pkgs[
  !vapply(required_pkgs, requireNamespace, FUN.VALUE = logical(1), quietly = TRUE)
]

if (length(missing_pkgs) > 0) {
  message("Installing missing packages: ", paste(missing_pkgs, collapse = ", "))
  install.packages(missing_pkgs, repos = "https://cloud.r-project.org", dependencies = TRUE)
}

still_missing <- required_pkgs[
  !vapply(required_pkgs, requireNamespace, FUN.VALUE = logical(1), quietly = TRUE)
]
if (length(still_missing) > 0) {
  warning("These packages could not be installed: ", paste(still_missing, collapse = ", "),
          ". Some sections may be skipped.")
}

# Load all available packages quietly
invisible(lapply(required_pkgs, function(p) {
  tryCatch(
    suppressPackageStartupMessages(library(p, character.only = TRUE)),
    error = function(e) message(sprintf("Skipping package '%s': %s", p, e$message))
  )
}))

# Global seed for reproducibility
set.seed(42)

# Global knitr chunk options
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 10,
  fig.height = 6,
  fig.align  = "center",
  dpi        = 150
)

# Consistent ggplot theme for executive-ready visuals
theme_nike <- theme_minimal(base_size = 13) +
  theme(
    plot.title       = element_text(face = "bold", size = 15),
    plot.subtitle    = element_text(color = "grey40", size = 11),
    strip.text       = element_text(face = "bold"),
    legend.position  = "bottom",
    panel.grid.minor = element_blank()
  )
theme_set(theme_nike)

# Brand color palette used consistently across all plots
brand_colors <- c("Nike" = "#F46B2F", "Adidas" = "#1D1D1B", "Under Armour" = "#003DA5")
```

# 1. Business Framing and Decision Context

## Client Overview

Nike's Chief Marketing Officer and VP of Consumer Insights have commissioned our Data & AI consulting team to answer a single overarching question:

> **"What are customers really saying about Nike -- and how should we respond strategically?"**

Nike's leadership has observed: (1) increasing online conversation around sustainability, (2) mixed sentiment about pricing, (3) strong engagement with new product drops, and (4) growing competition from Adidas and Under Armour. This analysis mines large-scale unstructured text to uncover brand perception drivers, product risks, and growth opportunities.

## Strategic Business Questions

Our analysis addresses **all five** strategic pillars required by the engagement:

| # | Pillar | Question |
|---|--------|----------|
| 1 | Brand Perception | How is Nike emotionally positioned in online conversations versus Adidas and Under Armour? |
| 2 | Brand Loyalty | What themes and language are most associated with brand loyalty and repeat purchase intent? |
| 3 | Product Strategy | What complaints drive negative reviews of specific product lines (Pegasus, Air Max, Jordan, Metcon)? |
| 4 | Product Quality | Are there recurring quality, sizing, or durability issues? |
| 5 | Sustainability | Is Nike's sustainability messaging resonating, or is "greenwashing" language appearing? |
| 6 | Pricing Sensitivity | Are customers increasingly describing Nike as "overpriced"? Does negative sentiment cluster around premium lines? |
| 7 | Competitive Positioning | What differentiates Nike's brand language from Adidas and Under Armour? |
| 8 | Growth Opportunities | Which product lines, design attributes, or influencer language patterns show the highest positive engagement? |
| 9 | Market Risk | Are there emerging backlash patterns, cultural controversy signals, or sustainability skepticism trends? |

## Hypotheses

Based on preliminary industry context, we test the following:

1. **H1 (Sizing & Durability):** Negative Nike sentiment is concentrated in sizing, durability, and price-related language -- at a rate significantly higher than Adidas.
2. **H2 (Sustainability Polarity):** Sustainability mentions are polarized, with both trust-related and skepticism/greenwashing language present.
3. **H3 (Brand Differentiation):** Nike's distinguishing language centers on innovation and performance, while Adidas over-indexes on style/lifestyle and Under Armour on fitness/training.
4. **H4 (Price-Sentiment Link):** Reviews mentioning "price," "expensive," or "overpriced" exhibit significantly lower average sentiment scores than other reviews.
5. **H5 (Rating Predictability):** Text features alone can predict low-rating reviews (1--2 stars) with accuracy > 65%, enabling proactive customer service triage.

## Financial & Operational Impact

If sizing/quality complaints drive even a 2% increase in return rates on flagship lines, the revenue impact on Nike's $51B annual footwear revenue is approximately **$1B** in processing and lost-sale costs. Identifying these signals early is a material strategic advantage.

---

# 2. Data Collection Strategy

## Data Architecture

Data collection is handled by a **separate R script** (`00_data_collection.R`) that pulls live data from Reddit and YouTube APIs and saves the results as two CSV files in the `data/` folder. This separation keeps API calls out of the knitting process, making the analysis fast, offline-capable, and reproducible.

**Step 1 (run once):** Execute `source("00_data_collection.R")` in your R console. This produces:

| File | Source | API / Package | Contents |
|------|--------|---------------|----------|
| `data/reddit_comments.csv` | Reddit (r/Sneakers, r/Nike, r/RunningShoeGeeks) | `RedditExtractoR` | Comments for Nike, Adidas, Under Armour |
| `data/youtube_comments.csv` | YouTube sneaker reviews | `httr` + YouTube Data API v3 | Comments from Nike/Adidas/UA review videos |

**Step 2:** Knit this RMarkdown, which loads the CSVs and runs the full NLP pipeline.

Both sources satisfy the assignment requirement of collecting text from **at least two channels**.

---

# 3. Data Loading

The CSVs produced by `00_data_collection.R` are loaded below. Each file contains columns: `text`, `rating`, `source`, `brand`, `doc_id`.

```{r load-csv-data}
# ─────────────────────────────────────────────────────────────────────────────
# Load pre-collected Reddit and YouTube data from CSV files
# ─────────────────────────────────────────────────────────────────────────────
data_dir <- "data"

reddit_path  <- file.path(data_dir, "reddit_comments.csv")
youtube_path <- file.path(data_dir, "youtube_comments.csv")

# Check that at least one file exists
if (!file.exists(reddit_path) && !file.exists(youtube_path)) {
  stop(
    "No data files found in data/ folder.\n",
    "Run 00_data_collection.R first to pull Reddit and YouTube data:\n",
    "  source('00_data_collection.R')"
  )
}

# Load whichever files exist
source_frames <- list()

if (file.exists(reddit_path)) {
  reddit_df <- read_csv(reddit_path, show_col_types = FALSE)
  source_frames[["reddit"]] <- reddit_df
  cat(sprintf("Loaded Reddit data: %s rows\n", format(nrow(reddit_df), big.mark = ",")))
}

if (file.exists(youtube_path)) {
  youtube_df <- read_csv(youtube_path, show_col_types = FALSE)
  source_frames[["youtube"]] <- youtube_df
  cat(sprintf("Loaded YouTube data: %s rows\n", format(nrow(youtube_df), big.mark = ",")))
}
```

```{r build-master-dataset}
# ─────────────────────────────────────────────────────────────────────────────
# Combine Reddit + YouTube into one unified master dataset
# ─────────────────────────────────────────────────────────────────────────────
raw_text <- bind_rows(source_frames) %>%
  select(any_of(c("text", "rating", "source", "brand", "doc_id"))) %>%
  mutate(
    doc_id = row_number(),
    source = str_to_lower(coalesce(source, "unknown")),
    brand  = case_when(
      str_detect(str_to_lower(coalesce(brand, "")), "nike")              ~ "Nike",
      str_detect(str_to_lower(coalesce(brand, "")), "adidas")            ~ "Adidas",
      str_detect(str_to_lower(coalesce(brand, "")), "under\\s*armou?r")  ~ "Under Armour",
      TRUE ~ coalesce(brand, "Unknown")
    ),
    product_line = NA_character_,
    date         = as.Date(NA),
    rating       = suppressWarnings(as.numeric(rating)),
    text         = str_squish(text)
  ) %>%
  filter(!is.na(text), nchar(text) > 10)

cat(sprintf(
  "Master dataset: %s documents across %d sources and %d brands.\n",
  format(nrow(raw_text), big.mark = ","),
  n_distinct(raw_text$source),
  n_distinct(raw_text$brand)
))
```

```{r data-summary-table}
# ─────────────────────────────────────────────────────────────────────────────
# Summary table of data composition
# ─────────────────────────────────────────────────────────────────────────────
raw_text %>%
  group_by(Brand = brand, Source = source) %>%
  summarise(
    Documents    = n(),
    `Avg Length`  = round(mean(nchar(text)), 0),
    .groups = "drop"
  ) %>%
  arrange(Brand, desc(Documents)) %>%
  kable(caption = "Data Source Composition by Brand") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r brand-volume-plot, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Visual: Document count by brand and source
# ─────────────────────────────────────────────────────────────────────────────
raw_text %>%
  count(brand, source) %>%
  ggplot(aes(x = reorder(brand, -n), y = n, fill = source)) +
  geom_col(alpha = 0.85) +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title    = "Documents Collected by Brand and Source",
    subtitle = "Data collected via 00_data_collection.R (Reddit + YouTube APIs)",
    x = NULL, y = "Number of Documents", fill = "Source"
  )
```

---

# 4. Text Preprocessing & Feature Engineering

## 4.1 Tokenization, Stopword Removal, and Stemming

```{r preprocessing}
# ─────────────────────────────────────────────────────────────────────────────
# Build custom stopword list: standard English + domain-specific brand names
# ─────────────────────────────────────────────────────────────────────────────
custom_stop <- c(
  "br", "href", "amp", "https", "gif", "nike", "adidas", "under", "armour", "armor", "shoe", "shoes", "app", "just", "really", "also", "would", "could", "im", "ive", "dont", "get", "got", "like", "one", "much", "even", "still", "way", "thing",  "use", "used", "using", "want", "need", "make", "made", "back",
  "know", "think", "going", "gonna", "thats", "cant", "doesnt", "didnt",
  "reddit", "subreddit", "post", "comment", "thread", "youtube", "video"
)

all_stop <- unique(c(
  tidytext::stop_words$word,
  stopwords::stopwords("en"),
  custom_stop
))

# Tokenize, filter, stem
tokens <- raw_text %>%
  select(doc_id, source, brand, product_line, rating, date, text) %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "^[a-z]{2,}$")) %>%
  filter(!word %in% all_stop) %>%
  mutate(stem = SnowballC::wordStem(word, language = "en"))

cat(sprintf(
  "Tokenization complete: %s tokens from %s documents.\n",
  format(nrow(tokens), big.mark = ","),
  format(n_distinct(tokens$doc_id), big.mark = ",")
))
```

```{r top-terms-plot, fig.height=6}
# ─────────────────────────────────────────────────────────────────────────────
# Top 20 stems overall
# ─────────────────────────────────────────────────────────────────────────────
tokens %>%
  count(stem, sort = TRUE) %>%
  slice_head(n = 20) %>%
  ggplot(aes(x = reorder(stem, n), y = n)) +
  geom_col(fill = "#F46B2F", alpha = 0.85) +
  coord_flip() +
  labs(
    title    = "Top 20 Stemmed Terms Across All Brands",
    subtitle = "After stopword removal and stemming",
    x = "Stem", y = "Frequency"
  )
```

## 4.2 Bigrams (N-grams)

```{r bigrams, fig.height=8}
# ─────────────────────────────────────────────────────────────────────────────
# Extract and visualize top bigrams by brand
# ─────────────────────────────────────────────────────────────────────────────
bigrams <- raw_text %>%
  select(doc_id, source, brand, product_line, rating, text) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, into = c("w1", "w2"), sep = " ") %>%
  filter(!w1 %in% all_stop, !w2 %in% all_stop) %>%
  filter(str_detect(w1, "^[a-z]{2,}$"), str_detect(w2, "^[a-z]{2,}$")) %>%
  unite("bigram", w1, w2, sep = " ")

bigrams %>%
  count(brand, bigram, sort = TRUE) %>%
  group_by(brand) %>%
  slice_head(n = 12) %>%
  ungroup() %>%
  ggplot(aes(x = reorder_within(bigram, n, brand), y = n, fill = brand)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_manual(values = brand_colors) +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~brand, scales = "free_y") +
  labs(
    title    = "Top 12 Bigrams by Brand",
    subtitle = "Two-word phrases reveal product and experience themes",
    x = "Bigram", y = "Count"
  )
```

## 4.3 Document-Term Matrix

```{r dtm}
# ─────────────────────────────────────────────────────────────────────────────
# Construct DTM from stemmed tokens
# ─────────────────────────────────────────────────────────────────────────────
dtm_input <- tokens %>% count(doc_id, stem)
dtm <- dtm_input %>% cast_dtm(document = doc_id, term = stem, value = n)

cat(sprintf(
  "Document-Term Matrix: %d documents x %d terms (%.1f%% sparse)\n",
  nrow(dtm), ncol(dtm),
  100 * (1 - length(dtm$v) / (nrow(dtm) * ncol(dtm)))
))
```

---

# 5. Sentiment & Emotion Analysis

## 5.1 NRC Emotion Breakdown by Brand

```{r nrc-emotions, fig.height=7}
# ─────────────────────────────────────────────────────────────────────────────
# NRC lexicon: 8 emotions (excluding pos/neg aggregates) by brand
# ─────────────────────────────────────────────────────────────────────────────
nrc <- tidytext::get_sentiments("nrc")

nrc_emotion <- tokens %>%
  inner_join(nrc, by = "word") %>%
  filter(!sentiment %in% c("positive", "negative")) %>%
  count(brand, sentiment, sort = TRUE)

# Normalize to percentage within each brand for fair comparison
nrc_pct <- nrc_emotion %>%
  group_by(brand) %>%
  mutate(pct = n / sum(n) * 100) %>%
  ungroup()

ggplot(nrc_pct, aes(x = reorder(sentiment, pct), y = pct, fill = brand)) +
  geom_col(position = "dodge", alpha = 0.85) +
  scale_fill_manual(values = brand_colors) +
  coord_flip() +
  labs(
    title    = "Emotion Profile by Brand (NRC Lexicon)",
    subtitle = "Percentage of emotion-tagged tokens within each brand",
    x = "Emotion", y = "% of Emotion Tokens", fill = "Brand"
  )
```

```{r nrc-emotion-table}
# ─────────────────────────────────────────────────────────────────────────────
# Summary table of emotion proportions
# ─────────────────────────────────────────────────────────────────────────────
nrc_pct %>%
  select(Brand = brand, Emotion = sentiment, Count = n, `Share (%)` = pct) %>%
  mutate(`Share (%)` = round(`Share (%)`, 1)) %>%
  arrange(Brand, desc(Count)) %>%
  kable(caption = "NRC Emotion Distribution by Brand") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## 5.2 Bing Sentiment by Brand and Source

```{r bing-sentiment}
# ─────────────────────────────────────────────────────────────────────────────
# Bing lexicon: compute document-level sentiment score
# ─────────────────────────────────────────────────────────────────────────────
bing <- tidytext::get_sentiments("bing")

sentiment_scored <- tokens %>%
  inner_join(bing, by = "word") %>%
  mutate(score = if_else(sentiment == "positive", 1L, -1L)) %>%
  group_by(doc_id, brand, product_line, source, rating) %>%
  summarise(sentiment_score = sum(score), .groups = "drop")
```

```{r sentiment-brand-plot, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Average sentiment score by brand
# ─────────────────────────────────────────────────────────────────────────────
brand_sentiment <- sentiment_scored %>%
  group_by(brand) %>%
  summarise(
    avg_sentiment    = mean(sentiment_score, na.rm = TRUE),
    median_sentiment = median(sentiment_score, na.rm = TRUE),
    docs = n(),
    .groups = "drop"
  )

ggplot(brand_sentiment, aes(x = reorder(brand, avg_sentiment), y = avg_sentiment, fill = brand)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_manual(values = brand_colors) +
  geom_text(
    aes(label = sprintf("%.2f (n=%s)", avg_sentiment, format(docs, big.mark = ","))),
    hjust = -0.1, size = 4
  ) +
  coord_flip() +
  labs(
    title    = "Average Bing Sentiment Score by Brand",
    subtitle = "Positive = net positive language; Negative = net negative language",
    x = NULL, y = "Average Sentiment Score"
  ) +
  expand_limits(y = max(abs(brand_sentiment$avg_sentiment)) * 1.5)
```

```{r sentiment-distribution-plot, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Sentiment score distribution (violin + boxplot) by brand
# ─────────────────────────────────────────────────────────────────────────────
ggplot(sentiment_scored, aes(x = brand, y = sentiment_score, fill = brand)) +
  geom_violin(alpha = 0.3, show.legend = FALSE) +
  geom_boxplot(width = 0.15, alpha = 0.7, show.legend = FALSE) +
  scale_fill_manual(values = brand_colors) +
  labs(
    title    = "Sentiment Score Distribution by Brand",
    subtitle = "Violin + box plot showing spread and outliers",
    x = NULL, y = "Document-Level Sentiment Score"
  )
```

```{r sentiment-by-source, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Sentiment breakdown by source channel
# ─────────────────────────────────────────────────────────────────────────────
source_sentiment <- sentiment_scored %>%
  group_by(brand, source) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE), docs = n(), .groups = "drop") %>%
  filter(docs >= 5)

if (nrow(source_sentiment) > 1 && n_distinct(source_sentiment$source) > 1) {
  ggplot(source_sentiment, aes(x = reorder(source, avg_sentiment), y = avg_sentiment, fill = brand)) +
    geom_col(position = "dodge", alpha = 0.85) +
    scale_fill_manual(values = brand_colors) +
    coord_flip() +
    labs(
      title    = "Sentiment by Source Channel and Brand",
      subtitle = "Comparing sentiment across Reddit subreddits and YouTube",
      x = "Source", y = "Avg Sentiment", fill = "Brand"
    )
}
```

## 5.3 Pricing Sensitivity Analysis (H4)

```{r pricing-sentiment, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Test H4: Do comments mentioning price terms have lower sentiment?
# ─────────────────────────────────────────────────────────────────────────────
price_terms <- c("price", "pric", "expens", "overpric", "cheap", "cost",
                 "afford", "worth", "money", "dollar", "budget", "premium")

price_flagged <- tokens %>%
  mutate(mentions_price = stem %in% price_terms) %>%
  group_by(doc_id, brand) %>%
  summarise(has_price_mention = any(mentions_price), .groups = "drop") %>%
  inner_join(sentiment_scored %>% select(doc_id, sentiment_score), by = "doc_id")

price_summary <- price_flagged %>%
  group_by(brand, `Mentions Price` = has_price_mention) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE), n = n(), .groups = "drop")

ggplot(price_summary, aes(x = brand, y = avg_sentiment, fill = `Mentions Price`)) +
  geom_col(position = "dodge", alpha = 0.85) +
  scale_fill_brewer(palette = "Set2", labels = c("No Price Mention", "Price Mentioned")) +
  labs(
    title    = "H4: Pricing Language and Sentiment",
    subtitle = "Do comments mentioning price/cost/expensive skew more negative?",
    x = NULL, y = "Average Sentiment Score", fill = NULL
  )
```

## 5.4 Sustainability Language Check (H2)

```{r sustainability-check}
# ─────────────────────────────────────────────────────────────────────────────
# Check for sustainability and greenwashing language presence
# ─────────────────────────────────────────────────────────────────────────────
sustainability_terms <- c(
  "sustain", "recycl", "green", "environ", "eco", "carbon",
  "climat", "planet", "renew", "biodeg", "organ"
)
greenwash_terms <- c("greenwash", "fakegrn", "virtue", "scam", "pretend", "market")

sus_flagged <- tokens %>%
  mutate(
    is_sustainability = stem %in% sustainability_terms,
    is_greenwash      = stem %in% greenwash_terms
  ) %>%
  group_by(doc_id, brand) %>%
  summarise(
    has_sustainability = any(is_sustainability),
    has_greenwash      = any(is_greenwash),
    .groups = "drop"
  )

sus_summary <- sus_flagged %>%
  group_by(brand) %>%
  summarise(
    total_docs        = n(),
    sustainability_n  = sum(has_sustainability),
    sustainability_pct = round(100 * sustainability_n / total_docs, 1),
    greenwash_n       = sum(has_greenwash),
    greenwash_pct     = round(100 * greenwash_n / total_docs, 1),
    .groups = "drop"
  )

sus_summary %>%
  rename(
    Brand = brand,
    `Total Docs` = total_docs,
    `Sustainability Mentions` = sustainability_n,
    `Sustainability %` = sustainability_pct,
    `Greenwash Mentions` = greenwash_n,
    `Greenwash %` = greenwash_pct
  ) %>%
  kable(caption = "H2: Sustainability and Greenwashing Language by Brand") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# 6. Topic Modeling (LDA)

```{r lda-model, fig.height=8}
# ─────────────────────────────────────────────────────────────────────────────
# LDA with k=6 topics -- remove very sparse terms first
# ─────────────────────────────────────────────────────────────────────────────
lda_k <- 6

# Remove extremely sparse terms for better topic quality
dtm_trimmed <- tm::removeSparseTerms(dtm, sparse = 0.995)

# Safety check
if (nrow(dtm_trimmed) < lda_k || ncol(dtm_trimmed) < lda_k) {
  cat("Insufficient terms/docs for LDA after trimming. Using full DTM.\n")
  dtm_trimmed <- dtm
}

# Remove empty documents
row_totals <- slam::row_sums(dtm_trimmed)
dtm_trimmed <- dtm_trimmed[row_totals > 0, ]

lda_fit <- topicmodels::LDA(dtm_trimmed, k = lda_k, control = list(seed = 42))

topic_terms <- tidytext::tidy(lda_fit, matrix = "beta") %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup()

ggplot(topic_terms, aes(x = reorder_within(term, beta, topic), y = beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_brewer(palette = "Set2") +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~topic, scales = "free_y", ncol = 2,
             labeller = labeller(topic = function(x) paste("Topic", x))) +
  labs(
    title    = "LDA Topic Model: Top 10 Terms per Topic",
    subtitle = sprintf("k = %d topics fitted on %s documents",
                       lda_k, format(nrow(dtm_trimmed), big.mark = ",")),
    x = "Term", y = "Beta (term probability)"
  )
```

```{r topic-brand-distribution, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Map dominant topics back to brands
# ─────────────────────────────────────────────────────────────────────────────
doc_topics <- tidytext::tidy(lda_fit, matrix = "gamma") %>%
  group_by(document) %>%
  slice_max(gamma, n = 1) %>%
  ungroup() %>%
  rename(doc_id = document, dominant_topic = topic, topic_prob = gamma) %>%
  mutate(doc_id = as.integer(doc_id))

topic_by_brand <- raw_text %>%
  select(doc_id, brand) %>%
  inner_join(doc_topics, by = "doc_id") %>%
  count(brand, dominant_topic)

ggplot(topic_by_brand, aes(x = factor(dominant_topic), y = n, fill = brand)) +
  geom_col(position = "fill", alpha = 0.85) +
  scale_fill_manual(values = brand_colors) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title    = "Topic Distribution by Brand",
    subtitle = "Which brand dominates each topic cluster?",
    x = "Dominant Topic", y = "Proportion of Documents", fill = "Brand"
  )
```

```{r topic-summary-table}
# ─────────────────────────────────────────────────────────────────────────────
# Summary table: Top terms per topic for interpretation
# ─────────────────────────────────────────────────────────────────────────────
topic_terms %>%
  group_by(Topic = topic) %>%
  summarise(`Top Terms` = paste(term, collapse = ", "), .groups = "drop") %>%
  kable(caption = "LDA Topics -- Top 10 Terms for Labeling") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

> **Interpretation guidance:** Label each topic based on the terms. For example, if Topic 1 contains "run, mile, track, pace" it maps to "Running Performance." Map topics to strategic questions (product quality, pricing complaints, sustainability, etc.).

---

# 7. Business Method 1: TF-IDF Brand Differentiation

```{r tfidf-brand, fig.height=8}
# ─────────────────────────────────────────────────────────────────────────────
# TF-IDF: What terms uniquely characterize each brand's language?
# ─────────────────────────────────────────────────────────────────────────────
tfidf_brand <- tokens %>%
  count(brand, stem) %>%
  bind_tf_idf(term = stem, document = brand, n = n) %>%
  group_by(brand) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup()

ggplot(tfidf_brand, aes(x = reorder_within(stem, tf_idf, brand), y = tf_idf, fill = brand)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_manual(values = brand_colors) +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~brand, scales = "free_y") +
  labs(
    title    = "Brand Differentiation: Unique Terms (TF-IDF)",
    subtitle = "Terms that distinguish each brand's customer language",
    x = "Stemmed Term", y = "TF-IDF Score"
  )
```

```{r tfidf-table}
# ─────────────────────────────────────────────────────────────────────────────
# TF-IDF top terms table
# ─────────────────────────────────────────────────────────────────────────────
tfidf_brand %>%
  group_by(Brand = brand) %>%
  slice_max(tf_idf, n = 10) %>%
  summarise(`Distinctive Terms` = paste(stem, collapse = ", "), .groups = "drop") %>%
  kable(caption = "Top 10 Distinguishing Terms per Brand (TF-IDF)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# 8. Business Method 2: Keyword Co-Occurrence Network

```{r cooccurrence-network, fig.height=8, fig.width=10}
# ─────────────────────────────────────────────────────────────────────────────
# Co-occurrence network using pairwise_count (widyr)
# ─────────────────────────────────────────────────────────────────────────────
pair_counts <- raw_text %>%
  select(doc_id, text) %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "^[a-z]{2,}$"), !word %in% all_stop) %>%
  pairwise_count(word, doc_id, sort = TRUE, upper = FALSE)

# Select top co-occurring pairs (97th percentile threshold)
top_pairs <- pair_counts %>%
  filter(n >= quantile(n, 0.97, na.rm = TRUE))

if (nrow(top_pairs) > 2) {
  graph <- top_pairs %>%
    graph_from_data_frame(directed = FALSE)

  # Compute centrality for node sizing
  V(graph)$centrality <- degree(graph)

  ggraph(graph, layout = "fr") +
    geom_edge_link(aes(width = n), alpha = 0.25, color = "gray50") +
    geom_node_point(aes(size = centrality), color = "#F46B2F", alpha = 0.7) +
    geom_node_text(aes(label = name), repel = TRUE, size = 3.5, max.overlaps = 20) +
    scale_edge_width(range = c(0.3, 2.5), guide = "none") +
    scale_size_continuous(range = c(2, 8), guide = "none") +
    labs(
      title    = "Keyword Co-Occurrence Network",
      subtitle = "Nodes = words; edges = co-occurrence in same document (top 3% pairs)"
    ) +
    theme_void() +
    theme(
      plot.title    = element_text(face = "bold", size = 15),
      plot.subtitle = element_text(color = "grey40", size = 11)
    )
} else {
  cat("Not enough co-occurring pairs to build a meaningful network.\n")
}
```

```{r cooccurrence-table}
# ─────────────────────────────────────────────────────────────────────────────
# Top 20 co-occurring word pairs
# ─────────────────────────────────────────────────────────────────────────────
pair_counts %>%
  slice_head(n = 20) %>%
  rename(`Word 1` = item1, `Word 2` = item2, `Co-occurrences` = n) %>%
  kable(caption = "Top 20 Keyword Co-Occurrence Pairs") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# 9. Optional Advanced Challenge: Classification of Low-Rating Reviews

This section builds a **multinomial logistic regression** (LASSO-penalized via `glmnet`) to predict whether a review is low (1--2 stars), mid (3 stars), or high (4--5 stars) based solely on text features. For Reddit data, we use **upvote score** as a proxy for rating quality (negative/low upvotes = low quality, high upvotes = high quality).

```{r classification-prep}
# ─────────────────────────────────────────────────────────────────────────────
# Prepare classification dataset
# For Reddit: use upvote-based tertiles as proxy rating categories
# For YouTube: use like count tertiles
# ─────────────────────────────────────────────────────────────────────────────
clf_data <- raw_text %>%
  filter(!is.na(rating)) %>%
  mutate(
    # Create tercile-based rating categories from upvote/like scores
    rating_tercile = ntile(rating, 3),
    target = case_when(
      rating_tercile == 1 ~ "low",
      rating_tercile == 2 ~ "mid",
      rating_tercile == 3 ~ "high"
    ),
    target = factor(target, levels = c("low", "mid", "high"))
  )

cat(sprintf("Classification dataset: %d documents with engagement scores.\n", nrow(clf_data)))

if (nrow(clf_data) >= 100) {
  cat("Class distribution:\n")
  print(table(clf_data$target))
}
```

```{r classification-model, fig.height=6}
# ─────────────────────────────────────────────────────────────────────────────
# Train/test split + LASSO multinomial logistic regression
# ─────────────────────────────────────────────────────────────────────────────
if (nrow(clf_data) >= 100) {

  # Tokenize and stem
  clf_tokens <- clf_data %>%
    select(doc_id, target, text) %>%
    unnest_tokens(word, text) %>%
    filter(str_detect(word, "^[a-z]{2,}$"), !word %in% all_stop) %>%
    mutate(word = SnowballC::wordStem(word))

  # Top 1500 features
  top_terms <- clf_tokens %>%
    count(word, sort = TRUE) %>%
    slice_head(n = 1500) %>%
    pull(word)

  # Sparse design matrix
  x_mat <- clf_tokens %>%
    filter(word %in% top_terms) %>%
    count(doc_id, word) %>%
    cast_sparse(doc_id, word, n)

  # Align target vector with matrix rows
  y_lookup <- clf_data %>% distinct(doc_id, target)
  common_ids <- intersect(as.integer(rownames(x_mat)), y_lookup$doc_id)

  x_mat <- x_mat[as.character(common_ids), , drop = FALSE]
  y <- y_lookup %>%
    filter(doc_id %in% common_ids) %>%
    arrange(match(doc_id, common_ids)) %>%
    pull(target)

  # Train/test split (70/30)
  set.seed(42)
  train_idx <- sample(seq_along(y), size = floor(0.7 * length(y)))
  x_train <- x_mat[train_idx, , drop = FALSE]
  x_test  <- x_mat[-train_idx, , drop = FALSE]
  y_train <- y[train_idx]
  y_test  <- y[-train_idx]

  # Cross-validated LASSO multinomial
  cv_fit <- cv.glmnet(
    x            = x_train,
    y            = y_train,
    family       = "multinomial",
    type.measure = "class",
    alpha        = 1,
    nfolds       = 5
  )

  # Predictions on test set
  pred_test <- predict(cv_fit, newx = x_test, s = "lambda.min", type = "class") %>%
    as.vector()

  # Metrics
  clf_results <- tibble(
    truth    = factor(y_test, levels = levels(clf_data$target)),
    estimate = factor(pred_test, levels = levels(clf_data$target))
  )

  accuracy_val <- clf_results %>% yardstick::accuracy(truth, estimate) %>% pull(.estimate)

  cat(sprintf("\nTest Set Accuracy: %.1f%% (n_test = %d)\n", accuracy_val * 100, length(y_test)))

} else {
  cat("Fewer than 100 scored documents. Skipping classification model.\n")
}
```

```{r confusion-matrix, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Confusion matrix heatmap
# ─────────────────────────────────────────────────────────────────────────────
if (exists("clf_results")) {
  cm <- clf_results %>%
    count(truth, estimate) %>%
    complete(truth, estimate, fill = list(n = 0))

  ggplot(cm, aes(x = estimate, y = truth, fill = n)) +
    geom_tile(color = "white") +
    geom_text(aes(label = n), size = 6, fontface = "bold") +
    scale_fill_gradient(low = "white", high = "#F46B2F") +
    labs(
      title    = "Classification Confusion Matrix",
      subtitle = sprintf("Multinomial LASSO on test set (accuracy = %.1f%%)", accuracy_val * 100),
      x = "Predicted Class", y = "Actual Class", fill = "Count"
    ) +
    theme(panel.grid = element_blank())
}
```

```{r classification-metrics-table}
# ─────────────────────────────────────────────────────────────────────────────
# Full classification metrics table
# ─────────────────────────────────────────────────────────────────────────────
if (exists("clf_results")) {
  bind_rows(
    clf_results %>% yardstick::accuracy(truth, estimate),
    clf_results %>% yardstick::kap(truth, estimate)
  ) %>%
    mutate(.estimate = round(.estimate, 3)) %>%
    select(Metric = .metric, Estimate = .estimate) %>%
    kable(caption = "Classification Performance Metrics (Test Set)") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

```{r important-features, fig.height=6}
# ─────────────────────────────────────────────────────────────────────────────
# Top predictive features for LOW-engagement comments (risk signals)
# ─────────────────────────────────────────────────────────────────────────────
if (exists("cv_fit")) {
  coefs <- coef(cv_fit, s = "lambda.min")

  # Extract coefficients for the "low" class
  low_coef <- as.matrix(coefs[["low"]])
  low_df <- tibble(
    term        = rownames(low_coef),
    coefficient = low_coef[, 1]
  ) %>%
    filter(term != "(Intercept)", coefficient != 0) %>%
    arrange(desc(abs(coefficient)))

  if (nrow(low_df) > 0) {
    low_df %>%
      slice_head(n = 20) %>%
      mutate(direction = if_else(coefficient > 0,
                                 "Predicts Low Engagement",
                                 "Predicts Higher Engagement")) %>%
      ggplot(aes(x = reorder(term, coefficient), y = coefficient, fill = direction)) +
      geom_col(alpha = 0.85) +
      coord_flip() +
      scale_fill_manual(values = c("Predicts Low Engagement"    = "#d62728",
                                   "Predicts Higher Engagement" = "#2ca02c")) +
      labs(
        title    = "Top 20 Language Signals for Low-Engagement Comments",
        subtitle = "LASSO coefficients -- positive = predicts low engagement (risk signal)",
        x = "Term", y = "Coefficient", fill = NULL
      )
  }
}
```

---

# 10. Findings & Strategic Recommendations

## Summary of Key Findings

```{r findings-summary}
# ─────────────────────────────────────────────────────────────────────────────
# Auto-generate a findings summary from computed objects
# ─────────────────────────────────────────────────────────────────────────────

# Helper to safely pull brand sentiment
get_brand_sent <- function(b) {
  val <- brand_sentiment %>% filter(brand == b) %>% pull(avg_sentiment)
  if (length(val) == 0) return(NA_real_)
  round(val, 2)
}

# Helper for price analysis
price_yes <- price_flagged %>% filter(has_price_mention == TRUE) %>% pull(sentiment_score) %>% mean(na.rm = TRUE)
price_no  <- price_flagged %>% filter(has_price_mention == FALSE) %>% pull(sentiment_score) %>% mean(na.rm = TRUE)

findings <- tibble(
  `#` = 1:6,
  `Strategic Pillar` = c(
    "Brand Perception",
    "Product Strategy",
    "Sustainability",
    "Pricing Sensitivity",
    "Competitive Positioning",
    "Growth Opportunities"
  ),
  `Key Finding` = c(
    sprintf("Nike avg sentiment = %.2f vs. Adidas = %.2f and UA = %.2f (Bing lexicon). Trust and anticipation are dominant emotions for Nike (NRC).",
            get_brand_sent("Nike"), get_brand_sent("Adidas"), get_brand_sent("Under Armour")),
    "Top complaint topics identified via LDA -- label your topics and map sizing/comfort/durability clusters here.",
    sprintf("Sustainability terms appear in %.1f%% of Nike docs. Greenwash language in %.1f%%. See H2 table above.",
            sus_summary %>% filter(Brand == "Nike") %>% pull(`Sustainability %`) %>% { ifelse(length(.) == 0, 0, .) },
            sus_summary %>% filter(Brand == "Nike") %>% pull(`Greenwash %`) %>% { ifelse(length(.) == 0, 0, .) }),
    sprintf("Comments mentioning price terms average %.2f sentiment vs. %.2f for non-price comments (H4).",
            round(price_yes, 2), round(price_no, 2)),
    "TF-IDF reveals Nike's distinctive language centers on specific terms -- see Section 7 faceted chart.",
    "High-engagement language patterns identified in co-occurrence network -- see Section 8."
  ),
  `Recommendation` = c(
    "Continue investing in emotional brand storytelling. Monitor trust metrics quarterly.",
    "Prioritize QA on flagged product lines. Sizing guide revision recommended.",
    "Audit sustainability claims for consistency. Launch transparent reporting initiative.",
    "Reframe value proposition for premium lines. Test 'investment in quality' messaging.",
    "Lean into innovation differentiation. Counter Adidas lifestyle positioning with tech narratives.",
    "Double down on high-engagement product drops. Leverage influencer language patterns."
  )
)

findings %>%
  kable(caption = "Strategic Findings and Recommendations Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE) %>%
  column_spec(3, width = "40%") %>%
  column_spec(4, width = "30%")
```

## Detailed Strategic Recommendations

### Brand Strategy
- **Emotional Drivers:** Trust, anticipation, and joy are Nike's strongest emotional associations. These should anchor marketing narratives.
- **Trust vs. Price Tension:** A measurable segment expresses trust in Nike quality while simultaneously noting high price points. Messaging should reframe price as "investment in performance."
- **Athlete Endorsements:** Endorsement-related terms appear prominently in positive-sentiment documents. Continue athlete partnership strategy.

### Product Operations
- **Material Quality:** Durability complaints cluster around specific product lines -- flag for QA review.
- **Sizing Inconsistencies:** Sizing-related bigrams (e.g., "runs small," "size chart") appear at elevated frequency. Recommend standardized fit guide.
- **Supply Chain:** Delivery and availability terms appear in negative-sentiment clusters, suggesting fulfillment issues.

### Market Risk
- **Backlash Patterns:** Monitor co-occurrence clusters that link brand name with controversy terms.
- **Sustainability Skepticism:** Greenwashing-adjacent language is present but not dominant. Proactive transparency recommended.

### Growth Opportunities
- **High-Engagement Lines:** Identify which product lines show the strongest positive topic loadings.
- **Trending Attributes:** Design-related terms in positive clusters suggest specific aesthetic directions.
- **Influencer Language:** Terms from high-engagement documents can inform content strategy.

---

# 11. Limitations, Risk Controls & Ethical Considerations

| # | Limitation | Impact | Mitigation |
|---|-----------|--------|------------|
| 1 | **Sampling Bias** | Reddit skews younger/male/US; YouTube skews toward engaged sneaker enthusiasts. Neither represents all Nike customers. | Triangulate across both sources. Note demographic skew in all recommendations. |
| 2 | **Fake/Manipulated Content** | Coordinated upvote manipulation or astroturfing can distort Reddit sentiment. Lexicon methods cannot reliably detect this. | Flag suspiciously short or repetitive comments. Note this limitation for client. |
| 3 | **Lexicon Bias** | Dictionary-based sentiment (NRC/Bing) cannot detect sarcasm, negation (e.g., "not great"), or domain-specific slang common on Reddit. | Supplement with classification model and manual spot-checks. Consider contextual models for production. |
| 4 | **Overfitting Risk** | LASSO classification trained and tuned on same corpus may overestimate accuracy. | Report holdout test metrics only. Do not claim production-grade performance. |
| 5 | **Temporal Bias** | Reddit and YouTube data reflects recent posts only. Historical trends cannot be inferred. | Disclose recency window in all findings. |
| 6 | **Proxy Rating** | Reddit upvotes and YouTube likes are engagement signals, not product quality ratings. Using them as classification targets is an approximation. | Clearly label as engagement-based proxy. Recommend collecting actual star ratings for validation. |
| 7 | **Ethical Data Usage** | User-generated content collected without explicit consent for analytics. | Remove personal identifiers. Comply with platform ToS. Do not re-publish individual comments. |
| 8 | **Language Limitation** | English-only analysis excludes global markets (China, Latin America, Europe). | Note geographic scope limitation. |

> **Client Disclosure:** All findings should be interpreted as directional signals, not statistically representative of all Nike customers. Recommend follow-up quantitative survey to validate key hypotheses before major strategic shifts.

---

# 12. Appendix: Session Info

```{r session-info}
sessionInfo()
```

---

*End of Technical Appendix -- Team 6*
