---
title: "A2: Nike Text Analytics & Classification Modeling"
author: "Team 6"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
format:
    html:
        theme: 
            light: flatly
            dark: darkly
        highlight-style: github
        code-fold: true
        code-tools: 
            source: true
            toggle: true
            # caption: none
        code-copy: true
        self-contained: true
        html-math-method: katex
        embed-resources: true
        code-overflow: wrap
        smooth-scroll: true       
        page-layout: full
        toc: true
        toc-location: right
        lightbox: true
   #  ipynb: default
   #  pdf: default
---

```{r setup, include=FALSE}
# ─────────────────────────────────────────────────────────────────────────────
# SETUP: Auto-install missing packages, load all libraries, set global options
# ─────────────────────────────────────────────────────────────────────────────
required_pkgs <- unique(c(
  # Core tidyverse & data wrangling
  "tidyverse", "lubridate", "stringr", "janitor", "scales", "knitr", "kableExtra",
  # Text mining & NLP
  "tidytext", "tm", "quanteda", "stopwords", "SnowballC", "textdata", "topicmodels",
  # Co-occurrence & network
  "widyr", "igraph", "ggraph",
  # Modeling & metrics
  "broom", "glmnet", "yardstick", "Matrix", "slam",
  # Data loading
  "jsonlite", "httr", "rappdirs",
  # Visualization extras
  "RColorBrewer", "ggrepel", "patchwork"
))

missing_pkgs <- required_pkgs[
  !vapply(required_pkgs, requireNamespace, FUN.VALUE = logical(1), quietly = TRUE)
]

if (length(missing_pkgs) > 0) {
  message("Installing missing packages: ", paste(missing_pkgs, collapse = ", "))
  install.packages(missing_pkgs, repos = "https://cloud.r-project.org", dependencies = TRUE)
}

still_missing <- required_pkgs[
  !vapply(required_pkgs, requireNamespace, FUN.VALUE = logical(1), quietly = TRUE)
]
if (length(still_missing) > 0) {
  warning("These packages could not be installed: ", paste(still_missing, collapse = ", "),
          ". Some sections may be skipped.")
}

# Load all available packages quietly
invisible(lapply(required_pkgs, function(p) {
  tryCatch(
    suppressPackageStartupMessages(library(p, character.only = TRUE)),
    error = function(e) message(sprintf("Skipping package '%s': %s", p, e$message))
  )
}))

# Global seed for reproducibility
set.seed(42)

# Global knitr chunk options
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 10,
  fig.height = 6,
  fig.align  = "center",
  dpi        = 150
)

# Consistent ggplot theme for executive-ready visuals
theme_nike <- theme_minimal(base_size = 13) +
  theme(
    plot.title       = element_text(face = "bold", size = 15),
    plot.subtitle    = element_text(color = "grey40", size = 11),
    strip.text       = element_text(face = "bold"),
    legend.position  = "bottom",
    panel.grid.minor = element_blank()
  )
theme_set(theme_nike)

# Centralized palettes used across the notebook
nike_accent <- "#F46B2F"
brand_colors <- c("Nike" = nike_accent, "Adidas" = "#1D1D1B", "Under Armour" = "#003DA5")
source_colors <- c("reddit" = "#4E79A7", "youtube" = "#E15759", "unknown" = "#76B7B2")
lexicon_colors <- c("AFINN" = nike_accent, "Bing" = "#4E79A7", "NRC" = "#59A14F")
vocab_palette <- c("Sustainability" = "#2E8B57", "Greenwashing" = "#B22222")
price_focus_color <- nike_accent
topic_palette <- c("1" = "#F28E2B", "2" = "#4E79A7", "3" = "#59A14F",
                   "4" = "#E15759", "5" = "#76B7B2", "6" = "#EDC948")

scale_fill_brand <- function(...) {
  scale_fill_manual(values = brand_colors, ...)
}

scale_fill_source <- function(...) {
  scale_fill_manual(values = source_colors, ...)
}

scale_fill_lexicon <- function(...) {
  scale_fill_manual(values = lexicon_colors, ...)
}

scale_fill_topic <- function(...) {
  scale_fill_manual(values = topic_palette, ...)
}

# Pre-cache textdata lexicons to avoid interactive menu() prompts during render
ensure_textdata_lexicon <- function(data_name, rds_name) {
  if (!requireNamespace("textdata", quietly = TRUE)) return(FALSE)

  cache_dir <- file.path(rappdirs::user_cache_dir("textdata"), data_name)
  rds_path  <- file.path(cache_dir, rds_name)

  if (file.exists(rds_path)) return(TRUE)

  dir.create(cache_dir, recursive = TRUE, showWarnings = FALSE)

  tryCatch({
    if (length(list.files(cache_dir)) == 0) {
      textdata:::download_functions[[data_name]](cache_dir)
    }
    textdata:::process_functions[[data_name]](cache_dir, rds_path)
    TRUE
  }, error = function(e) {
    message(sprintf(
      "Could not pre-cache '%s' lexicon: %s. Render will continue with fallback behavior.",
      data_name, e$message
    ))
    FALSE
  })
}

if (!interactive()) {
  invisible(ensure_textdata_lexicon("nrc", "NRCWordEmotion.rds"))
  invisible(ensure_textdata_lexicon("bing", "bing.rds"))
}
```

## How to Read This Notebook

This notebook follows a decision pipeline from business framing to recommendations:

1.  **Context and hypotheses** define the decisions we need to support.
2.  **Data pipeline and ingestion** establish what was collected and how it is standardized.
3.  **Nike baseline (Phase 1)** provides a focused single-brand view.
4.  **Cross-brand diagnostics (Phases 2-6)** expand to comparative NLP, sentiment, topics, and networks.
5.  **Executive synthesis** consolidates findings into practical actions for Nike leadership.

# 1. Executive Brief and Decision Context

## Client Overview

Nike's Chief Marketing Officer and VP of Consumer Insights have commissioned our Data & AI consulting team to answer a single overarching question:

> **"What are customers really saying about Nike -- and how should we respond strategically?"**

Nike's leadership has observed: (1) increasing online conversation around sustainability, (2) mixed sentiment about pricing, (3) recurring complaints around fit and durability in key product lines, and (4) uneven sentiment across channels. This analysis mines large-scale unstructured text to uncover brand perception drivers and product risks.

## Strategic Business Questions

Our analysis is scoped to the following **four business questions**:

| \# | Pillar | Question |
|------------------------|------------------------|------------------------|
| 1 | Brand Perception | What is the overall sentiment toward Nike across online conversations? |
| 2 | Product Strategy | Which Nike product lines are most associated with negative traits (e.g., sizing, durability, comfort)? |
| 3 | Sustainability | Is Nike's sustainability messaging resonating, or is greenwashing language appearing? |
| 4 | Pricing Sentiment | Are customers describing Nike as overpriced, and does pricing language cluster with negative sentiment? |

## Hypotheses

Based on preliminary industry context, we test the following:

1.  **H1 (Brand Perception):** Nike's net sentiment is positive overall, but varies meaningfully by source channel.
2.  **H2 (Product Strategy):** Negative Nike sentiment is concentrated in product-trait language related to sizing, durability, and comfort.
3.  **H3 (Sustainability Polarity):** Sustainability mentions are polarized, with both trust-related and skepticism/greenwashing language present.
4.  **H4 (Price-Sentiment Link):** Reviews mentioning "price," "expensive," or "overpriced" exhibit lower average sentiment scores than other reviews.

## Financial & Operational Impact

If sizing and quality complaints drive even a 2% increase in return rates on flagship lines, the revenue impact on Nike's \$51B annual footwear revenue is approximately **\$1B** in processing and lost-sale costs. Identifying these signals early is a material strategic advantage.

------------------------------------------------------------------------

# 2. Data Pipeline and Collection Design

## Data Architecture

Data collection is handled by a separate R script (`00_data_collection.R`) that pulls live data from Reddit and YouTube APIs and saves the results as two CSV files in the `data/` folder. Keeping collection separate from rendering makes the analysis faster, offline-capable, and reproducible.

**Step 1 (run once):** Execute `source("00_data_collection.R")` in your R console. This produces:

| File | Source | API / Package | Contents |
|------------------|------------------|------------------|------------------|
| `data/reddit_comments.csv` | Reddit (r/Sneakers, r/Nike, r/RunningShoeGeeks) | `RedditExtractoR` | Comments for Nike, Adidas, Under Armour |
| `data/youtube_comments.csv` | YouTube sneaker reviews | `httr` + YouTube Data API v3 | Comments from Nike/Adidas/UA review videos |

**Step 2:** Render this Quarto file, which loads the CSVs and runs the full NLP pipeline.

Both sources satisfy the assignment requirement of collecting text from **at least two channels**.

------------------------------------------------------------------------

# 3. Data Ingestion and Quality Checks

The CSVs produced by `00_data_collection.R` are loaded below. Each file contains columns: `text`, `rating`, `source`, `brand`, `doc_id`.

This section performs three steps in sequence: load each source, combine into a standardized master table, and validate composition by brand/source.

```{r load-csv-data}
# ─────────────────────────────────────────────────────────────────────────────
# Load pre-collected Reddit and YouTube data from CSV files
# ─────────────────────────────────────────────────────────────────────────────
# data_dir <- "data"
# reddit_path  <- file.path(data_dir, "reddit_comments.csv")
# youtube_path <- file.path(data_dir, "youtube_comments.csv")

# GitHub raw URLs (data files + external term lists)
github_data_base_url <- "https://raw.githubusercontent.com/renan-peres/mban-unstructured-data/refs/heads/main/%23A2%20-%20Nike%20Text%20Analytics%20(N-Aible%20Simulator)/data"
reddit_url                  <- paste0(github_data_base_url, "/reddit_comments.csv")
youtube_url                 <- paste0(github_data_base_url, "/youtube_comments.csv")
github_custom_stopwords_url <- paste0(github_data_base_url, "/custom_stopwords.txt")
github_sustainability_url   <- paste0(github_data_base_url, "/sustainability_terms.txt")
github_greenwashing_url     <- paste0(github_data_base_url, "/greenwashing_terms.txt")
github_product_segments     <- paste0(github_data_base_url, "/nike_product_segments.txt")

# Read and normalize external terms from GitHub text files
read_terms_from_github <- function(url, label, stem = FALSE) {
  raw_lines <- tryCatch(
    readr::read_lines(url, progress = FALSE),
    error = function(e) {
      stop(sprintf("Failed to load %s from GitHub URL '%s': %s", label, url, e$message))
    }
  )

  parsed <- raw_lines %>%
    stringr::str_replace_all("#.*$", "") %>%
    stringr::str_split(pattern = "[,;]") %>%
    purrr::flatten_chr() %>%
    stringr::str_trim() %>%
    purrr::discard(~ .x == "")

  if (length(parsed) == 0) {
    stop(sprintf("GitHub terms file for %s is empty: %s", label, url))
  }

  terms <- tolower(parsed)
  if (stem) {
    terms <- SnowballC::wordStem(terms, language = "en")
  }

  unique(terms)
}

source_frames <- list()

# Load Reddit
cat("Loading Reddit data...\n")
reddit_df <- tryCatch(
  read_csv(reddit_url, show_col_types = FALSE),
  error = function(e) {
    cat("  Reddit CSV failed:", e$message, "\n")
    NULL
  }
)

if (!is.null(reddit_df)) {
  source_frames[["reddit"]] <- reddit_df
  cat(sprintf("✓ Reddit: %s rows\n", format(nrow(reddit_df), big.mark = ",")))
}

# Load YouTube
cat("Loading YouTube data...\n")
youtube_df <- tryCatch(
  read_csv(youtube_url, show_col_types = FALSE),
  error = function(e) {
    cat("  YouTube CSV failed:", e$message, "\n")
    NULL
  }
)

if (!is.null(youtube_df)) {
  source_frames[["youtube"]] <- youtube_df
  cat(sprintf("✓ YouTube: %s rows\n", format(nrow(youtube_df), big.mark = ",")))
}

# Final check
if (length(source_frames) == 0) {
  stop("No data loaded. URLs may be invalid or files don't exist on GitHub.")
}

# ─────────────────────────────────────────────────────────────────────────────
# Check for sustainability and greenwashing language presence
# ─────────────────────────────────────────────────────────────────────────────
sustainability_terms <- read_terms_from_github(
  url = github_sustainability_url,
  label = "sustainability terms",
  stem = TRUE
)
greenwash_terms <- read_terms_from_github(
  url = github_greenwashing_url,
  label = "greenwashing terms",
  stem = TRUE
)

nike_product_segments <- read_terms_from_github(
  url = github_product_segments,
  label = "product segments",
  stem = TRUE
)

cat(sprintf("\n✓ Loaded %d sources total\n", length(source_frames)))
```

```{r build-master-dataset}
# ─────────────────────────────────────────────────────────────────────────────
# Combine Reddit + YouTube into one unified master dataset
# ─────────────────────────────────────────────────────────────────────────────
raw_text <- bind_rows(source_frames) %>%
  select(any_of(c("text", "rating", "source", "brand", "doc_id"))) %>%
  mutate(
    doc_id = row_number(),
    source = str_to_lower(coalesce(source, "unknown")),
    brand  = case_when(
      str_detect(str_to_lower(coalesce(brand, "")), "nike")              ~ "Nike",
      str_detect(str_to_lower(coalesce(brand, "")), "adidas")            ~ "Adidas",
      str_detect(str_to_lower(coalesce(brand, "")), "under\\s*armou?r")  ~ "Under Armour",
      TRUE ~ coalesce(brand, "Unknown")
    ),
    product_line = NA_character_,
    date         = as.Date(NA),
    rating       = suppressWarnings(as.numeric(rating)),
    text         = str_squish(text)
  ) %>%
  filter(!is.na(text), nchar(text) > 10)

cat(sprintf(
  "Master dataset: %s documents across %d sources and %d brands.\n",
  format(nrow(raw_text), big.mark = ","),
  n_distinct(raw_text$source),
  n_distinct(raw_text$brand)
))

# Load shared stopword resources once so the same custom list applies
# to Nike-only and full-corpus analyses.
custom_stop <- read_terms_from_github(
  url = github_custom_stopwords_url,
  label = "custom stopwords",
  stem = FALSE
)

all_stop <- unique(c(
  tidytext::stop_words$word,
  stopwords::stopwords("en"),
  custom_stop
))

cat(sprintf(
  "Loaded %s custom stopwords for full-corpus preprocessing.\n",
  format(length(custom_stop), big.mark = ",")
))
```

```{r analysis-primitives}
# ─────────────────────────────────────────────────────────────────────────────
# Build shared analysis objects once so downstream sections can reuse them
# regardless of narrative order in the report.
# ─────────────────────────────────────────────────────────────────────────────
tokens <- raw_text %>%
  select(doc_id, source, brand, product_line, rating, date, text) %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "^[a-z]{2,}$")) %>%
  filter(!word %in% all_stop) %>%
  mutate(
    word = if_else(word == "nmds", "nmd", word),
    stem = SnowballC::wordStem(word, language = "en"),
    stem = if_else(stem == "nmds", "nmd", stem)
  )

bing <- tryCatch(
  tidytext::get_sentiments("bing"),
  error = function(e) {
    stop(
      "Failed to load Bing lexicon in non-interactive mode. ",
      "Run once with internet access to populate the textdata cache. Original error: ",
      e$message
    )
  }
)

sentiment_scored <- tokens %>%
  inner_join(bing, by = "word") %>%
  mutate(score = if_else(sentiment == "positive", 1L, -1L)) %>%
  group_by(doc_id, brand, product_line, source, rating) %>%
  summarise(sentiment_score = sum(score), .groups = "drop")

cat(sprintf(
  "Shared analysis objects ready: %s tokens and %s sentiment-scored documents.\n",
  format(nrow(tokens), big.mark = ","),
  format(nrow(sentiment_scored), big.mark = ",")
))
```

```{r data-summary-table}
# ─────────────────────────────────────────────────────────────────────────────
# Summary table of data composition
# ─────────────────────────────────────────────────────────────────────────────
raw_text %>%
  group_by(Brand = brand, Source = source) %>%
  summarise(
    Documents    = n(),
    `Avg Length`  = round(mean(nchar(text)), 0),
    .groups = "drop"
  ) %>%
  arrange(Brand, desc(Documents)) %>%
  kable(caption = "Data Source Composition by Brand") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r brand-volume-plot, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Visual: Document count by brand and source
# ─────────────────────────────────────────────────────────────────────────────
raw_text %>%
  count(brand, source) %>%
  ggplot(aes(x = reorder(brand, -n), y = n, fill = source)) +
  geom_col(alpha = 0.85) +
  scale_fill_source() +
  labs(
    title    = "Documents Collected by Brand and Source",
    subtitle = "Data collected via 00_data_collection.R (Reddit + YouTube APIs)",
    x = NULL, y = "Number of Documents", fill = "Source"
  )
```

------------------------------------------------------------------------

# 4. Phase 1: Nike Baseline

To align with the core Nike use case in this codebase, we first run a focused Nike-only baseline before the cross-brand comparisons.

```{r nike-only-baseline}
# ─────────────────────────────────────────────────────────────────────────────
# Nike-only baseline view before cross-brand comparisons
# ─────────────────────────────────────────────────────────────────────────────
nike_text <- raw_text %>%
  filter(brand == "Nike")

if (nrow(nike_text) == 0) {
  stop("No Nike documents found after data loading and brand normalization.")
}

nike_all_stop <- all_stop

nike_tokens <- nike_text %>%
  select(doc_id, source, rating, text) %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "^[a-z]{2,}$")) %>%
  filter(!word %in% nike_all_stop) %>%
  mutate(
    word = if_else(word == "nmds", "nmd", word),
    stem = SnowballC::wordStem(word, language = "en"),
    stem = if_else(stem == "nmds", "nmd", stem)
  )

cat(sprintf(
  "Nike-only baseline: %s documents and %s cleaned tokens.\n",
  format(nrow(nike_text), big.mark = ","),
  format(nrow(nike_tokens), big.mark = ",")
))
```

```{r nike-only-summary-table}
# ─────────────────────────────────────────────────────────────────────────────
# Nike-only source summary
# ─────────────────────────────────────────────────────────────────────────────
nike_text %>%
  group_by(Source = source) %>%
  summarise(
    Documents = n(),
    `Avg Length` = round(mean(nchar(text)), 0),
    `Avg Rating` = round(mean(rating, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  arrange(desc(Documents)) %>%
  kable(caption = "Nike-Only Baseline Summary by Source") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## 4.1 Top Frequent Terms

The first diagnostic highlights dominant term stems in Nike-only documents to identify core conversation themes.

```{r nike-only-top-terms, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Top terms for Nike-only baseline
# ─────────────────────────────────────────────────────────────────────────────
nike_tokens %>%
  count(stem, sort = TRUE) %>%
  slice_head(n = 15) %>%
  ggplot(aes(x = reorder(stem, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.85) +
  coord_flip() +
  labs(
    title = "Nike-Only Baseline: Top 15 Stemmed Terms",
    subtitle = "Before switching to cross-brand comparative analysis",
    x = "Stem", y = "Frequency"
  )
```

## 4.2 Lexicon Sentiment Snapshot

We then compare sentiment lexicons to ensure directional consistency before scaling to cross-brand sentiment diagnostics.

```{r nike-only-nrc, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Nike-only emotion profile using NRC lexicon
# ─────────────────────────────────────────────────────────────────────────────
nrc_nike <- tryCatch(
  tidytext::get_sentiments("nrc"),
  error = function(e) {
    message("NRC lexicon unavailable in Nike-only section: ", e$message)
    tibble(word = character(), sentiment = character())
  }
)

if (nrow(nrc_nike) == 0) {
  nike_nrc_pct <- tibble(sentiment = character(), n = integer(), pct = numeric())

  ggplot() +
    ggplot2::annotate("text", x = 0, y = 0, label = "NRC lexicon unavailable for Nike-only section") +
    theme_void()
} else {
  nike_nrc_pct <- nike_tokens %>%
    inner_join(nrc_nike, by = "word") %>%
    filter(!sentiment %in% c("positive", "negative")) %>%
    count(sentiment, sort = TRUE) %>%
    mutate(pct = 100 * n / sum(n))

  ggplot(nike_nrc_pct, aes(x = reorder(sentiment, pct), y = pct)) +
    geom_col(fill = nike_accent, alpha = 0.85) +
    coord_flip() +
    labs(
      title = "Nike-Only Emotion Profile (NRC)",
      subtitle = "Share of emotion-tagged tokens in Nike documents",
      x = "Emotion", y = "% of Emotion Tokens"
    )
}
```

```{r nike-lexicon-comparison, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Compare sentiment totals across AFINN, Bing, and NRC (Netflix-style chart)
# ─────────────────────────────────────────────────────────────────────────────
afinn_nike <- tryCatch(
  tidytext::get_sentiments("afinn"),
  error = function(e) {
    afinn_url <- "https://raw.githubusercontent.com/fnielsen/afinn/master/afinn/data/AFINN-111.txt"
    tryCatch(
      readr::read_tsv(
        afinn_url,
        col_names = c("word", "value"),
        show_col_types = FALSE,
        progress = FALSE
      ),
      error = function(e2) tibble(word = character(), value = numeric())
    )
  }
)

bing_nike <- tryCatch(
  tidytext::get_sentiments("bing"),
  error = function(e) tibble(word = character(), sentiment = character())
)

nrc_compare <- if (exists("nrc_nike")) {
  nrc_nike
} else {
  tryCatch(
    tidytext::get_sentiments("nrc"),
    error = function(e) tibble(word = character(), sentiment = character())
  )
}

afinn_compare <- nike_tokens %>%
  inner_join(afinn_nike, by = "word") %>%
  summarise(sentiment = sum(value, na.rm = TRUE)) %>%
  mutate(method = "AFINN")

bing_nrc_compare <- bind_rows(
  nike_tokens %>%
    inner_join(bing_nike, by = "word") %>%
    mutate(method = "Bing"),
  nike_tokens %>%
    inner_join(nrc_compare %>% filter(sentiment %in% c("positive", "negative")), by = "word") %>%
    mutate(method = "NRC")
) %>%
  count(method, sentiment, name = "n") %>%
  tidyr::complete(method, sentiment = c("positive", "negative"), fill = list(n = 0)) %>%
  tidyr::pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(sentiment = positive - negative)

lexicon_compare <- bind_rows(afinn_compare, bing_nrc_compare) %>%
  mutate(method = factor(method, levels = c("AFINN", "Bing", "NRC")))

ggplot(lexicon_compare, aes(method, sentiment, fill = method)) +
  geom_col(show.legend = FALSE, alpha = 0.9) +
  facet_wrap(~method, ncol = 1, scales = "free_y") +
  scale_fill_lexicon() +
  labs(
    title = "Nike Lexicon Comparison: AFINN vs Bing vs NRC",
    subtitle = "Net sentiment totals using the same Nike token corpus",
    x = NULL,
    y = "Net Sentiment"
  )
```


## 4.3 Pricing Sentiment Analysis (H4)

This subsection tests whether price-related language is systematically associated with lower sentiment. The comparative calculations are retained for the executive summary, while the visuals focus only on documents where price is explicitly mentioned.

```{r pricing-sentiment, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Test H4: Do comments mentioning price terms have lower sentiment?
# ─────────────────────────────────────────────────────────────────────────────
price_terms <- c(
  "expensive", "pricey", "overpriced", "ripoff", "scam", "markup", "costly",
  "retail", "standard", "msrp", "normal", "base", "average", "regular",
  "cheap", "affordable", "deal", "steal", "discount", "sale", "budget"
)

price_doc_flags <- tokens %>%
  group_by(doc_id, brand) %>%
  summarise(has_price_mention = any(stem %in% price_terms), .groups = "drop")

price_flagged <- sentiment_scored %>%
  select(doc_id, brand, sentiment_score) %>%
  inner_join(price_doc_flags, by = c("doc_id", "brand"))

price_summary <- price_flagged %>%
  group_by(brand, has_price_mention) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE), n = n(), .groups = "drop")

price_mentioned_summary <- price_summary %>%
  filter(has_price_mention)

ggplot(price_mentioned_summary, aes(x = reorder(brand, avg_sentiment), y = avg_sentiment, fill = brand)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_brand() +
  coord_flip() +
  labs(
    title    = "H4: Sentiment Within Price-Mentioned Comments",
    subtitle = "Average sentiment among comments that explicitly discuss price or cost",
    x = NULL, y = "Average Sentiment Score"
  )
```

```{r nike-pricing-segments, fig.height=5}
nike_doc_segments <- tokens %>%
  filter(brand == "Nike") %>%
  filter(stem %in% nike_product_segments) %>%
  select(doc_id, segment = word) %>%
  distinct()

pricing_by_segment <- sentiment_scored %>%
  filter(brand == "Nike") %>%
  inner_join(nike_doc_segments, by = "doc_id") %>%
  inner_join(
    price_doc_flags %>%
      filter(brand == "Nike", has_price_mention) %>%
      select(doc_id, has_price_mention),
    by = "doc_id"
  )

segment_price_summary <- pricing_by_segment %>%
  group_by(segment) %>%
  summarise(
    avg_sentiment = mean(sentiment_score, na.rm = TRUE),
    doc_count = n(),
    .groups = "drop"
  ) %>%
  mutate(sentiment_band = if_else(avg_sentiment < 0, "Negative", "Non-negative")) %>%
  filter(doc_count >= 3)

ggplot(segment_price_summary, aes(x = reorder(segment, avg_sentiment), y = avg_sentiment, fill = sentiment_band)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  coord_flip() +
  scale_fill_manual(values = c(
    "Negative" = unname(vocab_palette["Greenwashing"]),
    "Non-negative" = price_focus_color
  )) +
  labs(
    title = "Nike Pricing Sentiment by Business Segment",
    subtitle = "Only Nike comments with explicit price mentions are included",
    x = "Product Segment",
    y = "Average Sentiment Score (Bing)"
  ) +
  theme_nike
```

```{r nike-pricing-categories, fig.height=5}
# Map product stems to broader business units
category_map <- c(
  "shoe" = "Footwear", "sneaker" = "Footwear", "run" = "Footwear",
  "jordan" = "Footwear", "dunk" = "Footwear", "max" = "Footwear",
  "shirt" = "Apparel", "hoodi" = "Apparel", "pant" = "Apparel",
  "jacket" = "Apparel", "jersei" = "Apparel", "sock" = "Apparel"
)

nike_doc_categories <- tokens %>%
  filter(brand == "Nike") %>%
  mutate(category = category_map[stem]) %>%
  filter(!is.na(category)) %>%
  select(doc_id, category) %>%
  distinct()

categorized_summary <- sentiment_scored %>%
  filter(brand == "Nike") %>%
  inner_join(nike_doc_categories, by = "doc_id") %>%
  inner_join(
    price_doc_flags %>%
      filter(brand == "Nike", has_price_mention) %>%
      select(doc_id, has_price_mention),
    by = "doc_id"
  ) %>%
  group_by(category) %>%
  summarise(
    avg_sentiment = mean(sentiment_score, na.rm = TRUE),
    doc_count = n(),
    .groups = "drop"
  ) %>%
  filter(doc_count >= 3)

ggplot(categorized_summary, aes(x = category, y = avg_sentiment)) +
  geom_col(fill = price_focus_color, alpha = 0.85) +
  labs(
    title = "Pricing Sentiment: Footwear vs. Apparel",
    subtitle = "Only Nike comments with explicit price mentions are included",
    x = "Business Unit",
    y = "Average Sentiment Score"
  ) +
  theme_nike
```

## 4.4 Sustainability Language Check (H3)

This subsection quantifies sustainability and greenwashing language prevalence, then profiles the Nike-specific vocabulary behind those signals.

```{r sustainability-summary-table}

sus_flagged <- tokens %>%
  mutate(
    is_sustainability = stem %in% sustainability_terms,
    is_greenwash      = stem %in% greenwash_terms
  ) %>%
  group_by(doc_id, brand) %>%
  summarise(
    has_sustainability = any(is_sustainability),
    has_greenwash      = any(is_greenwash),
    .groups = "drop"
  )

sus_summary <- sus_flagged %>%
  group_by(brand) %>%
  summarise(
    total_docs        = n(),
    sustainability_n  = sum(has_sustainability),
    sustainability_pct = round(100 * sustainability_n / total_docs, 1),
    greenwash_n       = sum(has_greenwash),
    greenwash_pct     = round(100 * greenwash_n / total_docs, 1),
    .groups = "drop"
  )

sus_summary %>%
  rename(
    Brand = brand,
    `Total Docs` = total_docs,
    `Sustainability Mentions` = sustainability_n,
    `Sustainability %` = sustainability_pct,
    `Greenwash Mentions` = greenwash_n,
    `Greenwash %` = greenwash_pct
  ) %>%
  kable(caption = "H3: Sustainability and Greenwashing Language by Brand") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r sustainability-vocabulary-plot, fig.height=6}
nike_vocab_sentiment <- bind_rows(
  tokens %>%
    filter(brand == "Nike", stem %in% sustainability_terms) %>%
    count(word, stem, sort = TRUE) %>%
    mutate(Vocabulary = "Sustainability"),
  tokens %>%
    filter(brand == "Nike", stem %in% greenwash_terms) %>%
    count(word, stem, sort = TRUE) %>%
    mutate(Vocabulary = "Greenwashing")
) %>%
  left_join(bing %>% select(word, sentiment), by = c("stem" = "word")) %>%
  mutate(sentiment = replace_na(sentiment, "Not labeled"))

nike_vocab_sentiment %>%
  group_by(Vocabulary) %>%
  slice_head(n = 10) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, Vocabulary)) %>%
  ggplot(aes(x = word, y = n, fill = Vocabulary)) +
  geom_col(show.legend = FALSE, alpha = 0.9) +
  coord_flip() +
  scale_fill_manual(values = vocab_palette) +
  scale_x_reordered() +
  facet_wrap(~Vocabulary, scales = "free_y") +
  labs(
    title = "Nike Sustainability and Greenwashing Vocabulary",
    subtitle = "Top 10 terms in each vocabulary group",
    x = NULL,
    y = "Frequency"
  )
```

```{r sustainability-vocabulary-table}
nike_vocab_sentiment %>%
  group_by(Vocabulary) %>%
  slice_head(n = 10) %>%
  ungroup() %>%
  select(
    Category = Vocabulary,
    Word = word,
    Frequency = n,
    Sentiment = sentiment
  ) %>%
  kable(caption = "Nike Sustainability and Greenwashing Terms with Bing Sentiment Labels") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

------------------------------------------------------------------------

# 5. Phase 2: Cross-Brand NLP Foundation (Nike vs Adidas vs Under Armour)

## 5.1 Tokenization, Stopword Removal, and Stemming

This section reports the reusable `tokens` object already built in the shared analysis setup above.

```{r preprocessing}
# ─────────────────────────────────────────────────────────────────────────────
# Reuse full-corpus tokens built in the shared analysis setup
# ─────────────────────────────────────────────────────────────────────────────
cat(sprintf(
  "Tokenization complete: %s tokens from %s documents.\n",
  format(nrow(tokens), big.mark = ","),
  format(n_distinct(tokens$doc_id), big.mark = ",")
))
```

```{r top-terms-plot, fig.height=6}
# ─────────────────────────────────────────────────────────────────────────────
# Top 20 stems overall
# ─────────────────────────────────────────────────────────────────────────────
tokens %>%
  count(stem, sort = TRUE) %>%
  slice_head(n = 20) %>%
  ggplot(aes(x = reorder(stem, n), y = n)) +
  geom_col(fill = nike_accent, alpha = 0.85) +
  coord_flip() +
  labs(
    title    = "Top 20 Stemmed Terms Across All Brands",
    subtitle = "After stopword removal and stemming",
    x = "Stem", y = "Frequency"
  )
```

## 5.2 Bigrams (N-grams)

Bigrams add phrase-level context, complementing unigram frequencies from the previous step.

```{r bigrams, fig.height=8}
# ─────────────────────────────────────────────────────────────────────────────
# Extract and visualize top bigrams by brand
# ─────────────────────────────────────────────────────────────────────────────
bigrams <- raw_text %>%
  select(doc_id, source, brand, product_line, rating, text) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, into = c("w1", "w2"), sep = " ") %>%
  filter(!w1 %in% all_stop, !w2 %in% all_stop) %>%
  filter(str_detect(w1, "^[a-z]{2,}$"), str_detect(w2, "^[a-z]{2,}$")) %>%
  unite("bigram", w1, w2, sep = " ")

bigrams %>%
  count(brand, bigram, sort = TRUE) %>%
  group_by(brand) %>%
  slice_head(n = 12) %>%
  ungroup() %>%
  ggplot(aes(x = reorder_within(bigram, n, brand), y = n, fill = brand)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_brand() +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~brand, scales = "free_y") +
  labs(
    title    = "Top 12 Bigrams by Brand",
    subtitle = "Two-word phrases reveal product and experience themes",
    x = "Bigram", y = "Count"
  )
```

## 5.3 Document-Term Matrix (DTM)

The DTM provides the sparse matrix representation needed for topic modeling and other term-based methods.

```{r dtm}
# ─────────────────────────────────────────────────────────────────────────────
# Construct DTM from stemmed tokens
# ─────────────────────────────────────────────────────────────────────────────
dtm_input <- tokens %>% count(doc_id, stem)
dtm <- dtm_input %>% cast_dtm(document = doc_id, term = stem, value = n)

cat(sprintf(
  "Document-Term Matrix: %d documents x %d terms (%.1f%% sparse)\n",
  nrow(dtm), ncol(dtm),
  100 * (1 - length(dtm$v) / (nrow(dtm) * ncol(dtm)))
))
```

With a standardized token and matrix foundation in place, we can now test sentiment-related hypotheses across brands.

------------------------------------------------------------------------

# 6. Phase 3: Cross-Brand Sentiment Diagnostics

This section addresses H1, H3, and H4 by combining emotion distributions, document sentiment scores, pricing language, and sustainability/greenwashing signals.

## 6.1 NRC Emotion Breakdown by Brand

We start with emotional composition to understand *how* each brand is discussed, beyond simple positive/negative polarity.

```{r nrc-emotions, fig.height=7}
# ─────────────────────────────────────────────────────────────────────────────
# NRC lexicon: 8 emotions (excluding pos/neg aggregates) by brand
# ─────────────────────────────────────────────────────────────────────────────
nrc <- tryCatch(
  tidytext::get_sentiments("nrc"),
  error = function(e) {
    message("NRC lexicon unavailable in this render: ", e$message)
    tibble(word = character(), sentiment = character())
  }
)

if (nrow(nrc) == 0) {
  nrc_pct <- tibble(
    brand = character(),
    sentiment = character(),
    n = integer(),
    pct = numeric()
  )

  ggplot() +
    ggplot2::annotate("text", x = 0, y = 0, label = "NRC lexicon unavailable for this render") +
    theme_void()
} else {
  nrc_emotion <- tokens %>%
    inner_join(nrc, by = "word") %>%
    filter(!sentiment %in% c("positive", "negative")) %>%
    count(brand, sentiment, sort = TRUE)

  # Normalize to percentage within each brand for fair comparison
  nrc_pct <- nrc_emotion %>%
    group_by(brand) %>%
    mutate(pct = n / sum(n) * 100) %>%
    ungroup()

  ggplot(nrc_pct, aes(x = reorder(sentiment, pct), y = pct, fill = brand)) +
    geom_col(position = "dodge", alpha = 0.85) +
    scale_fill_brand() +
    coord_flip() +
    labs(
      title    = "Emotion Profile by Brand (NRC Lexicon)",
      subtitle = "Percentage of emotion-tagged tokens within each brand",
      x = "Emotion", y = "% of Emotion Tokens", fill = "Brand"
    )
}
```

```{r nrc-emotion-table}
# ─────────────────────────────────────────────────────────────────────────────
# Summary table of emotion proportions
# ─────────────────────────────────────────────────────────────────────────────
if (nrow(nrc_pct) == 0) {
  tibble(Note = "NRC lexicon unavailable for this render") %>%
    kable(caption = "NRC Emotion Distribution by Brand") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
} else {
  nrc_pct %>%
    select(Brand = brand, Emotion = sentiment, Count = n, `Share (%)` = pct) %>%
    mutate(`Share (%)` = round(`Share (%)`, 1)) %>%
    arrange(Brand, desc(Count)) %>%
    kable(caption = "NRC Emotion Distribution by Brand") %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

## 6.2 Bing Sentiment by Brand and Source

Next, we compute document-level sentiment and compare both central tendency and distribution by brand and channel.

```{r bing-sentiment}
# ─────────────────────────────────────────────────────────────────────────────
# Reuse Bing lexicon and document-level sentiment score built upstream
# ─────────────────────────────────────────────────────────────────────────────
cat(sprintf(
  "Bing sentiment scores available for %s documents.\n",
  format(nrow(sentiment_scored), big.mark = ",")
))
```

```{r sentiment-brand-plot, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Average sentiment score by brand
# ─────────────────────────────────────────────────────────────────────────────
brand_sentiment <- sentiment_scored %>%
  group_by(brand) %>%
  summarise(
    avg_sentiment    = mean(sentiment_score, na.rm = TRUE),
    median_sentiment = median(sentiment_score, na.rm = TRUE),
    docs = n(),
    .groups = "drop"
  )

ggplot(brand_sentiment, aes(x = reorder(brand, avg_sentiment), y = avg_sentiment, fill = brand)) +
  geom_col(alpha = 0.85, show.legend = FALSE) +
  scale_fill_brand() +
  geom_text(
    aes(label = sprintf("%.2f (n=%s)", avg_sentiment, format(docs, big.mark = ","))),
    hjust = -0.1, size = 4
  ) +
  coord_flip() +
  labs(
    title    = "Average Bing Sentiment Score by Brand",
    subtitle = "Positive = net positive language; Negative = net negative language",
    x = NULL, y = "Average Sentiment Score"
  ) +
  expand_limits(y = max(abs(brand_sentiment$avg_sentiment)) * 1.5)
```

```{r sentiment-distribution-plot, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Sentiment score distribution (violin + boxplot) by brand
# ─────────────────────────────────────────────────────────────────────────────
ggplot(sentiment_scored, aes(x = brand, y = sentiment_score, fill = brand)) +
  geom_violin(alpha = 0.3, show.legend = FALSE) +
  geom_boxplot(width = 0.15, alpha = 0.7, show.legend = FALSE) +
  scale_fill_brand() +
  labs(
    title    = "Sentiment Score Distribution by Brand",
    subtitle = "Violin + box plot showing spread and outliers",
    x = NULL, y = "Document-Level Sentiment Score"
  )
```

```{r sentiment-by-source, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Sentiment breakdown by source channel
# ─────────────────────────────────────────────────────────────────────────────
source_sentiment <- sentiment_scored %>%
  group_by(brand, source) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE), docs = n(), .groups = "drop") %>%
  filter(docs >= 5)

if (nrow(source_sentiment) > 1 && n_distinct(source_sentiment$source) > 1) {
  ggplot(source_sentiment, aes(x = reorder(source, avg_sentiment), y = avg_sentiment, fill = brand)) +
    geom_col(position = "dodge", alpha = 0.85) +
    scale_fill_brand() +
    coord_flip() +
    labs(
      title    = "Sentiment by Source Channel and Brand",
      subtitle = "Comparing sentiment across Reddit subreddits and YouTube",
      x = "Source", y = "Avg Sentiment", fill = "Brand"
    )
}
```

------------------------------------------------------------------------

# 7. Phase 4: Topic Discovery (LDA)

LDA reveals hidden conversation clusters that are not obvious from sentiment scores alone.

```{r lda-model, fig.height=8}
# ─────────────────────────────────────────────────────────────────────────────
# LDA with k=6 topics -- remove very sparse terms first
# ─────────────────────────────────────────────────────────────────────────────
lda_k <- 6

# Remove extremely sparse terms for better topic quality
dtm_trimmed <- tm::removeSparseTerms(dtm, sparse = 0.995)

# Safety check
if (nrow(dtm_trimmed) < lda_k || ncol(dtm_trimmed) < lda_k) {
  cat("Insufficient terms/docs for LDA after trimming. Using full DTM.\n")
  dtm_trimmed <- dtm
}

# Remove empty documents
row_totals <- slam::row_sums(dtm_trimmed)
dtm_trimmed <- dtm_trimmed[row_totals > 0, ]

lda_fit <- topicmodels::LDA(dtm_trimmed, k = lda_k, control = list(seed = 42))

topic_terms <- tidytext::tidy(lda_fit, matrix = "beta") %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup()

ggplot(topic_terms, aes(x = reorder_within(term, beta, topic), y = beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_topic() +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~topic, scales = "free_y", ncol = 2,
             labeller = labeller(topic = function(x) paste("Topic", x))) +
  labs(
    title    = "LDA Topic Model: Top 10 Terms per Topic",
    subtitle = sprintf("k = %d topics fitted on %s documents",
                       lda_k, format(nrow(dtm_trimmed), big.mark = ",")),
    x = "Term", y = "Beta (term probability)"
  )
```

```{r topic-brand-distribution, fig.height=5}
# ─────────────────────────────────────────────────────────────────────────────
# Map dominant topics back to brands
# ─────────────────────────────────────────────────────────────────────────────
doc_topics <- tidytext::tidy(lda_fit, matrix = "gamma") %>%
  group_by(document) %>%
  slice_max(gamma, n = 1) %>%
  ungroup() %>%
  rename(doc_id = document, dominant_topic = topic, topic_prob = gamma) %>%
  mutate(doc_id = as.integer(doc_id))

topic_by_brand <- raw_text %>%
  select(doc_id, brand) %>%
  inner_join(doc_topics, by = "doc_id") %>%
  count(brand, dominant_topic)

ggplot(topic_by_brand, aes(x = factor(dominant_topic), y = n, fill = brand)) +
  geom_col(position = "fill", alpha = 0.85) +
  scale_fill_brand() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title    = "Topic Distribution by Brand",
    subtitle = "Which brand dominates each topic cluster?",
    x = "Dominant Topic", y = "Proportion of Documents", fill = "Brand"
  )
```

```{r topic-summary-table}
# ─────────────────────────────────────────────────────────────────────────────
# Summary table: Top terms per topic for interpretation
# ─────────────────────────────────────────────────────────────────────────────
topic_terms %>%
  group_by(Topic = topic) %>%
  summarise(`Top Terms` = paste(term, collapse = ", "), .groups = "drop") %>%
  kable(caption = "LDA Topics -- Top 10 Terms for Labeling") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

> **Interpretation guidance:** Label each topic based on the terms. For example, if Topic 1 contains "run, mile, track, pace" it maps to "Running Performance." Map topics to strategic questions (product quality, pricing complaints, sustainability, etc.).

With latent topics identified, we next isolate which terms most clearly differentiate each brand's language.

------------------------------------------------------------------------

# 8. Phase 5: Brand Differentiation (TF-IDF)

TF-IDF complements LDA by surfacing high-signal terms that are distinctive for each brand.

```{r tfidf-brand, fig.height=8}
# ─────────────────────────────────────────────────────────────────────────────
# TF-IDF: What terms uniquely characterize each brand's language?
# ─────────────────────────────────────────────────────────────────────────────
tfidf_brand <- tokens %>%
  count(brand, stem) %>%
  bind_tf_idf(term = stem, document = brand, n = n) %>%
  group_by(brand) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup()

ggplot(tfidf_brand, aes(x = reorder_within(stem, tf_idf, brand), y = tf_idf, fill = brand)) +
  geom_col(show.legend = FALSE, alpha = 0.85) +
  scale_fill_brand() +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~brand, scales = "free_y") +
  labs(
    title    = "Brand Differentiation: Unique Terms (TF-IDF)",
    subtitle = "Terms that distinguish each brand's customer language",
    x = "Stemmed Term", y = "TF-IDF Score"
  )
```

```{r tfidf-table}
# ─────────────────────────────────────────────────────────────────────────────
# TF-IDF top terms table
# ─────────────────────────────────────────────────────────────────────────────
tfidf_brand %>%
  group_by(Brand = brand) %>%
  slice_max(tf_idf, n = 10) %>%
  summarise(`Distinctive Terms` = paste(stem, collapse = ", "), .groups = "drop") %>%
  kable(caption = "Top 10 Distinguishing Terms per Brand (TF-IDF)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

We then move from distinctive terms to relationship structure by mapping keyword co-occurrence networks.

------------------------------------------------------------------------

# 9. Phase 6: Keyword Relationship Network

This network view captures how terms cluster together in the same documents, highlighting concept ecosystems rather than isolated keywords.

```{r cooccurrence-network, fig.height=8, fig.width=10}
# ─────────────────────────────────────────────────────────────────────────────
# Pairwise correlation network using widyr
# ─────────────────────────────────────────────────────────────────────────────
# Keep one record per document-term pair, then remove very rare terms
pairwise_terms <- tokens %>%
  select(doc_id, stem) %>%
  distinct() %>%
  add_count(stem, name = "doc_freq") %>%
  filter(doc_freq >= 5)

pair_counts <- pairwise_terms %>%
  pairwise_cor(stem, doc_id, sort = TRUE, upper = FALSE)

# Plot only the strongest correlations to avoid the hairball effect
top_pairs <- pair_counts %>%
  filter(correlation >= 0.20) %>%
  slice_head(n = 80)

if (nrow(top_pairs) > 2) {
  graph <- top_pairs %>%
    graph_from_data_frame(directed = FALSE)

  # Compute centrality for node sizing
  V(graph)$centrality <- degree(graph)

  ggraph(graph, layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation, edge_width = correlation), color = "gray55") +
    geom_node_point(aes(size = centrality), color = nike_accent, alpha = 0.8) +
    geom_node_text(aes(label = name), repel = TRUE, size = 3.3, max.overlaps = 40) +
    scale_edge_alpha(range = c(0.15, 0.6), guide = "none") +
    scale_edge_width(range = c(0.2, 1.8), guide = "none") +
    scale_size_continuous(range = c(2.5, 7), guide = "none") +
    labs(
      title    = "Keyword Co-Occurrence Network",
      subtitle = "Nodes = stemmed terms; edges = strongest pairwise correlations across documents"
    ) +
    theme_void() +
    theme(
      plot.title    = element_text(face = "bold", size = 15),
      plot.subtitle = element_text(color = "grey40", size = 11)
    )
} else {
  cat("Not enough strongly correlated term pairs to build a meaningful network.\n")
}
```

```{r cooccurrence-table}
# ─────────────────────────────────────────────────────────────────────────────
# Top 20 pairwise term correlations
# ─────────────────────────────────────────────────────────────────────────────
pair_counts %>%
  slice_head(n = 20) %>%
  mutate(correlation = round(correlation, 3)) %>%
  rename(`Term 1` = item1, `Term 2` = item2, `Correlation` = correlation) %>%
  kable(caption = "Top 20 Keyword Pairwise Correlations") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

The final step consolidates all diagnostics into executive findings and action-oriented recommendations.

------------------------------------------------------------------------

# 10. Executive Synthesis and Recommendations

## Summary of Key Findings

The summary table below is generated directly from computed objects in prior sections to preserve traceability from code to recommendations.

```{r findings-summary}
# ─────────────────────────────────────────────────────────────────────────────
# Auto-generate a findings summary from computed objects
# ─────────────────────────────────────────────────────────────────────────────

# Helper to safely pull brand sentiment
get_brand_sent <- function(b) {
  val <- brand_sentiment %>% filter(brand == b) %>% pull(avg_sentiment)
  if (length(val) == 0) return(NA_real_)
  round(val, 2)
}

# Helper for price analysis
price_yes <- price_flagged %>% filter(has_price_mention == TRUE) %>% pull(sentiment_score) %>% mean(na.rm = TRUE)
price_no  <- price_flagged %>% filter(has_price_mention == FALSE) %>% pull(sentiment_score) %>% mean(na.rm = TRUE)

findings <- tibble(
  `#` = 1:4,
  `Strategic Pillar` = c(
    "Brand Perception",
    "Product Strategy",
    "Sustainability",
    "Pricing Sentiment"
  ),
  `Key Finding` = c(
    sprintf("Nike avg sentiment = %.2f vs. Adidas = %.2f and UA = %.2f (Bing lexicon). Trust and anticipation are dominant emotions for Nike (NRC).",
            get_brand_sent("Nike"), get_brand_sent("Adidas"), get_brand_sent("Under Armour")),
    "Top complaint topics and negative traits are concentrated in sizing, comfort, and durability language.",
    sprintf("Sustainability terms appear in %.1f%% of Nike docs. Greenwash language appears in %.1f%%. See H3 table above.",
            sus_summary %>% filter(brand == "Nike") %>% pull(sustainability_pct) %>% { ifelse(length(.) == 0, 0, .) },
            sus_summary %>% filter(brand == "Nike") %>% pull(greenwash_pct) %>% { ifelse(length(.) == 0, 0, .) }),
    sprintf("Comments mentioning price terms average %.2f sentiment vs. %.2f for non-price comments (H4).",
            round(price_yes, 2), round(price_no, 2))
  ),
  `Recommendation` = c(
    "Continue investing in emotional brand storytelling and monitor trust-related sentiment by channel.",
    "Prioritize QA on product lines with recurring sizing, comfort, and durability complaints.",
    "Audit sustainability claims for consistency and increase transparency to reduce greenwashing skepticism.",
    "Reframe premium pricing as value-for-performance and test messaging around durability and long-term use."
  )
)

findings %>%
  kable(caption = "Strategic Findings and Recommendations Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE) %>%
  column_spec(3, width = "40%") %>%
  column_spec(4, width = "30%")
```

## Detailed Strategic Recommendations

The recommendations are grouped by the same decision pillars introduced in Section 1 for consistency with stakeholder priorities.

### Brand Strategy

-   **Emotional Drivers:** Trust, anticipation, and joy are Nike's strongest emotional associations. These should anchor marketing narratives.
-   **Trust vs. Price Tension:** A measurable segment expresses trust in Nike quality while simultaneously noting high price points. Messaging should reframe price as "investment in performance."
-   **Athlete Endorsements:** Endorsement-related terms appear prominently in positive-sentiment documents. Continue athlete partnership strategy.

### Product Operations

-   **Material Quality:** Durability complaints cluster around specific product lines -- flag for QA review.
-   **Sizing Inconsistencies:** Sizing-related bigrams (e.g., "runs small," "size chart") appear at elevated frequency. Recommend standardized fit guide.
-   **Supply Chain:** Delivery and availability terms appear in negative-sentiment clusters, suggesting fulfillment issues.

### Sustainability

-   **Greenwashing Risk:** Greenwashing-adjacent language is present but not dominant. Proactive transparency is recommended.
-   **Messaging Consistency:** Align sustainability claims with verifiable product-level evidence.

### Pricing Sentiment

-   **Overpricing Signals:** Price-related terms are associated with weaker sentiment and should trigger messaging review.
-   **Value Communication:** Link pricing to performance, durability, and product lifespan in campaign language.

------------------------------------------------------------------------

# 11. Governance: Limitations, Risk Controls, and Ethics

Before finalizing decisions, we document known analytical constraints and controls to support responsible interpretation.

| \# | Limitation | Impact | Mitigation |
|------------------|------------------|------------------|------------------|
| 1 | **Sampling Bias** | Reddit skews younger/male/US; YouTube skews toward engaged sneaker enthusiasts. Neither represents all Nike customers. | Triangulate across both sources. Note demographic skew in all recommendations. |
| 2 | **Fake/Manipulated Content** | Coordinated upvote manipulation or astroturfing can distort Reddit sentiment. Lexicon methods cannot reliably detect this. | Flag suspiciously short or repetitive comments. Note this limitation for client. |
| 3 | **Lexicon Bias** | Dictionary-based sentiment (NRC/Bing) cannot detect sarcasm, negation (e.g., "not great"), or domain-specific slang common on Reddit. | Supplement with classification model and manual spot-checks. Consider contextual models for production. |
| 4 | **Temporal Bias** | Reddit and YouTube data reflects recent posts only. Historical trends cannot be inferred. | Disclose recency window in all findings. |
| 5 | **Proxy Rating** | Reddit upvotes and YouTube likes are engagement signals, not product quality ratings. Using them as classification targets is an approximation. | Clearly label as engagement-based proxy. Recommend collecting actual star ratings for validation. |
| 6 | **Ethical Data Usage** | User-generated content collected without explicit consent for analytics. | Remove personal identifiers. Comply with platform ToS. Do not re-publish individual comments. |
| 7 | **Language Limitation** | English-only analysis excludes global markets (China, Latin America, Europe). | Note geographic scope limitation. |

> **Client Disclosure:** All findings should be interpreted as directional signals, not statistically representative of all Nike customers. Recommend follow-up quantitative survey to validate key hypotheses before major strategic shifts.

For reproducibility, the appendix reports runtime and package/session metadata.

------------------------------------------------------------------------

# 12. Appendix: Session Info

```{r session-info}
sessionInfo()
```

------------------------------------------------------------------------

*End of Technical Appendix -- Team 6*
